### 2012-03-21 outline/outline.tex
added outline to repo. this outline does not include lastest additions by siqi

\documentclass[11pt]{article}
\usepackage{amsmath,textcomp,amssymb,geometry,graphicx}
\newcommand{\argmin}[1]{\underset{#1}{\operatorname{argmin}}\text{ }}
\begin{document}
\title{Fast, Robust Classification with Applications to Periodic Variable Star Data Sets}
\author{Nathan Boley, Siqi Wu, Mark Rogers, and James Long}
\maketitle
We aim to design an efficient, robust support vector machine (SVM) algorithm by combining 1) automated tuning of the regularization parameter $\lambda$ (see \cite{hastie2004entire}) and 2) classification of interval data (see \cite{el2003robust}). The performance of this novel SVM will be tested using periodic variable star data where features are known to lie within confidence intervals. Results will be compared to several other implementations of the SVM, including each method individually and the SVM with the regularization parameter hand-tuned.

Roughly 10\% of stars exhibit variation in luminosity over time. Variable stars fall into one of a dozen or so classes. Determining the correct class of a star is important for astronomical knowledge discovery and efficient use of telescopic follow-up resources \cite{walkowicz2009impact}.

For a particular star, a telescope will observe it at a set of times $t_{1},\ldots,t_{l}$, recording flux measurements (amount of light emitted by star) of $m_{1},\ldots,m_{l}$. Typically there are measures of uncertainty on the flux measurements $e_{1},\ldots,e_{l}$.

The standard method for constructing classifiers on this data is to extract features from $D_{i}=\{(t_{i},m_{i},e_{i})\}_{i=1}^{l}$ (i.e. take functions of this data) that will separate stars in different classes \cite{richards2011machine,debosscher2007automated}. If we compute $p$ features and have a total of $n$ training stars of known class, then we can use standard classification techniques on this $n\times p$ data matrix.

A major problem with this approach is the high levels and heteroskedastic nature of the uncertainty in the features due to having poorly sampled time series ($l$ is small) or high error in the flux measurements ($e_{i}$ are systematically large). This leads to situations where features meant to represent physical quantities of the time series, such as amplitude or period, are incorrect. Our hope is that applying an interval or chance constrained SVM method (for example \cite{el2003robust,calafiore2006distributionally}) will decrease our mis-classification error as measured against an expert labelled data set.

One potential problem with this approach is that the results will
necessarily be a function of the regularization tuning parameter.
One solution is to optimize the tuning parameter so that the optimization
program is solved in the worst case. However, this can lead to much
higher prediction error in the average case. Another approach is to
use cross validation to minimize the prediction error on a test set;
however, this approach can be very expensive.
In {[}2{]}, Hastie et. al. approach this problem by deriving an algorithm
which efficiently computes the entire optimization path for an SVM.
The authors claim that the algorithm solves the standard SVM problem
for all regularization parameters in about twice the time that it
takes for the classic classification problem to solve it for a single,
fixed tuning parameter. The algorithm relies on work done by Rosset
and Zhu, who show in {[}1{]} that one can efficiently solve any optimization
problem of the form
\begin{equation}
\hat{\beta}(\text{\ensuremath{\lambda}})=\argmin\, L(y,\,
X\beta)+\lambda||\beta||_{1},
\end{equation}
\\
where the loss function $L$ is either: quadratic, piecewise quadratic,
piecewise linear, or mixed quadratic linear. Since the interval SVM
problem is of this form, we hope to be able to derive and implement
a fast algorithm.

\bibliographystyle{plain}
\bibliography{outline}

\end{document}

### 2012-04-01 code/Rfunctions.R
Rfunctions.R has functions for plotting time series i.e. light curves

@@ -1,0 +1,114 @@
+## useful R functions
+## by James Long
+## date: April 1, 2012
+
+
+## plot a single light curve
+plotLightCurve = function(tfe,xLabel="Time (Days)",yLabel="m",maintitle="A Lightcurve",
+                          sd.errors=1,width.error.bar=1,cex=.5,reverse=TRUE,
+                          point.colors=FALSE,plot.errors=TRUE){
+  if(class(point.colors) == "logical"){
+    if(!point.colors){
+      point.colors = 1
+    }
+    else {    
+      point.colors = rainbow(nrow(tfe))
+    }
+  }
+  
+  tfe[,2] = -1*tfe[,2]
+  # if there is no main title make the margin at the top very small
+  if(maintitle == "") { par(mar=c(5.1,4.1,1,2.1)) }
+
+  # set the width of the error bars
+  xmin = min(tfe[,1])
+  xmax = max(tfe[,1])
+  ymin = min(tfe[,2] - sd.errors * tfe[,3])
+  ymax = max(tfe[,2] + sd.errors * tfe[,3])
+
+  # set the width of the error bar relative to x-axis
+  width.error.bar = width.error.bar * (xmax - xmin) / 300
+  # set up the plot to the get right dimensions
+  plot(c(xmin,xmax),c(ymin,ymax),col=0,
+       main=maintitle,xlab=xLabel,ylab=yLabel,yaxt='n',
+       cex.lab=1)
+  if(!reverse) {   axis(2) }
+  else {
+    yaxis = (ymax - ymin) * (0:4) / 4 + ymin
+    axis(2,at=yaxis,labels=-round(yaxis,1),las=2,cex.lab=1)
+  }
+  ## draw the error bars
+  if(plot.errors){
+    segments(tfe[,1],tfe[,2] - sd.errors*tfe[,3],tfe[,1],tfe[,2] + sd.errors*tfe[,3],point.colors)
+    segments(tfe[,1]-width.error.bar,tfe[,2] + sd.errors*tfe[,3],tfe[,1] + width.error.bar,tfe[,2] + sd.errors*tfe[,3],point.colors)
+    segments(tfe[,1]-width.error.bar,tfe[,2] - sd.errors*tfe[,3],tfe[,1] + width.error.bar,tfe[,2] - sd.errors*tfe[,3],point.colors)
+  }
+  # put the points on the plot
+  points(tfe[,1],tfe[,2],pch=19,cex=cex,col=point.colors)
+}
+
+
+
+
+
+
+
+###
[…]

### 2012-04-01 code/initial_classification.R
checking to see if data files look right, some initial work with hastie's SVM on some data

@@ -1,0 +1,71 @@
+########## 
+########## 
+########## SOME INITIAL CLASSIFICATION WORK ON LIGHTCURVES 
+##########  
+##########
+########## by James Long 
+########## date: April 1, 2012 
+########## 
+
+
+#### TODO:
+## 1. relation of features on full light curve to interval
+##    - how often is full light curve feature in interval?
+##    - how often is interval essentially a point?
+##    - what features are these most often / least often
+##      true for
+
+## 2. move plotting functions into this folder
+
+## 3. run cart and RF on point data
+
+## 4. run ordinary SVM and hastie SVM on point data
+
+## 5. write up report detailing what you did
+
+
+## program setup
+rm(list=ls(all=TRUE))
+set.seed(22071985)
+options(width=50)
+
+## load source files
+source('Rfunctions.R')
+
+## get the data
+point_file = '../data/convexPoint.dat'
+interval_file = '../data/convexInterval.dat'
+tfe = '../data/convexTfe.dat'
+dataPoint = read.table(point_file,sep=';',header=TRUE)
+dataInterval = read.table(interval_file,sep=';',header=TRUE)
+time_flux = read.table(tfe,sep=';',header=TRUE)
+
+
+## plotting functionality
+i = 0
+i = i + 1
+source_to_plot = dataPoint$source_id[i]
+DrawThreeLightCurves(source_to_plot,dataPoint,time_flux)
+
+
+
+
+
+
+## check to see how often bounds are above / below full curve
+dataPoint = dataPoint[order(dataPoint$source_id),]
+dataInterval = dataInterval[order(dataInterval$source_id),]
+
+features = (grepl('U',names(dataInterval)) | grepl('L',names(dataInterval))) 
+dataInterval.features = dataInterval[,features]
+
+sum(dataInterval$flux_percentile_ratio_mid50L < dataInterval$flux_percentile_ratio_mid50U)
+
+
+sum(dataPoint$flux_percentile_ratio_mid50 < dataInterval$flux_percentile_ratio_mid50U)
+
+
+
+
+
+nrow(dataInterval)

### 2012-04-02 report/ms.tex
early first draft of report

--- 2012-03-21 outline/outline.tex
@@
 \maketitle
-We aim to design an efficient, robust support vector machine (SVM) algorithm by combining 1) automated tuning of the regularization parameter $\lambda$ (see \cite{hastie2004entire}) and 2) classification of interval data (see \cite{el2003robust}).
-The performance of this novel SVM will be tested using periodic variable star data where features are known to lie within confidence intervals.
-Results will be compared to several other implementations of the SVM, including each method individually and the SVM with the regularization parameter hand-tuned.
 
-Roughly 10\% of stars exhibit variation in luminosity over time.
-Variable stars fall into one of a dozen or so classes.
-Determining the correct class of a star is important for astronomical knowledge discovery and efficient use of telescopic follow-up resources \cite{walkowicz2009impact}.
-
-For a particular star, a telescope will observe it at a set of times $t_{1},\ldots,t_{l}$, recording flux measurements (amount of light emitted by star) of $m_{1},\ldots,m_{l}$.
-Typically there are measures of uncertainty on the flux measurements $e_{1},\ldots,e_{l}$.
-
-The standard method for constructing classifiers on this data is to extract features from $D_{i}=\{(t_{i},m_{i},e_{i})\}_{i=1}^{l}$ (i.e.
-take functions of this data) that will separate stars in different classes \cite{richards2011machine,debosscher2007automated}.
-If we compute $p$ features and have a total of $n$ training stars of known class, then we can use standard classification techniques on this $n\times p$ data matrix.
-
-A major problem with this approach is the high levels and heteroskedastic nature of the uncertainty in the features due to having poorly sampled time series ($l$ is small) or high error in the flux measurements ($e_{i}$ are systematically large).
-This leads to situations where features meant to represent physical quantities of the time series, such as amplitude or period, are incorrect.
-Our hope is that applying an interval or chance constrained SVM method (for example \cite{el2003robust,calafiore2006distributionally}) will decrease our mis-classification error as measured against an expert labelled data set.
-
-One potential problem with this approach is that the results will
-necessarily be a function of the regularization tuning parameter.
-One solution is to optimize the tuning parameter so that the optimization
-program is solved in the worst case. However, this can lead to much
-higher prediction error in the average case. Another approach is to
-use cross validation to minimize the prediction error on a test set;
-however, this approach can be very expensive.
-In {[}2{]}, Hastie et. al. approach this problem by deriving an algorithm
-which efficiently computes the entire optimization path for an SVM.
-The authors claim that the algorithm solves the standard SVM problem
-for all regularization parameters in about twice the time that it
-takes for the classic classification problem to solve it for a single,
-fixed tuning parameter. The algorithm relies on work done by Rosset
-and Zhu, who show in {[}1{]} that one can efficiently solve any optimization
-problem of the form
-\begin{equation}
-\hat{\beta}(\text{\ensuremath{\lambda}})=\argmin\, L(y,\,
-X\beta)+\lambda||\beta||_{1},
-\end{equation}
-\\
-where the loss function $L$ is either: quadratic, piecewise quadratic,
-piecewise linear, or mixed quadratic linear. Since the interval SVM
-problem is of this form, we hope to be able to derive and implement
-a fast algorithm.
-
-\bibliographystyle{plain}
-\bibliography{outline}
+Potential Issues:
+\begin{enumerate}
+\item for shorter lightcurves, certain features are biased downwards (for example freq\_signif features). probably std as well. should do bootstrap sampling instead
+\end{enumerate}
 

### 2012-04-03 report/ms.tex
initial rough draft of ms

@@
 
-Potential Issues:
+\section{Light Curves}
+
+Figures \ref{fig:mira}, \ref{fig:cepheid}, \ref{fig:rrlyrae} show the light curves (i.e.
+time series) of three stars.
+Each is of a different class.
+The figures show the raw light curve (time on x-axis, magnitude on y-axis) and folded light curve (phase on x-axis, magnitude on y-axis).
+The phase is determined by computing a period (sometimes wrong!, for example figure \ref{fig:mira}) for each star, and then looking at the remainder of time divided by the period.
+The folded light curve often make the structure of the function much clearer.
+
+\begin{figure}[h]
+  \begin{center}
+    \begin{includegraphics}[scale=.5]{204.pdf}
+      \caption{Light curve of a Mira type variable star.\label{fig:mira}}
+    \end{includegraphics}
+  \end{center}
+\end{figure}
+
+\begin{figure}[h]
+  \begin{center}
+    \begin{includegraphics}[scale=.5]{2000.pdf}
+      \caption{Light curve of a Classical type variable star.\label{fig:cepheid}}
+    \end{includegraphics}
+  \end{center}
+\end{figure}
+
+\begin{figure}[h]
+  \begin{center}
+    \begin{includegraphics}[scale=.5]{4000.pdf}
+      \caption{Light curve of a RR Lyrae AB variable star.\label{fig:rrlyrae}}
+    \end{includegraphics}
+  \end{center}
+\end{figure}
+
+\section{Initial Classification Work}
+
+\subsection{Ignoring Errors}
+I made a data set of 5508 of these light curves of class Mira, Classical Cepheid, and RR Lyrae AB.
+Random forest (a type of classifier) obtained a 0.55\% error rate, without using any feature error information.
+So the current classes may be too easy.
+I could generate features for some stars that belong to classes that are more similar to each other e.g.
+using stars from classes RR Lyrae C and RR Lyrae D (not used here) are a lot alike and would have much higher error rates.
+
+\subsection{Generating Hyper-rectangles}
+To generate the hyper-rectangles I did the following:
 \begin{enumerate}
-\item for shorter lightcurves, certain features are biased downwards (for example freq\_signif features). probably std as well. should do bootstrap sampling instead
+\item sliced each light curve into 5 contiguous parts. ordering measurements in time: slice 1 is 0\% through 50\%, slice 2 is 10\% through 60\%, . . .
+\item derive features for each of these parts
+\item put the interval minimum at the lowest value of the feature for the 5 slices. put the interval max at the maximum feature value across the 5 slices
+\end{enumerate}
+There are several problems with this approach.
+\begin{enumerate}
+\item measurements in the middle of the light curve get used more often
+\item sometimes the intervals do not contain the feature obtained when using the whole light curve.
+this is because taking shorter sections of light curves biases certain features high or low (frequency significance features tend to go down, should probably just get rid of these anyway)
+\end{enumerate}
+Bootstrap sampling might be a good approach, but this would destroy cadence sensitive features.
+So not sure what to do.
+This might be something interesting to discuss in the paper: \textbf{Determining feature error intervals for time series / image data is difficult.}
+
+\section{Notes on ``Robust Classification with Interval Data''}
+\begin{enumerate}
+\item how is new data point classified? this doesn't seem to be mentioned anywhere
+\item role of $\rho$ is not super clear. described as a ``global measure of uncertainty'' on page 3 but then is then is optimized over e.g. equation 16
+\item $\Sigma$ known and given
+\item no mention of kernels for SVM with intervals.
+(kernels are mentioned with respect to MPM on page 11) perhaps SVM intervals don't work with intervals.
+that seems really bad.
+maybe if kernel preserves rectangular structure of interval?
+\end{enumerate}
+\section{Note on Data}
+\begin{enumerate}
+\item for shorter lightcurves, certain features are biased downwards (for example freq\_signif features).
+probably std as well.
+should do bootstrap sampling instead?
+but bootstrap sampling destroys p2p features.
 \end{enumerate}

### 2012-04-03 code/Rfunctions.R
changed some plotting options

@@ -77,37 +77,37 @@ DrawThreeLightCurves=function(source_to_plot,data1,time_flux,
 
   ## plot the raw light curve
   if(plot.unfolded){
-    plotLightCurve(tfe,maintitle=as.character(lc.class),point.colors=point.colors,
+    plotLightCurve(tfe,maintitle=paste(lc.class,"Light Curve"),point.colors=point.colors,
                    plot.errors=plot.errors)
   }
   
   ## fold on twice estimated period
   tfe[,1] = (tfe[,1] %% period) / period
   if(plot.folded.twice){
-    plotLightCurve(tfe,xLabel="Phase",maintitle=period,point.colors=point.colors,
-                   plot.errors=plot.errors)
+    plotLightCurve(tfe,xLabel="Phase",maintitle=paste(lc.class,"folded on period",period),
+                   point.colors=point.colors,plot.errors=plot.errors)
     if(smoother){
       line.smu = supsmu(tfe[,1],tfe[,2],periodic=TRUE)
       line.smu$y = -1 * line.smu$y
-      lines(line.smu$x,line.smu$y,col='red',lty=1,lwd=2)
+      lines(line.smu$x,line.smu$y,col='gray',lty=1,lwd=2)
       line.smu = supsmu(tfe[,1],tfe[,2],
         span=.05,wt=1/tfe[,3],periodic=TRUE,bass=8)
       line.smu$y = -1 * line.smu$y
-      lines(line.smu$x,line.smu$y,col='green',lty=1,lwd=2)
+      ##lines(line.smu$x,line.smu$y,col='green',lty=1,lwd=2)
     }
   }  
   ## fold on estimated period
   tfe[,1] = (tfe[,1] %% .5) / .5
   if(plot.folded){
-    plotLightCurve(tfe,xLabel="Phase",maintitle=period/2,point.colors=point.colors,
-                   plot.errors=plot.errors)  
+    plotLightCurve(tfe,xLabel="Phase",maintitle=paste(lc.class,"folded on period",period/2),
+                   point.colors=point.colors,plot.errors=plot.errors)  
     if(smoother){
       line.smu = supsmu(tfe[,1],tfe[,2],periodic=TRUE)
       line.smu$y = -1 * line.smu$y
-      lines(line.smu$x,line.smu$y,col='red',lty=1,lwd=2)
[…]

### 2012-04-03 code/initial_classification.R
some initial classification results

@@ -8,22 +8,6 @@
 ########## 
 
 
-#### TODO:
-## 1. relation of features on full light curve to interval
-##    - how often is full light curve feature in interval?
-##    - how often is interval essentially a point?
-##    - what features are these most often / least often
-##      true for
-
-## 2. move plotting functions into this folder
-
-## 3. run cart and RF on point data
-
-## 4. run ordinary SVM and hastie SVM on point data
-
-## 5. write up report detailing what you did
-
-
 ## program setup
 rm(list=ls(all=TRUE))
 set.seed(22071985)
@@ -31,6 +15,10 @@ options(width=50)
 
 ## load source files
 source('Rfunctions.R')
+
+## load packages
+library('randomForest')
+library('rpart')
 
 ## get the data
 point_file = '../data/convexPoint.dat'
@@ -44,28 +32,112 @@ time_flux = read.table(tfe,sep=';',header=TRUE)
 ## plotting functionality
 i = 0
 i = i + 1
+
+
+
+source('Rfunctions.R')
+
+
+pdf(paste(i,".pdf",sep=""))
 source_to_plot = dataPoint$source_id[i]
-DrawThreeLightCurves(source_to_plot,dataPoint,time_flux)
+DrawThreeLightCurves(source_to_plot,dataPoint,time_flux,
+                     plot.folded.twice=FALSE,
+                     smoother=TRUE)
+dev.off()
 
 
 
 
 
+## check that lower bounds are always <= upper bounds
+feature_names = names(dataPoint)[2:(length(dataPoint)-1)]
+for(i in feature_names){
+  print(i)
+  upper_name = paste(i,"U",sep="")
+  lower_name = paste(i,"L",sep="")
+  print(sum(dataInterval[,lower_name] <=
+            dataInterval[,upper_name]))
+}
 
+
+
+
+
+##
 ## check to see how often bounds are above / below full curve
+##
 dataPoint = dataPoint[order(dataPoint$source_id),]
 dataInterval = dataInterval[order(dataInterval$source_id),]
 
-features = (grepl('U',names(dataInterval)) | grepl('L',names(dataInterval))) 
-dataInterval.features = dataInterval[,features]
+## how often is feature in interval
+feature_names = names(dataPoint)[2:(length(dataPoint)-1)]
+for(i in feature_names){
+  print(i)
+  upper_name = paste(i,"U",sep="")
+  lower_name = paste(i,"L",sep="")
[…]

### 2012-04-15 report/ms.tex
writing data description part of paper

@@
 \title{Fast, Robust Classification with Applications to Periodic Variable Star Data Sets}
-\author{Nathan Boley, Siqi Wu, Mark Rogers, and James Long}
+\author{Siqi Wu, Mark Rogers, and James Long}
 \maketitle
+
+\section{Introduction}
+
+\section{Periodic Variable Light Curves}
+Modern astronomical surveys observe billions of light sources over the course of a few years.
+Periodic variables, sources which vary periodically in brightness over time, are some of the most interesting.
+Periodic variables were crucial in Edwin Hubble's and XXXXX YYYY discovery of the existence of galaxies, and more recently in .
+.
+.
+.
+.
+..
+
+Figure \ref{fig:cepheid} displays the light curve (i.e.
+time series) of a periodic variable belonging to the class Classical Cepheid.
+The points in plot a) represent flux measurements (in magnitude) made by the telescope at particular times (the 0 point on the time axis is arbitrary).
+All of these measurements are of a single object.
+The brightness of Classical Cepheids varies periodically.
+Using fourier methods, one can estimate a period from the measurements in plot a).
+Plot b) of Figure \ref{fig:cepheid} displays the flux measurements against the phase of each time measurement (again, 0 point of phase is arbitrary).
+Here we can observe the structure of the periodic variation.
+This is known as the \textit{folded light curve}.
+\begin{figure}[h]
+  \begin{center}
+    \begin{includegraphics}[scale=.5]{2000.pdf}
+      \caption{Light curve of a Classical type variable star.\label{fig:cepheid}}
+    \end{includegraphics}
+  \end{center}
+\end{figure}
+
+There are many classes of periodic variable sources.
+Figure \ref{fig:mira} displays an example of a Mira light curve.
+From the y-axis we can see that this source has higher amplitude than the Classical Cepheid (this is typical of the Mira class) and more sinusoidal variation (also typical).
+Note that the fourier methods appear to have estimated an incorrect period for this source.
+The true period may be around 161, half the estimate.
+\begin{figure}[h]
+  \begin{center}
+    \begin{includegraphics}[scale=.5]{204.pdf}
+      \caption{Light curve of a Mira type variable star.\label{fig:mira}}
+    \end{includegraphics}
+  \end{center}
+\end{figure}
+
+Separating periodic variables into classes is important for scientific knowledge discovery and efficient use of telescopic follow-up resources.
+The size of modern data sets requires that much of this work be automated.
+
+This may be due to intrinsic variation in the amount of light a star emits over time or to extrinsic properties such as in eclipsing binaries systems where the eclipses cause less light to reach a telescope.
+
+Periodic variable starsThese stars exhibit periodic variation in the amount of light they emit.
+
+\begin{enumerate}
+\item background as to what these objects look like
+\item why this task is important / interesting
+\item previous work on the subject, creating features
+\item how there are errors in features
+\end{enumerate}
 
@@
 The folded light curve often make the structure of the function much clearer.
-
-\begin{figure}[h]
-  \begin{center}
-    \begin{includegraphics}[scale=.5]{204.pdf}
-      \caption{Light curve of a Mira type variable star.\label{fig:mira}}
-    \end{includegraphics}
-  \end{center}
-\end{figure}
-
-\begin{figure}[h]
-  \begin{center}
-    \begin{includegraphics}[scale=.5]{2000.pdf}
-      \caption{Light curve of a Classical type variable star.\label{fig:cepheid}}
-    \end{includegraphics}
-  \end{center}
-\end{figure}
 

### 2012-04-15 report/ms.tex
working on data description portion of report

--- 2012-04-03 report/ms.tex
@@
 \title{Fast, Robust Classification with Applications to Periodic Variable Star Data Sets}
-\author{Nathan Boley, Siqi Wu, Mark Rogers, and James Long}
+\author{Siqi Wu, Mark Rogers, and James Long}
 \maketitle
+
+\section{Introduction}
+
+\section{The Data}
+\subsection{Background on Periodic Variables}
+Modern astronomical surveys observe millions of light sources over the course of a mission lasting a few years.
+Periodic variables, sources which vary periodically in brightness over time, are some of the most interesting.
+Periodic variables were crucial in Edwin Hubble's discovery of objects outside the Milky Way.
+More recently,
+
+Periodic variables may be divided into a few dozen classes based on physical properties of light sources.
+Separating the sources into classes is a critical step in turning raw astronomical observations into scientific knowledge.
+The size of modern data sets requires that much of this work be automated by machine learning and statistical classifiers.
+
+Figure \ref{fig:cepheid} displays the light curve (i.e.
+time series) of a periodic variable belonging to the class Classical Cepheid.
+The points in plot a) represent flux measurements in magnitudes (i.e.
+brightness of the source) made by the telescope at particular times.
+The 0 point on the time axis is arbitrary.
+Using fourier methods, one can estimate a period from the measurements in plot a).
+Plot b) of Figure \ref{fig:cepheid} displays the flux measurements of the same object.
+However here the x-axis is phase of each time measurement, computed using the estimated period of 4.51 days.
+Here we can observe the structure of the periodic variation.
+This is known as the \textit{folded light curve}.
+\begin{figure}[h]
+  \begin{center}
+    \begin{includegraphics}[scale=.5]{2000.pdf}
+      \caption{Light curve of a Classical type variable star.\label{fig:cepheid}}
+    \end{includegraphics}
+  \end{center}
+\end{figure}
+
+Figure \ref{fig:mira} displays an example of a Mira light curve.
+From the y-axis we can see that this source has higher amplitude than the Classical Cepheid (this is typical of the Mira class) and more sinusoidal variation (also typical).
+Note that the fourier methods appear to have estimated an incorrect period for this source.
+The true period appears to be around 161 days, half of the estimate.
+\begin{figure}[h]
+  \begin{center}
+    \begin{includegraphics}[scale=.5]{204.pdf}
+      \caption{Light curve of a Mira type variable star.\label{fig:mira}}
+    \end{includegraphics}
+  \end{center}
+\end{figure}
+
+\subsection{Classification Methodology}
+There has been a lot of recent work in the astronomy literature towards developing highly accurate classifiers for periodic variables \cite{debosscher2007automated,richards2011machine,dubath2011random}.
+The standard methods work as follows.
+A telescope observes a source $j$ at times $t_{1},\ldots,t_{l}$, recording flux measurements of $m_{1},\ldots,m_{l}$.
+Typically there are measures of uncertainty on the flux measurements $e_{1},\ldots,e_{l}$.
+So each source $j$ is initially characterized by an $l \times 3$ matrix $D_j=\{(t_{i},m_{i},e_{i})\}_{i=1}^{l}$.
+Note that $l$, the number of times the source was observed, is different for each $D_j$.
+Also the time sampling of the flux measurements is irregular and different for each source.
+Associated with each source is a classification, such as Mira, Classical Cepheid, RR Lyrae, etc.
+
+In The standard method for constructing classifiers on this data is to extract features from $D$ (i.e.
+take functions of this data) that will separate stars in different classes \cite{richards2011machine,debosscher2007automated}.
+If we compute $p$ features and have a total of $n$ training stars of known class, then we can use standard classification techniques on this $n\times p$ data matrix.
+
+\subsection{Uncertain Features}
+A major problem with this approach is the high levels and heteroskedastic nature of the uncertainty in the features due to having poorly sampled time series ($l$ is small) or high error in the flux measurements ($e_{i}$ are systematically large).
+This leads to situations where features meant to represent physical quantities of the time series, such as amplitude or period, are incorrect.
+
+\begin{enumerate}
+\item previous work on the subject, creating features
+\item how there are errors in features
+\end{enumerate}
 
@@
 
+\bibliographystyle{plain}
+\bibliography{refs}
+
 \end{document}

### 2012-04-15 report/ms.tex
mostly done with description of the data

@@
 \begin{document}
-\title{Fast, Robust Classification with Applications to Periodic Variable Star Data Sets}
+\title{Fast, Robust Classification with Applications to Periodic Variable Stars}
 \author{Siqi Wu, Mark Rogers, and James Long}
@@
 Periodic variables, sources which vary periodically in brightness over time, are some of the most interesting.
-Periodic variables were crucial in Edwin Hubble's discovery of objects outside the Milky Way.
-More recently,
+In the 1920's, periodic variables were crucial in Edwin Hubble's discovery the existence of galaxies \cite{berendzen1971hubble}.
+More recently, periodic variables have played an important role in determining expansion of the universe \cite{freedman2010hubble}.
 
@@
 \end{figure}
-
 \subsection{Classification Methodology}
-There has been a lot of recent work in the astronomy literature towards developing highly accurate classifiers for periodic variables \cite{debosscher2007automated,richards2011machine,dubath2011random}.
-The standard methods work as follows.
+There has been a lot of recent progress in the astronomy literature towards developing highly accurate classifiers for periodic variables \cite{debosscher2007automated,richards2011machine,dubath2011random}.
+The standard approach works as follows.
 A telescope observes a source $j$ at times $t_{1},\ldots,t_{l}$, recording flux measurements of $m_{1},\ldots,m_{l}$.
@@
 So each source $j$ is initially characterized by an $l \times 3$ matrix $D_j=\{(t_{i},m_{i},e_{i})\}_{i=1}^{l}$.
-Note that $l$, the number of times the source was observed, is different for each $D_j$.
+Note that $l$, the number of times the source is observed, is different for each $D_j$.
 Also the time sampling of the flux measurements is irregular and different for each source.
@@
 
-In The standard method for constructing classifiers on this data is to extract features from $D$ (i.e.
-take functions of this data) that will separate stars in different classes \cite{richards2011machine,debosscher2007automated}.
-If we compute $p$ features and have a total of $n$ training stars of known class, then we can use standard classification techniques on this $n\times p$ data matrix.
+In order to construct a classifier, features are \textit{extracted} from $D$ (i.e.
+take functions of $D$) that will separate sources into different classes.
+Features vary from study to study, but typical ones include period (inverse of strongest fourier frequency), amplitude, skew, and estimates of derivatives.
+
+If we compute $p$ features and have a total of $n$ training stars of known class ($D_1, \ldots D_n$), then we can use standard classification techniques on this $n\times p$ data matrix to construct a classifier.
+Given this classifier, we can then assign a class to a new source by extracting features and running the features through the classifier.
 
 \subsection{Uncertain Features}
-A major problem with this approach is the high levels and heteroskedastic nature of the uncertainty in the features due to having poorly sampled time series ($l$ is small) or high error in the flux measurements ($e_{i}$ are systematically large).
+A major problem with the standard approach is the high levels and heteroskedastic nature of the uncertainty in the features due to having poorly sampled time series ($l$ is small) or high error in the flux measurements ($e_{i}$ are systematically large).
 This leads to situations where features meant to represent physical quantities of the time series, such as amplitude or period, are incorrect.
-
-\begin{enumerate}
-\item previous work on the subject, creating features
-\item how there are errors in features
-\end{enumerate}
+As an example \textbf{TODO: Include example with nice graphic here}
 

### 2012-04-17 code/cv.m
added classifier svm.m and cross-validator cv.m

@@ -1,0 +1,3 @@
+Lambda = 0:.01:1;
+Rho = 0:.01:1;
+

### 2012-04-17 code/svm.m

@@ -1,0 +1,54 @@
+function L = svm(model,XTr,YTr,XTe,YTe,lambda,rho,Sigma)
+% if argument is unused, just pass []. Loss function used: sign(y(i) * f(x(i)))
+%
+% INPUTS
+% 
+% model = 'path', 'interval', or 'combined': indicates model to use
+% XTr = [n x p]: training data with n points and p features
+% YTr = [n x 1]: training labels
+% XTe
+% lambda = nonnegative scalar: regularization parameter
+% rho = nonnegative scalar: global uncertainty parameter
+% Sigma = [n x p]: confidence intervals
+%
+% OUTPUTS
+%
+% L = scalar (loss): 
+
+% estimate beta, beta0, xi 
+if strcmp(model,'path')
+	cvx_begin
+		variable beta(p);
+		variable beta0(1);
+		variable xi(p);
+		minimize xi'*ones(p,1) + lambda/2*norm(beta,2)^2
+		subject to
+			1 - YTr .* (beta0+XTr*beta) <= xi;
+			xi >= 0;
+	cvx_end
+elseif strcmp(model,'interval')
+	cvx_begin
+		variable beta(p);
+		variable beta0(1);
+		variable xi(p);
+		minimize xi'*ones(p,1)
+		subject to
+			YTr .* (XTr*beta + beta0) >= 1 - xi + rho*Sigma*abs(beta);
+			xi >= 0;
+	cvx_end
+elseif strcmp(model,'combined')
+	cvx_begin
+		variable beta(p);
+		variable beta0(1);
+		variable xi(p);
+		minimize xi'*ones(p,1) + lambda/2*norm(beta,2)^2
+		subject to
+			xi >= 1 - YTr .* (beta0 + XTr*beta) + rho*Sigma*abs(beta);
+			xi >= 0;
+	cvx_end
+end
+
+% compute loss L
+f = @(x) beta0 + x'*beta;
+l = @(x,y,f) (1 - sign(y .* f(x))) / 2; % 0-1 loss function
+L = sum(l(XTe',YTe,f)) / numel(YTe);

### 2012-04-17 code/cv.m
modified cv.m

@@ -1,3 +1,23 @@
+function L = cv(X,Y,Sigma,model)
+% leave-one-out cross-validation
+%
+% X = [n x p]: Data
+% Y = [n x 1]: Labels
+% L in [0,inf]: Loss
+
 Lambda = 0:.01:1;
 Rho = 0:.01:1;
-
+L = zeros(numel(Lambda),numel(Rho));
+n = size(X,1);
+for lambda = Lambda
+	for rho = Rho
+		for i = 1:n
+			XTr = X(1:n ~= i,:);
+			YTr = Y(1:n ~= i);
+			XTe = X(i,:);
+			YTe = Y(i);
+			SigmaTr = X(1:n ~= i,:);
+			L(lambda*100+1,rho*100+1) = svm(model,XTr,YTr,XTe,YTe,lambda,rho,SigmaTr);
+		end
+	end
+end

### 2012-04-30 code/sim_data.py
updated the simulated data

@@ -7,8 +7,8 @@ def gen_normal_data(n1=100,n2=100,p=2):
     feat_class1 = np.random.normal(loc=0.,scale=1.,size=n1*p).reshape((n1,p))
     feat_class2 = np.random.normal(loc=1.,scale=1.,size=n2*p).reshape((n2,p))
     features = np.vstack((feat_class1,feat_class2))
-    error_feature1  = np.ones(n1*p).reshape((n1+n2,1))
-    error_feature2  = np.ones(n2*p).reshape((n1+n2,1)) / 10.0
+    error_feature1  = np.ones(n1+n2).reshape((n1+n2,1))
+    error_feature2  = np.ones((n1+n2)*(p-1)).reshape((n1+n2,p-1)) / 10.0
     errors = np.hstack((error_feature1,error_feature2))
     everything = np.hstack((classification,features,errors))
     return everything
@@ -16,5 +16,5 @@ def gen_normal_data(n1=100,n2=100,p=2):
     
 
 if __name__ == "__main__":
-    np.savetxt("simulated_interval",gen_normal_data(n1=10,n2=10),fmt="%f")
+    np.savetxt("simulated_interval",gen_normal_data(n1=50,n2=50,p=2),fmt="%f")
     

### 2012-04-30 code/sim_data.py
testing whether code is pushing correctly

@@ -1,4 +1,5 @@
 ## two classes normal, with a lot of error on 1
+## test add
 import numpy as np
 
 

### 2012-04-30 code/collectResults.m
pushed updated source files.

@@ -1,0 +1,18 @@
+function collectResults(fname_prefix,sname)
+if strcmp(fname_prefix(numel(fname_prefix)),'/')
+	fname_prefix = fname_prefix(1:(numel(fname_prefix)-1));
+end
+d = dir([fname_prefix '*.mat']);
+dname = fname_prefix;
+while ~strcmp(dname(numel(dname)),'/')
+	dname = dname(1:(numel(dname)-1));
+end
+results = zeros(100);
+save(sname,'results');
+load(sname); % has results variable in it, a table of loss values
+for i = 1:numel(d)
+	load([dname d(i).name]);
+	iParam
+	results(iParam) = loss;
+end
+save(sname,'results');

### 2012-04-30 code/formatStarIntervalData.m

@@ -26,7 +26,7 @@ p = (J-2)/2;
 X = zeros(n,p);
 S = zeros(n,p);
 Y = zeros(n,1);
-class = cell(n,1);
+class_of_each_datapoint = cell(n,1);
 class_names = {};
 source_id = zeros(n,1);
 L = zeros(n,p);
@@ -39,10 +39,10 @@ s = fgetl(f);
 for i = 1:n
 	C = split(fgetl(f),';');
 	disp([i,numel(C),J])
-	class{i} = C{J-1};
+	class_of_each_datapoint{i} = C{J-1};
 	try,source_id(i) = str2num(C{J});catch err,keyboard;end
-	if ~ismember(class{i},class_names)
-		class_names{numel(class_names)+1} = class{i};
+	if ~ismember(class_of_each_datapoint{i},class_names)
+		class_names{numel(class_names)+1} = class_of_each_datapoint{i};
 	end
 	for j = 1:(J-2)
 		feature_name = raw_feature_names{j}(1:(numel(raw_feature_names{j})-1));
@@ -70,9 +70,9 @@ end
 X = (L+U) ./ 2;
 S = abs(L-U) ./ 2;
 for i = 1:numel(class_names)
-	iClass = find(strcmp(class,class_names{i}));
+	iClass = find(strcmp(class_of_each_datapoint,class_names{i}));
 	Y(iClass) = i*ones(numel(iClass),1);
 end
 
 % save data in .mat file
-save(sname,'X','Y','S','class','class_names','source_id','feature_names');	
+save(sname,'X','Y','S','class_of_each_datapoint','class_names','source_id','feature_names');	

### 2012-04-30 code/formatStarPointData.m

@@ -29,9 +29,9 @@ for i = 1:n
 	i
 	C = split(fgetl(f),';');
 	source_id(i) = str2num(C{1});
-	class{i} = C{J};
-	if ~ismember(class{i},class_names)
-		class_names{numel(class_names)+1} = class{i};
+	class_of_each_datapoint{i} = C{J};
+	if ~ismember(class_of_each_datapoint{i},class_names)
+		class_names{numel(class_names)+1} = class_of_each_datapoint{i};
 	end
 	for j = 0:(p+1)
 		num = str2num(C{j+1});
@@ -46,9 +46,9 @@ end
 
 % construct Y
 for i = 1:numel(class_names)
-	iClass = find(strcmp(class,class_names{i}))
+	iClass = find(strcmp(class_of_each_datapoint,class_names{i}))
 	Y(iClass) = i*ones(numel(iClass),1);
 end
 
 % save data in .mat file
-save(sname,'X','Y','class','class_names','source_id','feature_names');
+save(sname,'X','Y','class_of_each_datapoint','class_names','source_id','feature_names');

### 2012-04-30 code/getParams.m

@@ -1,0 +1,9 @@
+function getParams(sname,Lambda,Rho)
+
+Params = cell(numel(Lambda),numel(Rho));
+for i = 1:numel(Lambda)
+	for j = 1:numel(Rho)
+		Params{i,j} = [Lambda(i) Rho(j)];
+	end
+end
+save(sname,'Params')

### 2012-04-30 code/getResults.m

@@ -1,0 +1,44 @@
+function getResults(fname,sname,params_fname,iParam,model)
+
+load(fname);
+cv_split = .1;
+num_cv_splits = 1/cv_split;
+random_splits = false;
+load(params_fname);
+lambda = Params{iParam}(1);
+rho = Params{iParam}(2);
+if strcmp(model,'path')
+	S = rand(size(X));
+end
+
+% if multiclass data, then choose the two classes with the most datapoints
+class_indices = 1:max(Y);
+class_freqs = zeros(size(class_indices));
+for i = class_indices
+	class_freqs(i) = numel(find(Y==i));
+end
+[temp class_indices] = sort(class_freqs,'descend');
+index_of_first_class = class_indices(1);
+index_of_second_class = class_indices(2);
+I1 = find(Y==index_of_first_class);
+I2 = find(Y==index_of_second_class);
+I1 = I1(1:numel(I2));
+Y1 = Y(I1) ./ Y(I1) * (1);
+Y2 = Y(I2) ./ Y(I2) * (-1);
+X1 = X(I1,:);
+X2 = X(I2,:);
+S1 = S(I1,:);
+S2 = S(I2,:);
+X = [X1;X2];
+Y = [Y1;Y2];
+S = [S1;S2];
+valid_feature_indices = zeros(1,size(X,2));
+for i = 1:size(X,2)
+	valid_feature_indices(i) = all(~isnan(X(:,i)));
+end
+valid_feature_indices = logical(valid_feature_indices);
+X = X(:,valid_feature_indices);
+S = S(:,valid_feature_indices);
+loss = xval(X,Y,S,model,lambda,rho,cv_split,num_cv_splits,random_splits);
+save([sname '_'  num2str(iParam,'%03d')],'lambda','rho','loss','iParam');
+

### 2012-04-30 code/svm.m

@@ -1,0 +1,56 @@
+function loss = svm(model,XTr,YTr,XTe,YTe,lambda,rho,S)
+% if argument is unused, just pass []. Loss function used: sign(y(i) * f(x(i)))
+%
+% INPUTS
+% 
+% model = 'path', 'interval', or 'combined': indicates model to use
+% XTr = [n x p]: training data with n points and p features
+% YTr = [n x 1]: training labels.  Each entry in {-1,1}.
+% XTe = [n' x p]: test data
+% YTe = [n' x 1]: test labels.  Each entry in {-1,1}.
+% lambda = nonnegative scalar: regularization parameter
+% rho = nonnegative scalar: global uncertainty parameter
+% S = [n x p]: confidence intervals
+%
+% OUTPUTS
+%
+% loss = scalar: loss
+
+% estimate beta, beta0, xi
+[n p] = size(XTr);
+if strcmp(model,'path')
+	cvx_begin
+		variable b(p);
+		variable b0(1);
+		variable xi(n);
+		minimize(xi'*ones(n,1) + lambda/2*b'*b)
+		subject to
+			ones(n,1) - YTr .* (b0+XTr*b) <= xi;
+			xi >= 0;
+	cvx_end
+elseif strcmp(model,'interval')
+	cvx_begin
+		variable b(p);
+		variable b0(1);
+		variable xi(n);
+		minimize(xi'*ones(n,1))
+		subject to
+			YTr .* (XTr*b + b0) >= 1 - xi + rho*S*abs(b);
+			xi >= 0;
+	cvx_end
+elseif strcmp(model,'combined')
+	cvx_begin
+		variable b(p);
+		variable b0(1);
+		variable xi(n);
+		minimize(xi'*ones(n,1) + lambda/2*b'*b)
+		subject to
+			xi >= 1 - YTr .* (b0 + XTr*b) + rho*S*abs(b);
+			xi >= 0;
+	cvx_end
+end
+
+% compute loss l
+f = @(x) b0 + x'*b;
+l = @(x,y,f) (1 - sign(y .* f(x))) / 2; % 0-1 loss function
+loss = sum(l(XTe',YTe,f)) / numel(YTe);

### 2012-04-30 code/testcombined.m

@@ -1,0 +1,17 @@
+function test(iParams)
+
+%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/simulated_interval';
+%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/simulated_interval/path/path';
+%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexPoint';
+%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexPoint/path/path';
+fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexInterval';
+sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/combined/combined';
+
+
+
+params_fname = '/home/aa/ugrad/mrogers/ee227a/project/params100.mat';
+model = 'path';
+for i = iParams
+	getResults(fname,sname,params_fname,i,model);
+end
+

### 2012-04-30 code/testinterval.m

@@ -1,0 +1,17 @@
+function test(iParams)
+
+%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/simulated_interval';
+%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/simulated_interval/path/path';
+%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexPoint';
+%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexPoint/path/path';
+fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexInterval';
+sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/interval/interval';
+
+
+
+params_fname = '/home/aa/ugrad/mrogers/ee227a/project/params100.mat';
+model = 'path';
+for i = iParams
+	getResults(fname,sname,params_fname,i,model);
+end
+

### 2012-04-30 code/testpath.m

@@ -1,0 +1,19 @@
+function test(iParams)
+
+%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/simulated_interval';
+%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/simulated_interval/path/path';
+%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexPoint';
+%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexPoint/path/path';
+%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexInterval';
+%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/path/path';
+fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RR2convexInterval';
+sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RR2convexInterval/path/path';
+
+
+
+params_fname = '/home/aa/ugrad/mrogers/ee227a/project/params100.mat';
+model = 'path';
+for i = iParams
+	getResults(fname,sname,params_fname,i,model);
+end
+

### 2012-04-30 code/xval.m

@@ -1,0 +1,57 @@
+function loss = xval(X,Y,S,model,lambda,rho,cv_split,num_cv_splits,random_splits)
+% cross-validation
+%
+% X = [n x p]: Data
+% Y = [n x 1]: Labels. Each entry in {-1,1}.
+% S = [n x p]: confidence intervals. 
+% L = {num_cv_splits x 1}: cell array containing triples [lambda,rho,loss]
+% cv_split: fraction of data to be tested on. To train on 75% of the data, for example, let cv_split = .75; to perform leave-one-out cross-validation, let cv_split = 1/n and num_cv_splits = n.
+% num_cv_splits: number of times to run cross validation on random splits
+
+loss = 0;
+n = size(X,1);
+
+% preprocess data so that labels are evenly distributed
+if ~random_splits
+	I1 = Y==Y(1);
+	I2 = Y~=Y(1);
+	X1 = X(I1,:);
+	X2 = X(I2,:);
+	Y1 = Y(I1);
+	Y2 = Y(I2);
+	S1 = S(I1,:);
+	S2 = S(I2,:);
+	X(1:2:n,:) = X1;
+	X(2:2:n,:) = X2;
+	Y(1:2:n,1) = Y1;
+	Y(2:2:n,1) = Y2;
+	S(1:2:n,:) = S1;
+	S(2:2:n,:) = S2;
+end
+
+for i = 1:num_cv_splits
+	nTe = floor(n*cv_split);
+	nTr = n-nTe;
+	
+	% construct training and test data and labels
+	if random_splits
+		r = randperm(n);
+		iTe = r(1:nTe);
+		iTr = r((nTe+1):n);
+		XTr = X(iTr,:);
+		YTr = Y(iTr);
+		XTe = X(iTe,:);
+		YTe = Y(iTe);
+		STr = S(iTr,:);
+	else
+		iTe = 1:nTe + (i-1)*nTe;
+		iTr = ~ismember(1:n,iTe);
+		XTr = X(iTr,:);
+		YTr = Y(iTr);
+		try,XTe = X(iTe,:);catch err,disp(err.message);keyboard;end
+		YTe = Y(iTe);
+		STr = S(iTr,:);
+	end
+	loss = loss + svm(model,XTr,YTr,XTe,YTe,lambda,rho,STr);
+end
+loss = loss / num_cv_splits;

### 2012-04-30 code/initial_classification.R
a few lines to play around with classification

@@ -21,13 +21,43 @@ library('randomForest')
 library('rpart')
 
 ## get the data
-point_file = '../data/convexPoint.dat'
-interval_file = '../data/convexInterval.dat'
-tfe = '../data/convexTfe.dat'
+data1_file = "../data/RR2convexMeta.dat"
+point_file = '../data/RR2convexPoint.dat'
+interval_file = '../data/RR2convexInterval.dat'
+tfe = '../data/RR2convexTfe.dat'
 dataPoint = read.table(point_file,sep=';',header=TRUE)
 dataInterval = read.table(interval_file,sep=';',header=TRUE)
 time_flux = read.table(tfe,sep=';',header=TRUE)
+data1 = read.table(data1_file,sep=";",header=TRUE)
 
+
+## density of points
+originals = (data1$features.source_id == data1$sources.original_source_id)
+sum(originals)
+d1 = density(data1$features.n_points[originals])
+plot(d1)
+
+
+##
+# 1. what kernel did joey use
+# 2. set up a small/hard two class problem
+# 3. figure out how kernels play in
+# 4. come up with realistic simulated data set
+# 5. lambda versus rho plot for loss on simulated and astro
+
+### densities of errors
+densities = aggregate(time_flux$error,by=list(time_flux$source_id),density,simplify=FALSE)
+class(densities)
+plot(c(.01,.06),c(0,200),col=0,xlab="Std. Dev.",ylab="Density")
+j = 100
+for(i in 1:j){
+  if(densities[i,2][[1]]$n > 40){
+    lines(densities[i,2][[1]])
+  }
+}
+
+class(densities[1])
+class(densities[1])
 
 ## plotting functionality
 i = 0
@@ -71,14 +101,24 @@ dataInterval = dataInterval[order(dataInterval$source_id),]
 
 ## how often is feature in interval
 feature_names = names(dataPoint)[2:(length(dataPoint)-1)]
-for(i in feature_names){
+frac_in_int = data.frame(rep("A",length(feature_names)),
+  rep(0,length(feature_names)),stringsAsFactors=FALSE)
+names(frac_in_int) = c("feature","frac_in_int")
+for(j in 1:length(feature_names)){
+  i = feature_names[j]
   print(i)
   upper_name = paste(i,"U",sep="")
[…]

### 2012-04-30 code/sim_data.py
updated sim_data. now more flexible for making simulated data

@@ -1,21 +1,90 @@
 ## two classes normal, with a lot of error on 1
 ## test add
+
+## TODO:
+## multivariate gaussian classes
+## error bars / interpretation of error bars
+## fix plotting issue
+## make loop more elegant
+
 import numpy as np
+import matplotlib
+from matplotlib import pyplot as plt
+
+def qda_model(means,covs,ns):
+    ''' generate classification data, multivariate gaussian '''
+    d, p = means.shape
+    ## error check for dimensions of entries
+    if covs.shape != (d,p,p):
+        print "means is " + repr(d) + " x " + repr(p) + ", covs must be " + repr(d) \
+            + " x " + repr(p) + " x " + repr(p)
+        return 0
+    if ns.shape != (d,):
+        print "means is " + repr(d) + " x " + repr(p) + ", ns must be " + repr(d)
+        return 0
+    ## now populate the feature matrix
+    features = np.ndarray((ns.sum(),p))
+    jj = 0
+    for ii in range(d):
+        features[jj:(ns[ii] + jj),:] = \
+            np.random.multivariate_normal(mean=means[ii,:],cov=covs[ii,:,:],size=ns[ii])
+        jj += ns[ii]
+
+    ## create class labels and return
+    classification = np.repeat(range(ns.size),ns).reshape((ns.sum(),1))
+    data = np.hstack((classification,features))
+    return data
+
+def fake_interval(means,covs,ns):
+    ''' generates gaussian data and add interval of width 0.
+    useful for testing interval svm code '''
+    data = qda_model(means,covs,ns)
+    n, p = data.shape
+    intervals = np.zeros(p*n).reshape((n,p))
+    data = np.hstack((data,intervals))
+    return data
 
 
-def gen_normal_data(n1=100,n2=100,p=2):
-    classification = np.concatenate((np.ones(n1,dtype="int32"),-1*np.ones(n2,dtype="int32"))).reshape((n1+n2,1))
-    feat_class1 = np.random.normal(loc=0.,scale=1.,size=n1*p).reshape((n1,p))
-    feat_class2 = np.random.normal(loc=1.,scale=1.,size=n2*p).reshape((n2,p))
-    features = np.vstack((feat_class1,feat_class2))
-    error_feature1  = np.ones(n1+n2).reshape((n1+n2,1))
-    error_feature2  = np.ones((n1+n2)*(p-1)).reshape((n1+n2,p-1)) / 10.0
[…]

### 2012-05-01 code/sim_data.py
added item to todo list

@@ -4,8 +4,10 @@
 ## TODO:
 ## multivariate gaussian classes
 ## error bars / interpretation of error bars
+##   - represent large test error through error bars
 ## fix plotting issue
 ## make loop more elegant
+## code up simulated data from p 431 in hastie ("skin around an orange")
 
 import numpy as np
 import matplotlib
@@ -46,8 +48,7 @@ def fake_interval(means,covs,ns):
 
 
 def unittest():
-    ## make sure we are generating normals
-    ## with correct mean and variance
+    ## qda_model
     mean = [3.0,5.0,-10.0,1.,6.]
     var = [1.3,4.0,9.0,1.,5.]
     for ii in zip(mean,var):

### 2012-05-01 code/initial_classification.R
some small updates

@@ -217,13 +217,7 @@ svm.fit.e = svm(fakedata$x,fakedata$y)
 
 
 
-################
-################ testing out svm on 
-################
 
-
-## using hastie's SVM
-library('e1071')
 
 ## if the data are not normalized, var = 1 along each dim,
 ## is there a problem with the margin concept
@@ -262,9 +256,16 @@ abline(a=(-b0 / b[2]),b=(-b[1] / b[2]),col='grey')
 ## this should be invarient to cost
 
 
-####
-#### train svm on cepheid point data
-####
+
+
+
+stop
+
+
+################
+################ testing out svm on RR lyrae data
+################
+
 
 
 

### 2012-05-01 code/initial_classification.R
test change

@@ -1,3 +1,5 @@
+## new change
+
 ########## 
 ########## 
 ########## SOME INITIAL CLASSIFICATION WORK ON LIGHTCURVES 

### 2012-05-01 code/TESTquantile_ranking.m
added quantile_ranking.m and modified test.m

@@ -1,0 +1,6 @@
+load CEPconvexInterval
+figure;imagesc(X);title('X');axis square;colorbar;
+figure;imagesc(S);title('S');axis square;colorbar;
+[X Y S] = quantile_ranking(X,Y,S);
+figure;imagesc(X);title('X normalized');axis square;colorbar;
+figure;imagesc(S);title('S normalized');axis square;colorbar;

### 2012-05-01 code/fakeData.m

@@ -1,0 +1,23 @@
+function fakeData(n,p)
+% require n to be even in order to balance the two classes.  Two standard Gaussians centered approximately at +1 and -1. Decision boundary is 0 and approximately 25% of data is on the wrong side of decision boundary.
+
+if mod(n,2)==1
+	error('n must be even in order to balance the two classes.');
+end
+u1 = .67*ones(p,1);
+u2 = .67*ones(p,1);
+X = randn(n,p);
+X(1:2:n,:) = X(1:2:n,:) + repmat(u1',n/2,1);
+X(2:2:n,:) = X(2:2:n,:) - repmat(u2',n/2,1);
+Y(1:2:n,1) = ones(n/2,1);
+Y(2:2:n,1) = -ones(n/2,1);
+S = rand(n,p);
+Params = cell(10);
+f = @(x) exp(x)-1;
+g = @(x) (x-1)/10;
+for i = 1:10
+	for j = 1:10
+		Params{i,j} = [f(g(i)) f(g(j))];
+	end
+end
+save('~/ee227a/project/fakeData','X','Y','S','n','p','Params');

### 2012-05-01 code/quantile_ranking.m

@@ -1,0 +1,19 @@
+function [X Y S] = quantile_ranking(X,Y,S)
+
+L = (X-S) / 2;
+H = (X+S) / 2;
+LH = [L;H];
+Irandom = randperm(numel(Y));
+[R Iinverse] = sort(Irandom);
+LH = LH(Irandom,:);
+for i = 1:size(LH,2)
+	[vals ranks] = sort(LH(:,i));
+	LH(:,i) = norminv(ranks / (numel(ranks)+1),0,1);
+end
+LH = LH(Iinverse,:);
+L = LH([1:(size(LH,1)/2)],:);
+H = LH([1:(size(LH,1)/2)]+size(LH,1)/2,:);
+X = (L+H) / 2;
+S = abs(L-H) / 2;
+
+

### 2012-05-01 code/test.m

@@ -1,0 +1,27 @@
+function test(iParams,model,dataset)
+
+if strcmp(dataset,'RR')
+	fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexInterval';
+	sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/';
+elseif strcmp(dataset,'RR2')
+  fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RR2convexInterval';
+  sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RR2convexInterval/';
+elseif strcmp(dataset,'CEP')
+  fname = '/home/aa/ugrad/mrogers/ee227a/project/data/CEPconvexInterval';
+  sname = '/home/aa/ugrad/mrogers/ee227a/project/results/CEPconvexInterval/';
+end
+if strcmp(model,'path')
+	params_fname = '/home/aa/ugrad/mrogers/ee227a/project/paramspath.mat';
+	sname = [sname 'path/path'];
+elseif strcmp(model,'interval')
+	params_fname = '/home/aa/ugrad/mrogers/ee227a/project/paramsinterval.mat';
+	sname = [sname 'interval/interval'];
+elseif strcmp(model,'combined')
+	params_fname = '/home/aa/ugrad/mrogers/ee227a/project/paramscombined.mat';
+	sname = [sname 'combined/combined'];
+end
+
+for i = iParams
+	getResults(fname,sname,params_fname,i,model);
+end
+

### 2012-05-01 code/testcombined.m

@@ -1,13 +1,7 @@
-function test(iParams)
+function testcombined(iParams)
 
-%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/simulated_interval';
-%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/simulated_interval/path/path';
-%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexPoint';
-%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexPoint/path/path';
-fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexInterval';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/combined/combined';
-
-
+fname = '/home/aa/ugrad/mrogers/ee227a/project/data/CEPconvexInterval';
+sname = '/home/aa/ugrad/mrogers/ee227a/project/results/CEPconvexInterval/combined/combined';
 
 params_fname = '/home/aa/ugrad/mrogers/ee227a/project/params100.mat';
 model = 'path';

### 2012-05-01 code/testinterval.m

@@ -1,11 +1,7 @@
-function test(iParams)
+function testinterval(iParams)
 
-%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/simulated_interval';
-%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/simulated_interval/path/path';
-%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexPoint';
-%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexPoint/path/path';
-fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexInterval';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/interval/interval';
+fname = '/home/aa/ugrad/mrogers/ee227a/project/data/CEPconvexInterval';
+sname = '/home/aa/ugrad/mrogers/ee227a/project/results/CEPconvexInterval/interval/interval';
 
 
 

### 2012-05-01 code/testpath.m

@@ -1,13 +1,7 @@
-function test(iParams)
+function testpath(iParams)
 
-%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/simulated_interval';
-%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/simulated_interval/path/path';
-%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexPoint';
-%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexPoint/path/path';
-%fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexInterval';
-%sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/path/path';
-fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RR2convexInterval';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RR2convexInterval/path/path';
+fname = '/home/aa/ugrad/mrogers/ee227a/project/data/CEPconvexInterval';
+sname = '/home/aa/ugrad/mrogers/ee227a/project/results/CEPconvexInterval/path/path';
 
 
 

### 2012-05-01 code/quantile_ranking.m
fixed bug in quantile_ranking.m

@@ -1,18 +1,20 @@
 function [X Y S] = quantile_ranking(X,Y,S)
 
+n = size(X,1);
+p = size(X,2);
 L = (X-S) / 2;
 H = (X+S) / 2;
 LH = [L;H];
-Irandom = randperm(numel(Y));
+Irandom = randperm(2*n);
 [R Iinverse] = sort(Irandom);
 LH = LH(Irandom,:);
-for i = 1:size(LH,2)
+for i = 1:p
 	[vals ranks] = sort(LH(:,i));
 	LH(:,i) = norminv(ranks / (numel(ranks)+1),0,1);
 end
 LH = LH(Iinverse,:);
-L = LH([1:(size(LH,1)/2)],:);
-H = LH([1:(size(LH,1)/2)]+size(LH,1)/2,:);
+L = LH([1:n],:);
+H = LH([1:n]+n,:);
 X = (L+H) / 2;
 S = abs(L-H) / 2;
 

### 2012-05-01 report/ms.tex
added a bunch to ms

@@
 The size of modern data sets requires that much of this work be automated by machine learning and statistical classifiers.
+\begin{figure}[h]
+  \begin{center}
+    \begin{includegraphics}[scale=.5]{2000.pdf}
+      \caption{Light curve of a Classical Cepheid type variable star.
+The brightness of the star is on the y-axis.
+For the top plot the brightness is plotted against time.
+This time series is periodic.
+Using fourier methods we can estimate a period of 4.51 days.
+We can convert the times from the top plot into phase ((time modulo period) / period)).
+Brightness versus phase is plotted in the bottom plot.
+Here we can observe the structure in the time series, which usually similar for stars of the same class but quite different for stars of different classes.\label{fig:cepheid}}
+    \end{includegraphics}
+  \end{center}
+\end{figure}
 
@@
 time series) of a periodic variable belonging to the class Classical Cepheid.
-The points in plot a) represent flux measurements in magnitudes (i.e.
+The points in the top plot represent flux measurements in magnitudes (i.e.
 brightness of the source) made by the telescope at particular times.
 The 0 point on the time axis is arbitrary.
-Using fourier methods, one can estimate a period from the measurements in plot a).
-Plot b) of Figure \ref{fig:cepheid} displays the flux measurements of the same object.
+Using fourier methods, one can estimate a period using these measurements.
+The lower plot of Figure \ref{fig:cepheid} displays the flux measurements of the same object.
 However here the x-axis is phase of each time measurement, computed using the estimated period of 4.51 days.
@@
 This is known as the \textit{folded light curve}.
-\begin{figure}[h]
-  \begin{center}
-    \begin{includegraphics}[scale=.5]{2000.pdf}
-      \caption{Light curve of a Classical type variable star.\label{fig:cepheid}}
-    \end{includegraphics}
-  \end{center}
-\end{figure}
 
@@
 
-In order to construct a classifier, features are \textit{extracted} from $D$ (i.e.
-take functions of $D$) that will separate sources into different classes.
+In order to construct a classifier, features are \textit{extracted} from $D_j$ (i.e.
+take functions of $D_j$) that will separate sources into different classes.
 Features vary from study to study, but typical ones include period (inverse of strongest fourier frequency), amplitude, skew, and estimates of derivatives.
@@
 \subsection{Uncertain Features}
+\begin{figure}[h]
+  \begin{center}
+    \begin{includegraphics}[scale=.5]{period_amplitude.pdf}
+      \caption{Period-Amplitude relationship for two classes: \textit{Classical Cepheid} stars and \textit{Population II Cepheid} stars.
+The green box represents (roughly) the physically possible range of periods and amplitudes.
+Clearly some of these features have been estimated incorrectly.\label{fig:period_amplitude}}
+    \end{includegraphics}
+  \end{center}
+\end{figure}
 A major problem with the standard approach is the high levels and heteroskedastic nature of the uncertainty in the features due to having poorly sampled time series ($l$ is small) or high error in the flux measurements ($e_{i}$ are systematically large).
 This leads to situations where features meant to represent physical quantities of the time series, such as amplitude or period, are incorrect.
-As an example \textbf{TODO: Include example with nice graphic here}
+As an example see Figure \ref{fig:period_amplitude}.
+This plot show the period and amplitude features for two classes of stars with a box around known physical limits for these features.
+Some of the observations have values outside these physical limits.
+
+Many of the features used for classification rely on a correct estimate of period for the object.
+For example, features related to the derivative are often computed based on the folded light curve.
+If the light curve is folded on the wrong period, then the derivative estimates are likely to be wrong.
+
+\section{Interval SVMs}
+\subsection{Constructing the Intervals from the Time Series}
+In certain applications, methods for constructing hyper-rectangles (or hyper-spheres) in feature space may be fairly straitforward.
+For example in El Ghaoui \cite{el2003robust}, the authors discuss applications to micro-array data where several replicates of some experiment are available, and a hyper-rectangle can be chosen to enclose all replicates.
+
+With astronomy data there is no clearly correct way to construct intervals around features. A few possibilities include:
+\begin{enumerate}
+\item Make width of feature interval proportional to number of measurements in time series.
+Long time series mean that features are likely to be accurate.
+For simple features, such as the standard deviation of the brightness measurements, making the interval width go down at rate $\sqrt{n}$ is grounded in probability theory.
+\item Subsample the time series and derive features for each subsample. Represent observations as intervals that contain features derived from every subsample.
+\item Heuristically put intervals around observations with features that are wrong.
+For example the amplitude of a star cannot be greater than 6 magnitudes, so any star with amplitude greater than 6, could be given an interval that contains values less than 6.
+\end{enumerate}
+
+- probably happen with any high dim problem, like image classification
+
+\begin{enumerate}
+\item sliced each light curve into 5 contiguous parts. ordering measurements in time: slice 1 is 0\% through 50\%, slice 2 is 10\% through 60\%, . . .
+\item derive features for each of these parts
+\item put the interval minimum at the lowest value of the feature for the 5 slices. put the interval max at the maximum feature value across the 5 slices
+\end{enumerate}
 
@@
 
+\begin{enumerate}
+\item problem with normalizing data
+\item how is data normalized in svms
+\end{enumerate}
+
 \bibliographystyle{plain}

### 2012-05-02 code/quantile_ranking.m
fixed quantile_ranking.m.  should work now

@@ -9,7 +9,8 @@ Irandom = randperm(2*n);
 [R Iinverse] = sort(Irandom);
 LH = LH(Irandom,:);
 for i = 1:p
-	[vals ranks] = sort(LH(:,i));
+	[R I] = sort(LH(:,i));
+	[RI ranks] = sort(I);
 	LH(:,i) = norminv(ranks / (numel(ranks)+1),0,1);
 end
 LH = LH(Iinverse,:);

### 2012-05-02 report/ms.tex

@@
 \item Make width of feature interval proportional to number of measurements in time series.
-Long time series mean that features are likely to be accurate.
-For simple features, such as the standard deviation of the brightness measurements, making the interval width go down at rate $\sqrt{n}$ is grounded in probability theory.
-\item Subsample the time series and derive features for each subsample. Represent observations as intervals that contain features derived from every subsample.
+Long time series will have small intervals around features, short time series will have wide intervals.
+For simple features, such as the standard deviation of the brightness measurements, making the interval width go down at rate $\sqrt{n}$ has a probabilistic interpretation via the central limit theorem.
+\item Subsample the time series and derive features for each subsample.
+Represent observations as hyper-rectangles that contain features derived from every subsample (or a certain fraction of the subsamples).
 \item Heuristically put intervals around observations with features that are wrong.
-For example the amplitude of a star cannot be greater than 6 magnitudes, so any star with amplitude greater than 6, could be given an interval that contains values less than 6.
+For example, the amplitude of a star cannot be greater than 6 magnitudes, so any star with amplitude greater than 6 mags could be given an interval that contains values less than 6.
 \end{enumerate}
+In this work we take the second approach.
+While the first approach is attractive for simple features, many features (such as frequency) do not have a $\sqrt{n}$ convergence to the true value.
+Further the irregular time sampling means that even simple features may not have a $\sqrt{n}$ convergence.
+The third approach involves a lot of domain knowledge and will change from application to application.
+Further, there is no guarantee that features within the range of what is physically possible are actually correct.
+By subsampling the time series and deriving features, we hope to determine this.
 
-- probably happen with any high dim problem, like image classification
-
+Figure \ref{fig:interval_construction} describes precisely how we subsample the time series and determine interval widths.
+The details of this procedure could be changed.
+For example one could bootstrap sample the time measurements.
+Certain computational considerations enter here.
+It takes around 1 second to derive features for an average length light curve.
+So sampling, say 20 times, could become prohibitively expansive if the data set is initially at the limits of what is computationally feasible.
+\begin{figure*}[ht]
+\begin{center}
+{\small
+\framebox[6in]{
+\begin{minipage}[t]{5.8in}
+% Insert here your text
+\begin{center} \textbf{Constructing Hyper-rectangles from Time Series} \end{center}
 \begin{enumerate}
-\item sliced each light curve into 5 contiguous parts. ordering measurements in time: slice 1 is 0\% through 50\%, slice 2 is 10\% through 60\%, . . .
-\item derive features for each of these parts
-\item put the interval minimum at the lowest value of the feature for the 5 slices. put the interval max at the maximum feature value across the 5 slices
+\item Order the the light curve measurements in time i.e. $\{(t_1,m_1,e_1),(t_2,m_2,e_2), \ldots , (t_l,m_l,e_l)\}$ where $t_i < t_j$ for $i < j$.
+\item Sliced each light curve into 5 contiguous sections, producing 5 time series.
+Slice 1 is $(t_i,m_i,e_i)$ for $\frac{0}{10}l \leq i \leq \frac{5}{10}l$, slice 2 is $\frac{1}{10}l \leq i \leq \frac{6}{10}l$, ect.
+%% \begin{enumerate}
+%% \item $\{(t_1,m_1,e_1), \ldots , (t_{l/2},m_{l/2},e_{l/2})\}$
+%% \item $\{(t_1,m_1,e_1),(t_2,m_2,e_2), \ldots , (t_l,m_l,e_l)\}$
+%% \end{enumerate}
+\item Derive features for each of these slices.
+\item Put the interval minimum at the lowest value of the feature for the 5 slices. Put the interval max at the maximum feature value across the 5 slices.
 \end{enumerate}
+\end{minipage}
+}
+}
+\end{center}
+\caption{Description of interval construction algorithm.\label{fig:interval_construction}}
+\label{lb}
+\end{figure*}
 

### 2012-05-02 code/TESTcollectResults.m
cleaned up a bunch of files, deleted old ones.  should be more intuitive to use now.

@@ -1,17 +1,0 @@
-model = 'path';
-fname_prefix = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/path/path_';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/summary/path';
-collectResults(model,fname_prefix,sname);
-load(sname);
-Lambda = 0:.1:9.9;
-figure;plot(Lambda,results);title('model: path, data: RR');xlabel('lambda');ylabel('loss');
-
-model = 'interval';
-fname_prefix = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/interval/interval_';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/summary/interval';
-collectResults(model,fname_prefix,sname);
-load(sname);
-Rho = 0:.1:9.9;
-figure;plot(Rho,results);title('model: interval, data: RR');xlabel('rho');ylabel('loss');
-
-

### 2012-05-02 code/TESTquantile_ranking.m

@@ -1,6 +1,0 @@
-load CEPconvexInterval
-figure;imagesc(X);title('X');axis square;colorbar;
-figure;imagesc(S);title('S');axis square;colorbar;
-[X Y S] = quantile_ranking(X,Y,S);
-figure;imagesc(X);title('X normalized');axis square;colorbar;
-figure;imagesc(S);title('S normalized');axis square;colorbar;

### 2012-05-02 code/collectResults.m

@@ -1,4 +1,14 @@
-function collectResults(model,fname_prefix,sname)
+function collectResults(fname_prefix,sname,params_fname,name_of_dataset)
+% collectResults.m stores all losses computed by computeResults.m in a matrix and plots them.
+%
+% INPUTS
+% fname_prefix: filename prefix.  All result files are of the form fname_prefix_index.mat
+% sname[DO NOT GIVE AN EXTENSION]: file to store matrix of results.  also the name of the plot files.
+% params_fname: name of file where parameters are stored.
+% name_of_dataset: name of dataset analyzed, which is used to label plots
+
+
+% do not give sname an extension.
 if strcmp(fname_prefix(numel(fname_prefix)),'/')
 	fname_prefix = fname_prefix(1:(numel(fname_prefix)-1));
 end
@@ -7,21 +17,38 @@ dname = fname_prefix;
 while ~strcmp(dname(numel(dname)),'/')
 	dname = dname(1:(numel(dname)-1));
 end
-if strcmp(model,'path')
-	load('/home/aa/ugrad/mrogers/ee227a/project/paramspath')
-	results = zeros(size(Params));	
-elseif strcmp(model,'interval')
-	load('/home/aa/ugrad/mrogers/ee227a/project/paramsinterval')
-	results = zeros(size(Params));
-elseif strcmp(model,'combined')
-	load('/home/aa/ugrad/mrogers/ee227a/project/paramscombined')
-	results = zeros(size(Params));
-end
-save(sname,'results');
-load(sname); % has results variable in it, a table of loss values
+load(params_fname);
+results = zeros(size(Params));
 for i = 1:numel(d)
 	load([dname d(i).name]);
 	iParam
 	results(iParam) = loss;
 end
-save(sname,'results');
+save([sname '.mat'],'results','Lambda','Rho');
+if ismember(0,Rho)
+	i = find(Rho==0);
+	f=figure('units','normalized','outerposition',[0 0 1 1],'visible','off');
+	plot(Lambda,results(:,i));
+	title(['standard SVM applied to ' name_of_dataset]);
+	xlabel('lambda');
+	ylabel('loss');
+	saveas(f,[sname '_standard.png']);
+end
+if ismember(0,Lambda)
+	i = find(Lambda==0);
+	f=figure('units','normalized','outerposition',[0 0 1 1],'visible','off');
+	plot(Rho,results(:,i));
[…]

### 2012-05-02 code/collectResults2.m

@@ -1,46 +1,0 @@
-model = 'path';
-fname_prefix = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/path/path_';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/summary/path';
-collectResults(model,fname_prefix,sname)
-
-model = 'interval';
-fname_prefix = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/interval/interval_';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/summary/interval';
-collectResults(model,fname_prefix,sname)
-
-model = 'combined';
-fname_prefix = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/combined/combined_';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/summary/combined';
-collectResults(model,fname_prefix,sname)
-
-model = 'path';
-fname_prefix = '/home/aa/ugrad/mrogers/ee227a/project/results/RR2convexInterval/path/path_';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RR2convexInterval/summary/path';
-collectResults(model,fname_prefix,sname)
-
-model = 'interval';
-fname_prefix = '/home/aa/ugrad/mrogers/ee227a/project/results/RR2convexInterval/interval/interval_';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RR2convexInterval/summary/interval';
-collectResults(model,fname_prefix,sname)
-
-model = 'combined';
-fname_prefix = '/home/aa/ugrad/mrogers/ee227a/project/results/RR2convexInterval/combined/combined_';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RR2convexInterval/summary/combined';
-collectResults(model,fname_prefix,sname)
-
-model = 'path';
-fname_prefix = '/home/aa/ugrad/mrogers/ee227a/project/results/CEPconvexInterval/path/path_';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/CEPconvexInterval/summary/path';
-collectResults(model,fname_prefix,sname)
-
-model = 'interval';
-fname_prefix = '/home/aa/ugrad/mrogers/ee227a/project/results/CEPconvexInterval/interval/interval_';
[…]

### 2012-05-02 code/computeResults.m

@@ -1,0 +1,48 @@
+function computeResults(fname,sname_prefix,params_fname,iParam)
+% computeResults.m computes the loss of the SVM interval classifier when applied to data in fname. The result is stored in sname_prefix_iParam.mat, the parameters are loaded from params_fname, and iParam is the index of the cell array Params, located in params_fname, to use.
+
+load(fname);
+cv_split = .1;
+num_cv_splits = 1/cv_split;
+load(params_fname);
+lambda = Params{iParam}(1);
+rho = Params{iParam}(2);
+if ~exist('S')
+	S = zeros(size(X));
+end
+
+
+% normalize data via quantile ranking
+[X Y S] = quantile_ranking(X,Y,S);
+
+% if multiclass data, then choose the two classes with the most datapoints
+class_indices = 1:max(Y);
+class_freqs = zeros(size(class_indices));
+for i = class_indices
+	class_freqs(i) = numel(find(Y==i));
+end
+[temp class_indices] = sort(class_freqs,'descend');
+index_of_first_class = class_indices(1);
+index_of_second_class = class_indices(2);
+I1 = find(Y==index_of_first_class);
+I2 = find(Y==index_of_second_class);
+I1 = I1(1:numel(I2));
+Y1 = Y(I1) ./ Y(I1) * (1);
+Y2 = Y(I2) ./ Y(I2) * (-1);
+X1 = X(I1,:);
+X2 = X(I2,:);
+S1 = S(I1,:);
+S2 = S(I2,:);
+X = [X1;X2];
+Y = [Y1;Y2];
+S = [S1;S2];
+valid_feature_indices = zeros(1,size(X,2));
+for i = 1:size(X,2)
+	valid_feature_indices(i) = all(~isnan(X(:,i)));
+end
+valid_feature_indices = logical(valid_feature_indices);
+X = X(:,valid_feature_indices);
+S = S(:,valid_feature_indices);
+loss = xval(X,Y,S,lambda,rho,cv_split,num_cv_splits);
+save([sname_prefix '_'  num2str(iParam,'%03d') '.mat'],'lambda','rho','loss','iParam');
+

### 2012-05-02 code/getParams.m

@@ -6,4 +6,4 @@ for i = 1:numel(Lambda)
 		Params{i,j} = [Lambda(i) Rho(j)];
 	end
 end
-save(sname,'Params')
+save(sname,'Params','Lambda','Rho')

### 2012-05-02 code/svm.m

@@ -1,9 +1,8 @@
-function loss = svm(model,XTr,YTr,XTe,YTe,lambda,rho,S)
+function loss = svm(XTr,YTr,XTe,YTe,lambda,rho,S)
 % if argument is unused, just pass []. Loss function used: sign(y(i) * f(x(i)))
 %
 % INPUTS
 % 
-% model = 'path', 'interval', or 'combined': indicates model to use
 % XTr = [n x p]: training data with n points and p features
 % YTr = [n x 1]: training labels.  Each entry in {-1,1}.
 % XTe = [n' x p]: test data
@@ -16,39 +15,17 @@ function loss = svm(model,XTr,YTr,XTe,YTe,lambda,rho,S)
 %
 % loss = scalar: loss
 
-% estimate beta, beta0, xi
+% estimate b, b0, xi
 [n p] = size(XTr);
-if strcmp(model,'path')
-	cvx_begin
-		variable b(p);
-		variable b0(1);
-		variable xi(n);
-		minimize(xi'*ones(n,1) + lambda/2*b'*b)
-		subject to
-			ones(n,1) - YTr .* (b0+XTr*b) <= xi;
-			xi >= 0;
-	cvx_end
-elseif strcmp(model,'interval')
-	cvx_begin
-		variable b(p);
-		variable b0(1);
-		variable xi(n);
-		minimize(xi'*ones(n,1))
-		subject to
-			YTr .* (XTr*b + b0) >= 1 - xi + rho*S*abs(b);
-			xi >= 0;
-	cvx_end
-elseif strcmp(model,'combined')
-	cvx_begin
-		variable b(p);
-		variable b0(1);
-		variable xi(n);
-		minimize(xi'*ones(n,1) + lambda/2*b'*b)
-		subject to
-			xi >= 1 - YTr .* (b0 + XTr*b) + rho*S*abs(b);
-			xi >= 0;
-	cvx_end
-end
+cvx_begin
+	variable b(p);
+	variable b0(1);
+	variable xi(n);
+	minimize(xi'*ones(n,1) + lambda/2*b'*b)
+	subject to
+		xi >= 1 - YTr .* (b0 + XTr*b) + rho*S*abs(b);
+		xi >= 0;
+cvx_end
 
 % compute loss l
 f = @(x) b0 + x'*b;

### 2012-05-02 code/test.m

@@ -1,27 +1,9 @@
-function test(iParams,model,dataset)
+function test(iParams)
+% test.m computes the results of applying the SVM interval classifier data in sname.  The results are stored in sname and the parameters are loaded from params_fname. iParams is a vector of indices which indicates which (lambda,rho) pairs of the cell array Params in params_fname to use.  Note that for each index i of iParam, the corresponding save name is sname_prefix_i.mat.
 
-if strcmp(dataset,'RR')
-	fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexInterval';
-	sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval/';
-elseif strcmp(dataset,'RR2')
-  fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RR2convexInterval';
-  sname = '/home/aa/ugrad/mrogers/ee227a/project/results/RR2convexInterval/';
-elseif strcmp(dataset,'CEP')
-  fname = '/home/aa/ugrad/mrogers/ee227a/project/data/CEPconvexInterval';
-  sname = '/home/aa/ugrad/mrogers/ee227a/project/results/CEPconvexInterval/';
-end
-if strcmp(model,'path')
-	params_fname = '/home/aa/ugrad/mrogers/ee227a/project/paramspath.mat';
-	sname = [sname 'path/path'];
-elseif strcmp(model,'interval')
-	params_fname = '/home/aa/ugrad/mrogers/ee227a/project/paramsinterval.mat';
-	sname = [sname 'interval/interval'];
-elseif strcmp(model,'combined')
-	params_fname = '/home/aa/ugrad/mrogers/ee227a/project/paramscombined.mat';
-	sname = [sname 'combined/combined'];
-end
-
+fname = '/home/aa/ugrad/mrogers/ee227a/project/data/RRconvexInterval.mat'; % filename where the data is stored
+sname_prefix = '/home/aa/ugrad/mrogers/ee227a/project/results/RRconvexInterval'; % prefix of the filename where the data will be saved
+params_fname = '/home/aa/ugrad/mrogers/ee227a/project/params.mat'; % where parameters are saved
 for i = iParams
-	getResults(fname,sname,params_fname,i,model);
+	computeResults(fname,sname_prefix,params_fname,i);
 end
-

### 2012-05-02 code/testcombined.m

@@ -1,11 +1,0 @@
-function testcombined(iParams)
-
-fname = '/home/aa/ugrad/mrogers/ee227a/project/data/CEPconvexInterval';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/CEPconvexInterval/combined/combined';
-
-params_fname = '/home/aa/ugrad/mrogers/ee227a/project/params100.mat';
-model = 'path';
-for i = iParams
-	getResults(fname,sname,params_fname,i,model);
-end
-

### 2012-05-02 code/testinterval.m

@@ -1,13 +1,0 @@
-function testinterval(iParams)
-
-fname = '/home/aa/ugrad/mrogers/ee227a/project/data/CEPconvexInterval';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/CEPconvexInterval/interval/interval';
-
-
-
-params_fname = '/home/aa/ugrad/mrogers/ee227a/project/params100.mat';
-model = 'path';
-for i = iParams
-	getResults(fname,sname,params_fname,i,model);
-end
-

### 2012-05-02 code/testpath.m

@@ -1,13 +1,0 @@
-function testpath(iParams)
-
-fname = '/home/aa/ugrad/mrogers/ee227a/project/data/CEPconvexInterval';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/CEPconvexInterval/path/path';
-
-
-
-params_fname = '/home/aa/ugrad/mrogers/ee227a/project/params100.mat';
-model = 'path';
-for i = iParams
-	getResults(fname,sname,params_fname,i,model);
-end
-

### 2012-05-02 code/xval.m

@@ -1,10 +1,11 @@
-function loss = xval(X,Y,S,model,lambda,rho,cv_split,num_cv_splits,random_splits)
+function loss = xval(X,Y,S,lambda,rho,cv_split,num_cv_splits)
 % cross-validation
 %
 % X = [n x p]: Data
 % Y = [n x 1]: Labels. Each entry in {-1,1}.
-% S = [n x p]: confidence intervals. 
-% L = {num_cv_splits x 1}: cell array containing triples [lambda,rho,loss]
+% S = [n x p]: confidence intervals.
+% lambda: regularization parameter
+% rho: global uncertainty parameter
 % cv_split: fraction of data to be tested on. To train on 75% of the data, for example, let cv_split = .75; to perform leave-one-out cross-validation, let cv_split = 1/n and num_cv_splits = n.
 % num_cv_splits: number of times to run cross validation on random splits
 
@@ -12,46 +13,34 @@ loss = 0;
 n = size(X,1);
 
 % preprocess data so that labels are evenly distributed
-if ~random_splits
-	I1 = Y==Y(1);
-	I2 = Y~=Y(1);
-	X1 = X(I1,:);
-	X2 = X(I2,:);
-	Y1 = Y(I1);
-	Y2 = Y(I2);
-	S1 = S(I1,:);
-	S2 = S(I2,:);
-	X(1:2:n,:) = X1;
-	X(2:2:n,:) = X2;
-	Y(1:2:n,1) = Y1;
-	Y(2:2:n,1) = Y2;
-	S(1:2:n,:) = S1;
-	S(2:2:n,:) = S2;
-end
+I1 = Y==Y(1);
+I2 = Y~=Y(1);
+X1 = X(I1,:);
+X2 = X(I2,:);
+Y1 = Y(I1);
+Y2 = Y(I2);
+S1 = S(I1,:);
+S2 = S(I2,:);
+X(1:2:n,:) = X1;
+X(2:2:n,:) = X2;
+Y(1:2:n,1) = Y1;
+Y(2:2:n,1) = Y2;
+S(1:2:n,:) = S1;
+S(2:2:n,:) = S2;
 
 for i = 1:num_cv_splits
+
+	% construct training and test data and labels
 	nTe = floor(n*cv_split);
 	nTr = n-nTe;
-	
[…]

### 2012-05-03 code/james/Rfunctions.R
made james folder in data to keep all my files, better organization

@@ -1,0 +1,114 @@
+## useful R functions
+## by James Long
+## date: April 1, 2012
+
+
+## plot a single light curve
+plotLightCurve = function(tfe,xLabel="Time (Days)",yLabel="m",maintitle="A Lightcurve",
+                          sd.errors=1,width.error.bar=1,cex=.5,reverse=TRUE,
+                          point.colors=FALSE,plot.errors=TRUE){
+  if(class(point.colors) == "logical"){
+    if(!point.colors){
+      point.colors = 1
+    }
+    else {    
+      point.colors = rainbow(nrow(tfe))
+    }
+  }
+  
+  tfe[,2] = -1*tfe[,2]
+  # if there is no main title make the margin at the top very small
+  if(maintitle == "") { par(mar=c(5.1,4.1,1,2.1)) }
+
+  # set the width of the error bars
+  xmin = min(tfe[,1])
+  xmax = max(tfe[,1])
+  ymin = min(tfe[,2] - sd.errors * tfe[,3])
+  ymax = max(tfe[,2] + sd.errors * tfe[,3])
+
+  # set the width of the error bar relative to x-axis
+  width.error.bar = width.error.bar * (xmax - xmin) / 300
+  # set up the plot to the get right dimensions
+  plot(c(xmin,xmax),c(ymin,ymax),col=0,
+       main=maintitle,xlab=xLabel,ylab=yLabel,yaxt='n',
+       cex.lab=1)
+  if(!reverse) {   axis(2) }
+  else {
+    yaxis = (ymax - ymin) * (0:4) / 4 + ymin
+    axis(2,at=yaxis,labels=-round(yaxis,1),las=2,cex.lab=1)
+  }
+  ## draw the error bars
+  if(plot.errors){
+    segments(tfe[,1],tfe[,2] - sd.errors*tfe[,3],tfe[,1],tfe[,2] + sd.errors*tfe[,3],point.colors)
+    segments(tfe[,1]-width.error.bar,tfe[,2] + sd.errors*tfe[,3],tfe[,1] + width.error.bar,tfe[,2] + sd.errors*tfe[,3],point.colors)
+    segments(tfe[,1]-width.error.bar,tfe[,2] - sd.errors*tfe[,3],tfe[,1] + width.error.bar,tfe[,2] - sd.errors*tfe[,3],point.colors)
+  }
+  # put the points on the plot
+  points(tfe[,1],tfe[,2],pch=19,cex=cex,col=point.colors)
+}
+
+
+
+
+
+
+
+###
[…]

### 2012-05-03 code/james/initial_classification.R

@@ -1,0 +1,295 @@
+## new change
+
+########## 
+########## 
+########## SOME INITIAL CLASSIFICATION WORK ON LIGHTCURVES 
+##########  
+##########
+########## by James Long 
+########## date: April 1, 2012 
+########## 
+
+
+## program setup
+rm(list=ls(all=TRUE))
+set.seed(22071985)
+options(width=50)
+
+## load source files
+source('Rfunctions.R')
+
+## load packages
+library('R.matlab')
+library('randomForest')
+library('rpart')
+
+## get the data
+data1_file = "../data/RR2convexMeta.dat"
+point_file = '../data/RR2convexPoint.dat'
+interval_file = '../data/RR2convexInterval.dat'
+tfe = '../data/RR2convexTfe.dat'
+dataPoint = read.table(point_file,sep=';',header=TRUE)
+dataInterval = read.table(interval_file,sep=';',header=TRUE)
+time_flux = read.table(tfe,sep=';',header=TRUE)
+data1 = read.table(data1_file,sep=";",header=TRUE)
+
+
+## density of points
+originals = (data1$features.source_id == data1$sources.original_source_id)
+sum(originals)
+d1 = density(data1$features.n_points[originals])
+plot(d1)
+
+
+##
+# 1. what kernel did joey use
+# 2. set up a small/hard two class problem
+# 3. figure out how kernels play in
+# 4. come up with realistic simulated data set
+# 5. lambda versus rho plot for loss on simulated and astro
+
+### densities of errors
+densities = aggregate(time_flux$error,by=list(time_flux$source_id),density,simplify=FALSE)
+class(densities)
+plot(c(.01,.06),c(0,200),col=0,xlab="Std. Dev.",ylab="Density")
+j = 100
+for(i in 1:j){
+  if(densities[i,2][[1]]$n > 40){
+    lines(densities[i,2][[1]])
+  }
+}
+
+class(densities[1])
+class(densities[1])
+
+## plotting functionality
+i = 0
+i = i + 1
+
+
+
+source('Rfunctions.R')
+
+
+pdf(paste(i,".pdf",sep=""))
+source_to_plot = dataPoint$source_id[i]
+DrawThreeLightCurves(source_to_plot,dataPoint,time_flux,
+                     plot.folded.twice=FALSE,
+                     smoother=TRUE)
+dev.off()
+
+
+
+
+
[…]

### 2012-05-03 code/james/make_easy.R

@@ -1,0 +1,42 @@
+########## 
+########## 
+########## CONVERT INTERVAL DATA INTO EASY FORM 
+##########  
+##########
+########## by James Long 
+########## date: April 29, 2012 
+########## 
+
+
+convert_to_easy_format = function(input,output){
+  dataInterval = read.table(input,sep=';',header=TRUE)
+  nrow(dataInterval)
+  feat_names = names(dataInterval)[1:(length(dataInterval)-2)]
+  feat_names = substr(feat_names,1,nchar(feat_names)-1)
+  feat_names = unique(feat_names)
+  nrow(feat_names)
+  classification = rep(1,nrow(dataInterval))
+  class2 = levels(dataInterval$classification)[2]
+  classification[dataInterval$classification==class2] = -1
+
+
+  ## construct data matrix to output
+  datamatrix = matrix(0,nrow=nrow(dataInterval),
+    ncol=2*length(feat_names)+1)
+  datamatrix[,1] = classification
+  cnames = names(dataInterval)
+  cnames = substr(cnames,1,nchar(cnames)-1)
+  for(i in 1:length(feat_names)){
+    temp = dataInterval[,cnames %in% feat_names[i]]
+    center = rowSums(temp) / 2
+    width = abs(temp[,1] - temp[,2]) / 2
+    datamatrix[,(i+1)] = center
+    datamatrix[,(length(feat_names)+i+1)] = width
+  }
+  head(datamatrix)
+  write.table(datamatrix,file=output,row.names=FALSE,
+              col.names=FALSE)
+}
+
+
+

### 2012-05-03 code/james/plots.R

@@ -1,0 +1,78 @@
+########## 
+########## 
+########## PLOTS FOR FINAL REPORT 
+##########  
+##########
+########## by James Long 
+########## date:  May 1, 2012
+########## 
+
+
+
+
+
+
+#####
+##### show that RR lyrae periods are sometimes wrong
+#####
+
+
+## load packages
+data1_file = "../data/CEPconvexMeta.dat"
+point_file = '../data/CEPconvexPoint.dat'
+interval_file = '../data/CEPconvexInterval.dat'
+tfe = '../data/CEPconvexTfe.dat'
+dataPoint = read.table(point_file,sep=';',header=TRUE)
+dataInterval = read.table(interval_file,sep=';',header=TRUE)
+time_flux = read.table(tfe,sep=';',header=TRUE)
+data1 = read.table(data1_file,sep=";",header=TRUE)
+
+ordering = sample(1:nrow(dataPoint),nrow(dataPoint))
+dataPoint = dataPoint[ordering,]
+
+int_classes = rep(1,nrow(dataPoint))
+int_classes[dataPoint$classification==levels(dataPoint$classification)[2]] = 2
+coloring = c("orange","blue")
+pchs = c(1,2)
+
+pdf('../report/period_amplitude.pdf')
+plot(log(dataPoint$amplitude,base=10),
+     log(1/dataPoint$freq1_harmonics_freq_0,base=10),
+     col=coloring[int_classes],
+     pch=pchs[int_classes],
+     lwd=2,
+     xlab="log(amplitude)",
+     ylab="log(period)",
+     main="Period-Amplitude Relationship for Two Star Classes")
+rect(-1,0,0,2,border="green",lwd=2)
+legend("topleft",levels(dataPoint$classification),
+       col=coloring,pch=pchs,lwd=2)
+dev.off()
+## 2 > log(period) > 0
+## 0 > log(amplidue) > -1
+
+
+
+source('Rfunctions.R')
+
+
+pdf(paste(i,".pdf",sep=""))
+source_to_plot = dataPoint$source_id[i]
+DrawThreeLightCurves(source_to_plot,dataPoint,time_flux,
+                     plot.folded.twice=FALSE,
+                     smoother=TRUE)
+dev.off()
+
+
+
+
+meanfreq =  (dataInterval$freq1_harmonics_freq_0U + dataInterval$freq1_harmonics_freq_0L) / 2
+meanamp = (dataInterval$amplitudeU + dataInterval$amplitudeL)/2
+meanamp
[…]

### 2012-05-03 code/james/sim_data.py

@@ -1,0 +1,91 @@
+## two classes normal, with a lot of error on 1
+## test add
+
+## TODO:
+## multivariate gaussian classes
+## error bars / interpretation of error bars
+##   - represent large test error through error bars
+## fix plotting issue
+## make loop more elegant
+## code up simulated data from p 431 in hastie ("skin around an orange")
+
+import numpy as np
+import matplotlib
+from matplotlib import pyplot as plt
+
+def qda_model(means,covs,ns):
+    ''' generate classification data, multivariate gaussian '''
+    d, p = means.shape
+    ## error check for dimensions of entries
+    if covs.shape != (d,p,p):
+        print "means is " + repr(d) + " x " + repr(p) + ", covs must be " + repr(d) \
+            + " x " + repr(p) + " x " + repr(p)
+        return 0
+    if ns.shape != (d,):
+        print "means is " + repr(d) + " x " + repr(p) + ", ns must be " + repr(d)
+        return 0
+    ## now populate the feature matrix
+    features = np.ndarray((ns.sum(),p))
+    jj = 0
+    for ii in range(d):
+        features[jj:(ns[ii] + jj),:] = \
+            np.random.multivariate_normal(mean=means[ii,:],cov=covs[ii,:,:],size=ns[ii])
+        jj += ns[ii]
+
+    ## create class labels and return
+    classification = np.repeat(range(ns.size),ns).reshape((ns.sum(),1))
+    data = np.hstack((classification,features))
+    return data
+
+def fake_interval(means,covs,ns):
+    ''' generates gaussian data and add interval of width 0.
+    useful for testing interval svm code '''
+    data = qda_model(means,covs,ns)
+    n, p = data.shape
+    intervals = np.zeros(p*n).reshape((n,p))
+    data = np.hstack((data,intervals))
+    return data
+
+
+def unittest():
+    ## qda_model
+    mean = [3.0,5.0,-10.0,1.,6.]
+    var = [1.3,4.0,9.0,1.,5.]
+    for ii in zip(mean,var):
+        means = np.array([ii[0]]).reshape((1,1))
+        covs = np.array([ii[1]]).reshape((1,1))
+        covs = np.array([covs])
+        ns = np.array([1000])
+        data = qda_model(means,covs,ns)
+        print data
+        print data[:,1].mean()
[…]

### 2012-05-03 code/Rfunctions.R
deleted a bunch of files from code, actually they were moved from code/ to code/james, but due to poor git skills, they look like new files in code/james. so if you want to figure out how make_easy.R in data/ has changed, look at make_easy.R in data/james. same for other files that were 'deleted' here

@@ -1,114 +1,0 @@
-## useful R functions
-## by James Long
-## date: April 1, 2012
-
-
-## plot a single light curve
-plotLightCurve = function(tfe,xLabel="Time (Days)",yLabel="m",maintitle="A Lightcurve",
-                          sd.errors=1,width.error.bar=1,cex=.5,reverse=TRUE,
-                          point.colors=FALSE,plot.errors=TRUE){
-  if(class(point.colors) == "logical"){
-    if(!point.colors){
-      point.colors = 1
-    }
-    else {    
-      point.colors = rainbow(nrow(tfe))
-    }
-  }
-  
-  tfe[,2] = -1*tfe[,2]
-  # if there is no main title make the margin at the top very small
-  if(maintitle == "") { par(mar=c(5.1,4.1,1,2.1)) }
-
-  # set the width of the error bars
-  xmin = min(tfe[,1])
-  xmax = max(tfe[,1])
-  ymin = min(tfe[,2] - sd.errors * tfe[,3])
-  ymax = max(tfe[,2] + sd.errors * tfe[,3])
-
-  # set the width of the error bar relative to x-axis
-  width.error.bar = width.error.bar * (xmax - xmin) / 300
-  # set up the plot to the get right dimensions
-  plot(c(xmin,xmax),c(ymin,ymax),col=0,
-       main=maintitle,xlab=xLabel,ylab=yLabel,yaxt='n',
-       cex.lab=1)
-  if(!reverse) {   axis(2) }
-  else {
-    yaxis = (ymax - ymin) * (0:4) / 4 + ymin
-    axis(2,at=yaxis,labels=-round(yaxis,1),las=2,cex.lab=1)
-  }
-  ## draw the error bars
-  if(plot.errors){
-    segments(tfe[,1],tfe[,2] - sd.errors*tfe[,3],tfe[,1],tfe[,2] + sd.errors*tfe[,3],point.colors)
-    segments(tfe[,1]-width.error.bar,tfe[,2] + sd.errors*tfe[,3],tfe[,1] + width.error.bar,tfe[,2] + sd.errors*tfe[,3],point.colors)
-    segments(tfe[,1]-width.error.bar,tfe[,2] - sd.errors*tfe[,3],tfe[,1] + width.error.bar,tfe[,2] - sd.errors*tfe[,3],point.colors)
-  }
-  # put the points on the plot
-  points(tfe[,1],tfe[,2],pch=19,cex=cex,col=point.colors)
-}
-
-
-
-
-
-
-
-###
[…]

### 2012-05-03 code/initial_classification.R

@@ -1,294 +1,0 @@
-## new change
-
-########## 
-########## 
-########## SOME INITIAL CLASSIFICATION WORK ON LIGHTCURVES 
-##########  
-##########
-########## by James Long 
-########## date: April 1, 2012 
-########## 
-
-
-## program setup
-rm(list=ls(all=TRUE))
-set.seed(22071985)
-options(width=50)
-
-## load source files
-source('Rfunctions.R')
-
-## load packages
-library('randomForest')
-library('rpart')
-
-## get the data
-data1_file = "../data/RR2convexMeta.dat"
-point_file = '../data/RR2convexPoint.dat'
-interval_file = '../data/RR2convexInterval.dat'
-tfe = '../data/RR2convexTfe.dat'
-dataPoint = read.table(point_file,sep=';',header=TRUE)
-dataInterval = read.table(interval_file,sep=';',header=TRUE)
-time_flux = read.table(tfe,sep=';',header=TRUE)
-data1 = read.table(data1_file,sep=";",header=TRUE)
-
-
-## density of points
-originals = (data1$features.source_id == data1$sources.original_source_id)
-sum(originals)
-d1 = density(data1$features.n_points[originals])
-plot(d1)
-
-
-##
-# 1. what kernel did joey use
-# 2. set up a small/hard two class problem
-# 3. figure out how kernels play in
-# 4. come up with realistic simulated data set
-# 5. lambda versus rho plot for loss on simulated and astro
-
-### densities of errors
-densities = aggregate(time_flux$error,by=list(time_flux$source_id),density,simplify=FALSE)
-class(densities)
-plot(c(.01,.06),c(0,200),col=0,xlab="Std. Dev.",ylab="Density")
-j = 100
-for(i in 1:j){
-  if(densities[i,2][[1]]$n > 40){
-    lines(densities[i,2][[1]])
-  }
-}
-
-class(densities[1])
-class(densities[1])
-
-## plotting functionality
-i = 0
-i = i + 1
-
-
-
-source('Rfunctions.R')
-
-
-pdf(paste(i,".pdf",sep=""))
-source_to_plot = dataPoint$source_id[i]
-DrawThreeLightCurves(source_to_plot,dataPoint,time_flux,
-                     plot.folded.twice=FALSE,
-                     smoother=TRUE)
-dev.off()
-
-
-
-
-
[…]

### 2012-05-03 code/make_easy.R

@@ -1,42 +1,0 @@
-########## 
-########## 
-########## CONVERT INTERVAL DATA INTO EASY FORM 
-##########  
-##########
-########## by James Long 
-########## date: April 29, 2012 
-########## 
-
-
-convert_to_easy_format = function(input,output){
-  dataInterval = read.table(input,sep=';',header=TRUE)
-  nrow(dataInterval)
-  feat_names = names(dataInterval)[1:(length(dataInterval)-2)]
-  feat_names = substr(feat_names,1,nchar(feat_names)-1)
-  feat_names = unique(feat_names)
-  nrow(feat_names)
-  classification = rep(1,nrow(dataInterval))
-  class2 = levels(dataInterval$classification)[2]
-  classification[dataInterval$classification==class2] = -1
-
-
-  ## construct data matrix to output
-  datamatrix = matrix(0,nrow=nrow(dataInterval),
-    ncol=2*length(feat_names)+1)
-  datamatrix[,1] = classification
-  cnames = names(dataInterval)
-  cnames = substr(cnames,1,nchar(cnames)-1)
-  for(i in 1:length(feat_names)){
-    temp = dataInterval[,cnames %in% feat_names[i]]
-    center = rowSums(temp) / 2
-    width = abs(temp[,1] - temp[,2]) / 2
-    datamatrix[,(i+1)] = center
-    datamatrix[,(length(feat_names)+i+1)] = width
-  }
-  head(datamatrix)
-  write.table(datamatrix,file=output,row.names=FALSE,
-              col.names=FALSE)
-}
-
-
-

### 2012-05-03 code/sim_data.py

@@ -1,91 +1,0 @@
-## two classes normal, with a lot of error on 1
-## test add
-
-## TODO:
-## multivariate gaussian classes
-## error bars / interpretation of error bars
-##   - represent large test error through error bars
-## fix plotting issue
-## make loop more elegant
-## code up simulated data from p 431 in hastie ("skin around an orange")
-
-import numpy as np
-import matplotlib
-from matplotlib import pyplot as plt
-
-def qda_model(means,covs,ns):
-    ''' generate classification data, multivariate gaussian '''
-    d, p = means.shape
-    ## error check for dimensions of entries
-    if covs.shape != (d,p,p):
-        print "means is " + repr(d) + " x " + repr(p) + ", covs must be " + repr(d) \
-            + " x " + repr(p) + " x " + repr(p)
-        return 0
-    if ns.shape != (d,):
-        print "means is " + repr(d) + " x " + repr(p) + ", ns must be " + repr(d)
-        return 0
-    ## now populate the feature matrix
-    features = np.ndarray((ns.sum(),p))
-    jj = 0
-    for ii in range(d):
-        features[jj:(ns[ii] + jj),:] = \
-            np.random.multivariate_normal(mean=means[ii,:],cov=covs[ii,:,:],size=ns[ii])
-        jj += ns[ii]
-
-    ## create class labels and return
-    classification = np.repeat(range(ns.size),ns).reshape((ns.sum(),1))
-    data = np.hstack((classification,features))
-    return data
-
-def fake_interval(means,covs,ns):
-    ''' generates gaussian data and add interval of width 0.
-    useful for testing interval svm code '''
-    data = qda_model(means,covs,ns)
-    n, p = data.shape
-    intervals = np.zeros(p*n).reshape((n,p))
-    data = np.hstack((data,intervals))
-    return data
-
-
-def unittest():
-    ## qda_model
-    mean = [3.0,5.0,-10.0,1.,6.]
-    var = [1.3,4.0,9.0,1.,5.]
-    for ii in zip(mean,var):
-        means = np.array([ii[0]]).reshape((1,1))
-        covs = np.array([ii[1]]).reshape((1,1))
-        covs = np.array([covs])
-        ns = np.array([1000])
-        data = qda_model(means,covs,ns)
-        print data
-        print data[:,1].mean()
[…]

### 2012-05-03 code/svm_in_R.R

@@ -1,41 +1,0 @@
-####
-#### get CV error rates for R svm
-####
-library('e1071')
-library('randomForest')
-
-
-## get the data
-data1 = read.table("../data/CEPeasy")
-datamatrix = as.matrix(data1)
-p = (ncol(datamatrix)-1)/2
-y = as.factor(datamatrix[,1])
-x = datamatrix[,2:(p+1)]
-x = x[,apply(x,2,var)!=0]
-
-## get cv error as a function of tuning parameter
-nsplits = 10
-costs = 1:10
-nums = (rep((1:nsplits),ceiling(nrow(x) / nsplits)))[1:nrow(x)]
-cvs = sample(nums,length(nums))
-results = matrix(0,nrow=length(costs),ncol=nsplits)
-
-for(ii in 1:ncol(results)){
-    trainx = x[cvs!=ii,]
-    trainy = y[cvs!=ii]
-    testx = x[cvs==ii,]
-    testy = y[cvs==ii]
-    for(jj in 1:nrow(results)){
-      svm.fit.e =  svm(trainx,trainy,kernel="linear",
-        cost=costs[jj])
-      predictions = predict(svm.fit.e,testx)
-      results[jj,ii] = mean(predictions != testy)
-    }
-}
-mar_means = rowMeans(results)
-plot(costs,mar_means)
-
-
-## what does random forest do?
-rf.fit = randomForest(x,y)
-rf.fit

### 2012-05-03 report/ms.tex
updated ms a bit. writing general stuff about SVMs

@@
 \subsection{Background on Periodic Variables}
-Modern astronomical surveys observe millions of light sources over the course of a mission lasting a few years.
+Modern astronomical surveys observe millions of light sources (stars, galaxies, asteroids) over the course of a mission lasting a few years.
 Periodic variables, sources which vary periodically in brightness over time, are some of the most interesting.
@@
 Brightness versus phase is plotted in the bottom plot.
-Here we can observe the structure in the time series, which usually similar for stars of the same class but quite different for stars of different classes.\label{fig:cepheid}}
+Here we can observe the structure in the time series, which is usually similar for stars of the same class but different for stars of different classes.\label{fig:cepheid}}
     \end{includegraphics}
@@
 A telescope observes a source $j$ at times $t_{1},\ldots,t_{l}$, recording flux measurements of $m_{1},\ldots,m_{l}$.
-Typically there are measures of uncertainty on the flux measurements $e_{1},\ldots,e_{l}$.
+Typically there are measurements of uncertainty on the flux measurements $e_{1},\ldots,e_{l}$.
 So each source $j$ is initially characterized by an $l \times 3$ matrix $D_j=\{(t_{i},m_{i},e_{i})\}_{i=1}^{l}$.
@@
 \end{figure}
-A major problem with the standard approach is the high levels and heteroskedastic nature of the uncertainty in the features due to having poorly sampled time series ($l$ is small) or high error in the flux measurements ($e_{i}$ are systematically large).
+A major problem with the standard approach is the high levels and heteroskedastic nature of the uncertainty in the features due to having poorly sampled time series ($l$ is small), high error in the flux measurements ($e_{i}$ are systematically large), or irregular nature of sampling ($t_i$'s are highly concentrated, giving a poor representation of variation).
 This leads to situations where features meant to represent physical quantities of the time series, such as amplitude or period, are incorrect.
-As an example see Figure \ref{fig:period_amplitude}.
-This plot show the period and amplitude features for two classes of stars with a box around known physical limits for these features.
-Some of the observations have values outside these physical limits.
+As an example in Figure \ref{fig:period_amplitude} we plot the period and amplitude features for two classes of stars with a box around known physical limits for these features for these two classes.
+Some of the observations have values outside these physical limits, clearly indicating that the features are incorrectly estimated.
+This suggests that classifiers which incorporate feature uncertainty may be able to acheive improved performance.
 
-Many of the features used for classification rely on a correct estimate of period for the object.
+%% Many of the features used for classification rely on a correct estimate of period for the object.
 For example, features related to the derivative are often computed based on the folded light curve.
@@
 
-\section{Interval SVMs}
+\section{SVMs for Interval Data}
+\subsection{Mathematical Formulation}
+
+Support Vector Machines (SVMs) are a popular method for constructing classifiers \cite{scholkopf2002learning}.
+Letting $x_i \in \mathbb{R}^p$ be the vector of features for observation $i$ and $y_i$ its class (either $-1$ or $+1$), we can determine the SVM classifier by solving the optimization problem,
+\begin{align}
+\label{eq:dual}
+& \min_{\beta,\beta_0}  \sum_{i=1}^n \xi_i + \frac{\lambda}{2}\beta^T\beta\\
+& \text{subject to }  1 - y_if(x_i) \leq \xi_i; \, \xi \geq 0; \, f(x) = \beta_0 + \beta^Tx \nonumber
+\end{align}
+We determine the $\beta^*$ and $\beta_0^*$ that acheive the minimum and classify any new observation $x$ using $sign(\beta^* x + \beta_0)$.
+$\lambda$ is a tuning parameter than balances a tradeoff between maximizing the margin and separating observations in different classes.
+An optimal $\lambda$ may be chosen using 0-1 loss on a test set or through cross-validation.
+
+Various extensions to this classifier have been proposed that seek to incorporate uncertainty in the features ($x$'s) into the optimization problem.
+These formulations often take (or can be interpreted) worst case
+
+- similarities to elastic net of LASSO / SVM (cite elastic net article)
+- who has done L2 norm on location of features (
+
+\subsection{Path Algorithm for Determining Optimal Tuning Parameter}
+
+\section{Application to Variable Star Data Sets}
 \subsection{Constructing the Intervals from the Time Series}
@@
 Long time series will have small intervals around features, short time series will have wide intervals.
-For simple features, such as the standard deviation of the brightness measurements, making the interval width go down at rate $\sqrt{n}$ has a probabilistic interpretation via the central limit theorem.
+For simple features, such as the standard deviation of the brightness measurements, making the interval width go down at rate root-n has a probabilistic interpretation via the central limit theorem.
 \item Subsample the time series and derive features for each subsample.
@@
 In this work we take the second approach.
-While the first approach is attractive for simple features, many features (such as frequency) do not have a $\sqrt{n}$ convergence to the true value.
-Further the irregular time sampling means that even simple features may not have a $\sqrt{n}$ convergence.
+While the first approach is attractive for simple features, many features (such as frequency) do not have a sqrt-n convergence to the true value.
+Further the irregular time sampling means that even simple features may not have a root-n convergence.
 The third approach involves a lot of domain knowledge and will change from application to application.
 Further, there is no guarantee that features within the range of what is physically possible are actually correct.
-By subsampling the time series and deriving features, we hope to determine this.
 
@@
 The details of this procedure could be changed.
-For example one could bootstrap sample the time measurements.
+For example one could bootstrap sample the time measurements, instead of subsampling contiguous sections.
 Certain computational considerations enter here.
@@
 \begin{enumerate}
-\item Order the the light curve measurements in time i.e. $\{(t_1,m_1,e_1),(t_2,m_2,e_2), \ldots , (t_l,m_l,e_l)\}$ where $t_i < t_j$ for $i < j$.
-\item Sliced each light curve into 5 contiguous sections, producing 5 time series.
+\item Order the light curve measurements in time i.e. $\{(t_1,m_1,e_1),(t_2,m_2,e_2), \ldots , (t_l,m_l,e_l)\}$ where $t_i < t_j$ for $i < j$.
+\item Slice each light curve into 5 contiguous sections, producing 5 time series.
 Slice 1 is $(t_i,m_i,e_i)$ for $\frac{0}{10}l \leq i \leq \frac{5}{10}l$, slice 2 is $\frac{1}{10}l \leq i \leq \frac{6}{10}l$, ect.
@@
 \end{figure*}
+
+%% \begin{enumerate}
+%% \item measurements in the middle of the light curve get used more often
+%% \item sometimes the intervals do not contain the feature obtained when using the whole light curve.
+this is because taking shorter sections of light curves biases certain features high or low (frequency significance features tend to go down, should probably just get rid of these anyway)
+%% \end{enumerate}
+%% Bootstrap sampling might be a good approach, but this would destroy cadence sensitive features.
+So not sure what to do.
+This might be something interesting to discuss in the paper: \textbf{Determining feature error intervals for time series / image data is difficult.}
 
@@
 
-\subsection{Generating Hyper-rectangles}
-To generate the hyper-rectangles I did the following:
-\begin{enumerate}
-\item sliced each light curve into 5 contiguous parts. ordering measurements in time: slice 1 is 0\% through 50\%, slice 2 is 10\% through 60\%, . . .
-\item derive features for each of these parts
-\item put the interval minimum at the lowest value of the feature for the 5 slices. put the interval max at the maximum feature value across the 5 slices
-\end{enumerate}
-There are several problems with this approach.
-\begin{enumerate}
-\item measurements in the middle of the light curve get used more often
-\item sometimes the intervals do not contain the feature obtained when using the whole light curve.
-this is because taking shorter sections of light curves biases certain features high or low (frequency significance features tend to go down, should probably just get rid of these anyway)
-\end{enumerate}
-Bootstrap sampling might be a good approach, but this would destroy cadence sensitive features.
-So not sure what to do.
-This might be something interesting to discuss in the paper: \textbf{Determining feature error intervals for time series / image data is difficult.}
-
 \section{Notes on ``Robust Classification with Interval Data''}
@@
 \end{enumerate}
-\section{Note on Data}
-\begin{enumerate}
-\item for shorter lightcurves, certain features are biased downwards (for example freq\_signif features).
-probably std as well.
-should do bootstrap sampling instead?
-but bootstrap sampling destroys p2p features.
-\end{enumerate}
-
-\begin{enumerate}
-\item problem with normalizing data
-\item how is data normalized in svms
-\end{enumerate}
 

### 2012-05-03 report/ms.tex
a lot of updates here. working on getting the svm section in shape

@@
 \section{SVMs for Interval Data}
-\subsection{Mathematical Formulation}
+Support Vector Machines (SVMs) are a popular method for constructing classifiers.
+Let $x_i \in \mathbb{R}^p$ be the vector of features for observation $i$ and $y_i$ its class (either $-1$ or $+1$), we can determine the SVM classifier by solving the optimization problem,
+\begin{equation}
+\label{eq:svm}
+\min_{\beta,\beta_0}  \sum_{i=1}^n (1 - y_i(\beta^Tx + \beta_0))_{+} + \frac{\lambda}{2}\beta^T\beta
+\end{equation}
+The optimal $\beta^*$ and $\beta_0^*$ are used to classify a new observation $x$ using $sign(\beta^* x + \beta_0)$.
+$\lambda$ is a tuning parameter that balances a tradeoff between maximizing the margin and separating observations in different classes.
+An optimal $\lambda$ may be chosen using 0-1 loss on a test set or through cross-validation.
+See \cite{scholkopf2002learning} for an extensive overview of SVMs.
 
-Support Vector Machines (SVMs) are a popular method for constructing classifiers \cite{scholkopf2002learning}.
-Letting $x_i \in \mathbb{R}^p$ be the vector of features for observation $i$ and $y_i$ its class (either $-1$ or $+1$), we can determine the SVM classifier by solving the optimization problem,
-\begin{align}
-\label{eq:dual}
-& \min_{\beta,\beta_0}  \sum_{i=1}^n \xi_i + \frac{\lambda}{2}\beta^T\beta\\
-& \text{subject to }  1 - y_if(x_i) \leq \xi_i; \, \xi \geq 0; \, f(x) = \beta_0 + \beta^Tx \nonumber
-\end{align}
-We determine the $\beta^*$ and $\beta_0^*$ that acheive the minimum and classify any new observation $x$ using $sign(\beta^* x + \beta_0)$.
-$\lambda$ is a tuning parameter than balances a tradeoff between maximizing the margin and separating observations in different classes.
-An optimal $\lambda$ may be chosen using 0-1 loss on a test set or through cross-validation.
+Various extensions to the standard SVM have been proposed that seek to incorporate uncertainty in the features into the optimization problem.
+These formulations often take (or can be interpreted) as minimizing the objective function for a worst case allocation of features in some fixed set, i.e.
+\begin{equation}
+\label{eq:svm_minimax}
+\min_{\beta,\beta_0}  \max_{z \in \mathcal{X}} \sum_{i=1}^n (1 - y_i(\beta^Tz_i + \beta_0))_{+} + \frac{\lambda}{2}\beta^T\beta
+\end{equation}
+See \cite{bhattacharyya2004robust,shivaswamy2006second,ben2011chance} for discussions of some of these models.
 
-Various extensions to this classifier have been proposed that seek to incorporate uncertainty in the features ($x$'s) into the optimization problem.
-These formulations often take (or can be interpreted) worst case
+TO DISCUSS:
+\begin{enumerate}
+\item similarities to elastic net of LASSO / SVM e.g. Wang \cite{wang2007hybrid}
+\item our algorithm is not contained (?) in those considered by Russet \cite{rosset2007piecewise}
+\end{enumerate}
 
-- similarities to elastic net of LASSO / SVM (cite elastic net article)
-- who has done L2 norm on location of features (
-
-\subsection{Path Algorithm for Determining Optimal Tuning Parameter}
+\section{Path Algorithm for Interval SVM}
 
@@
 
-\section{Light Curves}
+%% \section{Light Curves}
 
-Figures \ref{fig:mira}, \ref{fig:cepheid}, \ref{fig:rrlyrae} show the light curves (i.e.
+%% Figures \ref{fig:mira}, \ref{fig:cepheid}, \ref{fig:rrlyrae} show the light curves (i.e.
 time series) of three stars.
@@
 
-\begin{figure}[h]
-  \begin{center}
-    \begin{includegraphics}[scale=.5]{4000.pdf}
-      \caption{Light curve of a RR Lyrae AB variable star.\label{fig:rrlyrae}}
-    \end{includegraphics}
-  \end{center}
-\end{figure}
+%% \begin{figure}[h]
+%%   \begin{center}
+%%     \begin{includegraphics}[scale=.5]{4000.pdf}
+%%       \caption{Light curve of a RR Lyrae AB variable star.\label{fig:rrlyrae}}
+%%     \end{includegraphics}
+%%   \end{center}
+%% \end{figure}
 
-\section{Initial Classification Work}
+%% \section{Initial Classification Work}
 
-\subsection{Ignoring Errors}
-I made a data set of 5508 of these light curves of class Mira, Classical Cepheid, and RR Lyrae AB.
+%% \subsection{Ignoring Errors}
+%% I made a data set of 5508 of these light curves of class Mira, Classical Cepheid, and RR Lyrae AB.
 Random forest (a type of classifier) obtained a 0.55\% error rate, without using any feature error information.
@@
 
-\section{Notes on ``Robust Classification with Interval Data''}
+\subsection{The Data Sets}
+
+\subsection{Results}
+
+\subsection{Conclusions}
 \begin{enumerate}
-\item how is new data point classified? this doesn't seem to be mentioned anywhere
-\item role of $\rho$ is not super clear. described as a ``global measure of uncertainty'' on page 3 but then is then is optimized over e.g. equation 16
-\item $\Sigma$ known and given
-\item no mention of kernels for SVM with intervals.
-(kernels are mentioned with respect to MPM on page 11) perhaps SVM intervals don't work with intervals.
-that seems really bad.
-maybe if kernel preserves rectangular structure of interval?
+\item constructing intervals is non-trivial in many high dimensional problems
+\item not clear that this robust framework is ideal when new observation might have low error on certain features
+\item kernels, are they possible to use
 \end{enumerate}

### 2012-05-03 code/james/svm_in_R.R
lines to read in different files

@@ -6,12 +6,39 @@ library('randomForest')
 
 
 ## get the data
-data1 = read.table("../data/CEPeasy")
+data1 = read.table("../../data/CEPeasy")
 datamatrix = as.matrix(data1)
 p = (ncol(datamatrix)-1)/2
 y = as.factor(datamatrix[,1])
 x = datamatrix[,2:(p+1)]
 x = x[,apply(x,2,var)!=0]
+
+###
+### read in mark's transformed data file to test that
+### U / L to Y X S trans is working correctly
+###
+library('R.matlab')
+library('Rcompression')
+filename = "../../data/.mat"
+mat = readMat(filename)
+p = dim(mat$x)[1]
+x = t(mat$x)
+y = as.factor(mat$y[1,])
+
+
+###
+### read in mark's transformed data file to test that
+### U / L to Y X S trans is working correctly
+###
+library('R.matlab')
+library('Rcompression')
+filename = "../../data/CEPconvexInterval.mat"
+mat = readMat(filename)
+x = mat$X
+p = dim(x)[2]
+y = as.factor(mat$Y[,1])
+featnames = sapply(mat$feature.names,function(x){x[1,1]})
+colnames(x) = featnames
 
 ## get cv error as a function of tuning parameter
 nsplits = 10
@@ -39,3 +66,9 @@ plot(costs,mar_means)
 ## what does random forest do?
 rf.fit = randomForest(x,y)
 rf.fit
+
+dev.new()
+varImpPlot(rf.fit)
+
+
+

### 2012-05-03 code/james/plots.R
changed location of rectangle / where we read in files from

@@ -18,10 +18,10 @@
 
 
 ## load packages
-data1_file = "../data/CEPconvexMeta.dat"
-point_file = '../data/CEPconvexPoint.dat'
-interval_file = '../data/CEPconvexInterval.dat'
-tfe = '../data/CEPconvexTfe.dat'
+data1_file = "../../data/CEPconvexMeta.dat"
+point_file = '../../data/CEPconvexPoint.dat'
+interval_file = '../../data/CEPconvexInterval.dat'
+tfe = '../../data/CEPconvexTfe.dat'
 dataPoint = read.table(point_file,sep=';',header=TRUE)
 dataInterval = read.table(interval_file,sep=';',header=TRUE)
 time_flux = read.table(tfe,sep=';',header=TRUE)
@@ -35,7 +35,7 @@ int_classes[dataPoint$classification==levels(dataPoint$classification)[2]] = 2
 coloring = c("orange","blue")
 pchs = c(1,2)
 
-pdf('../report/period_amplitude.pdf')
+pdf('../../report/period_amplitude.pdf')
 plot(log(dataPoint$amplitude,base=10),
      log(1/dataPoint$freq1_harmonics_freq_0,base=10),
      col=coloring[int_classes],
@@ -44,7 +44,8 @@ plot(log(dataPoint$amplitude,base=10),
      xlab="log(amplitude)",
      ylab="log(period)",
      main="Period-Amplitude Relationship for Two Star Classes")
-rect(-1,0,0,2,border="green",lwd=2)
+rect(log(.1,base=10),log(1,base=10),
+     log(2,base=10),log(200,base=10),border="green",lwd=2)
 legend("topleft",levels(dataPoint$classification),
        col=coloring,pch=pchs,lwd=2)
 dev.off()

### 2012-05-03 code/james/initial_classification.R
some screwing around here

@@ -24,10 +24,10 @@ library('randomForest')
 library('rpart')
 
 ## get the data
-data1_file = "../data/RR2convexMeta.dat"
-point_file = '../data/RR2convexPoint.dat'
-interval_file = '../data/RR2convexInterval.dat'
-tfe = '../data/RR2convexTfe.dat'
+data1_file = "../../data/CEPconvexMeta.dat"
+point_file = '../../data/CEPconvexPoint.dat'
+interval_file = '../../data/CEPconvexInterval.dat'
+tfe = '../../data/CEPconvexTfe.dat'
 dataPoint = read.table(point_file,sep=';',header=TRUE)
 dataInterval = read.table(interval_file,sep=';',header=TRUE)
 time_flux = read.table(tfe,sep=';',header=TRUE)
@@ -155,7 +155,7 @@ text(rpart.fit,use.n=TRUE)
 
 rf.fit = randomForest(classification~.,data=dataPoint)
 rf.fit
-
+varImpPlot(rf.fit)
 
 
 

### 2012-05-08 code/analyze_features.m
added some results in results/may7_1 (check README files within). polished main functions a bit and added function analyze_features.m

@@ -1,0 +1,28 @@
+function analyze_features(data_fname,results_fname,sname,params_fname,name_of_dataset)
+
+min_loss = inf;
+load(fname);
+load(params_fname);
+load(data_fname);
+for i = 1:numel(loss_values)
+	if loss_values(i) < min_loss
+		lambdaBEST = Params{i}(1);
+		rhoBEST = Params{i}(2);
+	end
+end
+
+[loss b b0] = svm(X,Y,X,Y,lambdaBEST,rhoBEST,S);
+
+[R iSorted] = sort(b);
+b = b(iSorted);
+feature_namesOLD = feature_names;
+feature_names = cell(1,numel(feature_names));
+for i = 1:numel(feature_names)
+	feature_names{i} = feature_namesOLD{iSorted(i)};
+end
+
+f=fopen(sname,'w');
+for i = numel(feature_names):-1:1
+	fprintf(f,[feature_names{i} ':\t' num2str(b(i),'%.10f') '\n']);
+end
+fclose(f);

### 2012-05-08 code/collect.m

@@ -1,0 +1,5 @@
+dname = '/home/aa/ugrad/mrogers/ee227a/project/results/RR2convexInterval/';
+save_dname = '/home/aa/ugrad/mrogers/ee227a/project/results/summary/may7_1/';
+params_fname = '~/ee227a/project/paramsRR2.mat';
+name_of_dataset = 'RR2';
+collectResults(dname,save_dname,params_fname,name_of_dataset);

### 2012-05-08 code/collectResults.m

@@ -1,54 +1,112 @@
-function collectResults(fname_prefix,sname,params_fname,name_of_dataset)
-% collectResults.m stores all losses computed by computeResults.m in a matrix and plots them.
+function collectResults(dname,save_dname,params_fname,name_of_dataset)
+% collectResults.m does two things:  one, it stores all losses computed by computeResults.m in a matrix and plots them. Second, it stores the L0 values of primal variable b as a function of rho for some optimal lambda.
 %
 % INPUTS
 % fname_prefix: filename prefix.  All result files are of the form fname_prefix_index.mat
-% sname[DO NOT GIVE AN EXTENSION]: file to store matrix of results.  also the name of the plot files.
+% save_dname: directory to store matrix of loss values, vector of L0_norm(b) vs. rho values are stored.
 % params_fname: name of file where parameters are stored.
 % name_of_dataset: name of dataset analyzed, which is used to label plots
 
 
-% do not give sname an extension.
-if strcmp(fname_prefix(numel(fname_prefix)),'/')
-	fname_prefix = fname_prefix(1:(numel(fname_prefix)-1));
+if ~strcmp(dname(numel(dname)),'/')
+	dname = [dname '/'];
 end
-d = dir([fname_prefix '*.mat']);
-dname = fname_prefix;
-while ~strcmp(dname(numel(dname)),'/')
-	dname = dname(1:(numel(dname)-1));
+if ~strcmp(save_dname(numel(save_dname)),'/')
+	save_dname = [save_dname '/'];
 end
+d = dir([dname '*.mat']);
 load(params_fname);
-results = zeros(size(Params));
+
+% create matrix of loss values, matrix of L0_norm(b) values
+disp('collecting loss values in single matrix')
+loss_values = zeros(size(Params));
+L0_norm_b = zeros(size(Params));
 for i = 1:numel(d)
 	load([dname d(i).name]);
-	iParam
-	results(iParam) = loss;
+	i
+	loss_values(i) = loss;
+	L0_norm_b(i) = numel(find(b~=0));
 end
-save([sname '.mat'],'results','Lambda','Rho');
+
[…]

### 2012-05-08 code/computeResults.m

@@ -1,19 +1,16 @@
-function computeResults(fname,sname_prefix,params_fname,iParam)
+function computeResults(iParams,fname,save_dname,params_fname)
 % computeResults.m computes the loss of the SVM interval classifier when applied to data in fname. The result is stored in sname_prefix_iParam.mat, the parameters are loaded from params_fname, and iParam is the index of the cell array Params, located in params_fname, to use.
 
+if ~strcmp(save_dname(numel(save_dname)),'/')
+	save_dname = [save_dname '/'];
+end
 load(fname);
 cv_split = .1;
 num_cv_splits = 1/cv_split;
 load(params_fname);
-lambda = Params{iParam}(1);
-rho = Params{iParam}(2);
 if ~exist('S')
 	S = zeros(size(X));
 end
-
-
-% normalize data via quantile ranking
-[X Y S] = quantile_ranking(X,Y,S);
 
 % if multiclass data, then choose the two classes with the most datapoints
 class_indices = 1:max(Y);
@@ -36,13 +33,45 @@ S2 = S(I2,:);
 X = [X1;X2];
 Y = [Y1;Y2];
 S = [S1;S2];
-valid_feature_indices = zeros(1,size(X,2));
-for i = 1:size(X,2)
-	valid_feature_indices(i) = all(~isnan(X(:,i)));
+
+% MATLAB cell arrays are dumb so I have to do something tricky to update class_of_each_datapoint
+class_of_each_datapointOLD = class_of_each_datapoint;
+class_of_each_datapoint = cell(numel(I1)+numel(I2),1);
+for i = 1:numel(I1)
+	class_of_each_datapoint1{i} = class_of_each_datapointOLD{I1(i)};
 end
-valid_feature_indices = logical(valid_feature_indices);
+for i = 1:numel(I2)
+	class_of_each_datapoint{i+numel(I1)} = class_of_each_datapointOLD{I2(i)};
+end
+
+% remove columns containing all zeros or containing some NaNs
+valid_feature_indices = zeros(1,size(X,2));
+is_valid_feature = @(r) (  numel(find(isnan(r)))==0  ) && (  numel(find(r))>0  );
+for i = 1:size(X,2)
+	valid_feature_indices(i) = is_valid_feature(X(:,i));
+end
+valid_feature_indices = find(valid_feature_indices);
 X = X(:,valid_feature_indices);
 S = S(:,valid_feature_indices);
[…]

### 2012-05-08 code/getParams.m

@@ -1,9 +1,21 @@
-function getParams(sname,Lambda,Rho)
+function getParams(sname,C,Lambda,Rho)
 
+if size(Lambda,2)==1
+	Lambda = Lambda';
+end
+if size(C,2)==1
+	Rho = Rho';
+end
+if size(Rho,2)==1
+	C = C';
+end
+C = sort(C);
+Lambda = sort(Lambda);
+Rho = sort(Rho);
 Params = cell(numel(Lambda),numel(Rho));
 for i = 1:numel(Lambda)
 	for j = 1:numel(Rho)
 		Params{i,j} = [Lambda(i) Rho(j)];
 	end
 end
-save(sname,'Params','Lambda','Rho')
+save(sname,'Params','C','Lambda','Rho')

### 2012-05-08 code/mytiedrank.m

@@ -1,0 +1,13 @@
+function ranks = mytiedrank(x)
+
+[R I] = sort(x);
+[RI II] = sort(I);
+ranks = zeros(size(x));
+for i = 1:numel(ranks)
+	for j = 1:numel(ranks)
+		if x(I(II(i)))==x(I(II(j)))
+			ranks(i) = ranks(i) + II(j);
+		end
+	end
+	ranks(i) = ranks(i) / numel(find(x == x(I(II(i)))));
+end

### 2012-05-08 code/quantile_ranking.m

@@ -5,18 +5,23 @@ p = size(X,2);
 L = (X-S) / 2;
 H = (X+S) / 2;
 LH = [L;H];
-Irandom = randperm(2*n);
-[R Iinverse] = sort(Irandom);
-LH = LH(Irandom,:);
+%Irandom = randperm(2*n);
+%[R Iinverse] = sort(Irandom);
+%LH = LH(Irandom,:);
 for i = 1:p
-	[R I] = sort(LH(:,i));
-	[RI ranks] = sort(I);
+%	[R I] = sort(LH(:,i));
+%	[RI ranks] = sort(I);
+	ranks = mytiedrank(LH(:,i));
 	LH(:,i) = norminv(ranks / (numel(ranks)+1),0,1);
+	license_error_is_thrown = false;
 end
-LH = LH(Iinverse,:);
+%LH = LH(Iinverse,:);
 L = LH([1:n],:);
 H = LH([1:n]+n,:);
 X = (L+H) / 2;
-S = abs(L-H) / 2;
+S = (H-L) / 2;
+if ~all(S(:) >= 0)
+	error('Some lower bounds are exceeding their upper bounds.');
+end
 
 

### 2012-05-08 code/svm.m

@@ -1,4 +1,4 @@
-function loss = svm(XTr,YTr,XTe,YTe,lambda,rho,S)
+function [loss b b0] = svm(XTr,YTr,XTe,YTe,lambda,rho,S)
 % if argument is unused, just pass []. Loss function used: sign(y(i) * f(x(i)))
 %
 % INPUTS

### 2012-05-08 code/xval.m

@@ -1,4 +1,4 @@
-function loss = xval(X,Y,S,lambda,rho,cv_split,num_cv_splits)
+function [loss b b0] = xval(X,Y,S,lambda,rho,cv_split,num_cv_splits)
 % cross-validation
 %
 % X = [n x p]: Data
@@ -44,3 +44,6 @@ for i = 1:num_cv_splits
 	loss = loss + svm(XTr,YTr,XTe,YTe,lambda,rho,STr);
 end
 loss = loss / num_cv_splits;
+
+% compute b and b0 by training on entire dataset
+[loss2 b b0] = svm(X,Y,X,Y,lambda,rho,S);

### 2012-05-08 code/analyze_features.m
features.m is a script that can be edited so that it can run analyze_features.m, which produces text file of (L0_norm(beta), feature_name) pairs.  Such text files also added to repo in /results/may7_1.

@@ -1,7 +1,7 @@
 function analyze_features(data_fname,results_fname,sname,params_fname,name_of_dataset)
 
 min_loss = inf;
-load(fname);
+load(results_fname);
 load(params_fname);
 load(data_fname);
 for i = 1:numel(loss_values)
@@ -10,9 +10,9 @@ for i = 1:numel(loss_values)
 		rhoBEST = Params{i}(2);
 	end
 end
-
+[X Y S class_of_each_datapoint feature_names] = preprocess_data(X,Y,S,class_of_each_datapoint,feature_names);
 [loss b b0] = svm(X,Y,X,Y,lambdaBEST,rhoBEST,S);
-
+b=abs(b);
 [R iSorted] = sort(b);
 b = b(iSorted);
 feature_namesOLD = feature_names;
@@ -23,6 +23,6 @@ end
 
 f=fopen(sname,'w');
 for i = numel(feature_names):-1:1
-	fprintf(f,[feature_names{i} ':\t' num2str(b(i),'%.10f') '\n']);
+	fprintf(f,[feature_names{i} ':\t\t\t\t' num2str(b(i),'%.10f') '\n']);
 end
 fclose(f);

### 2012-05-08 code/computeResults.m

@@ -12,57 +12,8 @@ if ~exist('S')
 	S = zeros(size(X));
 end
 
-% if multiclass data, then choose the two classes with the most datapoints
-class_indices = 1:max(Y);
-class_freqs = zeros(size(class_indices));
-for i = class_indices
-	class_freqs(i) = numel(find(Y==i));
-end
-[temp class_indices] = sort(class_freqs,'descend');
-index_of_first_class = class_indices(1);
-index_of_second_class = class_indices(2);
-I1 = find(Y==index_of_first_class);
-I2 = find(Y==index_of_second_class);
-I1 = I1(1:numel(I2));
-Y1 = Y(I1) ./ Y(I1) * (1);
-Y2 = Y(I2) ./ Y(I2) * (-1);
-X1 = X(I1,:);
-X2 = X(I2,:);
-S1 = S(I1,:);
-S2 = S(I2,:);
-X = [X1;X2];
-Y = [Y1;Y2];
-S = [S1;S2];
-
-% MATLAB cell arrays are dumb so I have to do something tricky to update class_of_each_datapoint
-class_of_each_datapointOLD = class_of_each_datapoint;
-class_of_each_datapoint = cell(numel(I1)+numel(I2),1);
-for i = 1:numel(I1)
-	class_of_each_datapoint1{i} = class_of_each_datapointOLD{I1(i)};
-end
-for i = 1:numel(I2)
-	class_of_each_datapoint{i+numel(I1)} = class_of_each_datapointOLD{I2(i)};
-end
-
-% remove columns containing all zeros or containing some NaNs
-valid_feature_indices = zeros(1,size(X,2));
-is_valid_feature = @(r) (  numel(find(isnan(r)))==0  ) && (  numel(find(r))>0  );
-for i = 1:size(X,2)
-	valid_feature_indices(i) = is_valid_feature(X(:,i));
-end
-valid_feature_indices = find(valid_feature_indices);
-X = X(:,valid_feature_indices);
-S = S(:,valid_feature_indices);
-
-% MATLAB cell arrays are dumb so I have to do something tricky to update class_of_each_datapoint
-feature_namesOLD = feature_names;
-feature_names = cell(1,numel(valid_feature_indices));
-for i = 1:numel(feature_names)
-	feature_names{i} = feature_namesOLD{valid_feature_indices(i)};
-end
-
-% normalize data via quantile ranking
-[X Y S] = quantile_ranking(X,Y,S);
[…]

### 2012-05-08 code/features.m

@@ -1,0 +1,6 @@
+data_fname = '/home/aa/ugrad/mrogers/ee227a/project/data/CEPconvexInterval.mat';
+results_fname=  '/home/aa/ugrad/mrogers/ee227a/project/results/summary/may7_1/CEP_results.mat';
+sname = '/home/aa/ugrad/mrogers/ee227a/project/results/summary/may7_1/CEP_features.txt';
+params_fname = '/home/aa/ugrad/mrogers/ee227a/project/paramsCEP.mat';
+name_of_dataset = 'CEP';
+analyze_features(data_fname,results_fname,sname,params_fname,name_of_dataset);

### 2012-05-08 code/preprocess_data.m

@@ -1,0 +1,53 @@
+function [X Y S class_of_each_datapoint feature_names] = preprocess_data(X,Y,S,class_of_each_datapoint,feature_names)
+
+% if multiclass data, then choose the two classes with the most datapoints
+class_indices = 1:max(Y);
+class_freqs = zeros(size(class_indices));
+for i = class_indices
+	class_freqs(i) = numel(find(Y==i));
+end
+[temp class_indices] = sort(class_freqs,'descend');
+index_of_first_class = class_indices(1);
+index_of_second_class = class_indices(2);
+I1 = find(Y==index_of_first_class);
+I2 = find(Y==index_of_second_class);
+I1 = I1(1:numel(I2));
+Y1 = Y(I1) ./ Y(I1) * (1);
+Y2 = Y(I2) ./ Y(I2) * (-1);
+X1 = X(I1,:);
+X2 = X(I2,:);
+S1 = S(I1,:);
+S2 = S(I2,:);
+X = [X1;X2];
+Y = [Y1;Y2];
+S = [S1;S2];
+
+% MATLAB cell arrays are dumb so I have to do something tricky to update class_of_each_datapoint
+class_of_each_datapointOLD = class_of_each_datapoint;
+class_of_each_datapoint = cell(numel(I1)+numel(I2),1);
+for i = 1:numel(I1)
+	class_of_each_datapoint1{i} = class_of_each_datapointOLD{I1(i)};
+end
+for i = 1:numel(I2)
+	class_of_each_datapoint{i+numel(I1)} = class_of_each_datapointOLD{I2(i)};
+end
+
+% remove columns containing all zeros or containing some NaNs
+valid_feature_indices = zeros(1,size(X,2));
+is_valid_feature = @(r) (  numel(find(isnan(r)))==0  ) && (  numel(find(r))>0  );
+for i = 1:size(X,2)
+	valid_feature_indices(i) = is_valid_feature(X(:,i));
+end
+valid_feature_indices = find(valid_feature_indices);
+X = X(:,valid_feature_indices);
+S = S(:,valid_feature_indices);
+
+% MATLAB cell arrays are dumb so I have to do something tricky to update class_of_each_datapoint
+feature_namesOLD = feature_names;
+feature_names = cell(1,numel(valid_feature_indices));
+for i = 1:numel(feature_names)
+	feature_names{i} = feature_namesOLD{valid_feature_indices(i)};
+end
+
+% normalize data via quantile ranking
+[X Y S] = quantile_ranking(X,Y,S);

### 2012-05-09 report/svmIntPath.tex
pushed document siqi wrote for convenience

\documentclass[11pt]{article}
\usepackage{amssymb,amsmath,amsthm}
\newtheorem*{theorem}{Theorem}
\newtheorem{lamma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem*{definition}{Definition}  
%\setlength{\oddsidemargin}{0in} 
%\setlength{\textwidth}{6.5in}
%\setlength{\headheight}{0in}
%\setlength{\headsep}{0in}
%\setlength{\topmargin}{0in}
%\setlength{\textheight}{9in}
%\pagestyle{empty}
\usepackage{graphicx}
\usepackage{enumerate}
%\documentclass[11pt]{article}
\pagestyle{empty}
\oddsidemargin=0in
\topmargin=-.5in
\textwidth=6.5in
\textheight=8.6in

\begin{document}

\title{The Entire Regularization Path for the Interval Support Vector Machine}
\maketitle
\section{Problem formulation}
Suppose $n$ data points are given: $(x_i,y_i)$ for $i=1,...,n$. Let $\mathcal I_+ = \{i: y_i=+1\}$ and $\mathcal I_- = \{i: y_i=-1\}$ be the set of positive class and negative class respectively. Also let $n_+=|\mathcal I_+|$ and $n_-=|\mathcal I_-|$ be the number of data points in these two classes. In this section, we will derive an efficient algorithm to compute the entire regularization path for the following interval svm problem:
\begin{equation}
\label{eq:svmInit}
\min_{\beta}\sum_{i=1}^n(1-y_i(\beta_0+\beta^Tx_i)+\rho\sigma_i^T|\beta|)_++\frac{\lambda}{2} ||\beta||_2^2.
\end{equation}
\eqref{eq:q}
(\ref{eq:q})
Introducing slack variables to get rid of the hinge loss function and absolute values, the problem is equivalent to:
\begin{align}
\label{eq:primal}
\min & \sum_{i=1}^n\xi_i + \lambda\frac{\beta^T\beta}{2}, \\
\text{subject to } & \xi_i \geq 1 - y_i(\beta_0+\beta^Tx_i)+\rho \sigma_i^Tt,\nonumber \\
                   & \xi_i \geq 0, \text{ for }i=1,2,...,n; \nonumber\\
                   & -t_j\leq \beta_j \leq t_j,\nonumber\\
                   & t_i \geq 0, \text{ for } j=1,2,...,p. \nonumber                      
\end{align}
Let the above problem be the primal problem. The Lagragian for this problem is
\[
\begin{array}{rl}
L(\xi,\beta_0,\beta,t,\alpha,\gamma,\nu,\mu,c)  = & \sum_{i=1}^n \xi_i + \lambda \frac{\beta^T\beta}{2} + \sum_{i=1}^n\alpha_i(1 - y_i(\beta_0+\beta^Tx_i)+\rho \sigma_i^Tt-\xi_i) \\
& - \sum_{j=1}^p\mu_j(t_j-\beta_j) - \sum_{j=1}^p\nu_j(t_j+\beta_j) - \sum_{i=1}^n\gamma_i\xi_i - \sum_{i=1}^nc_jt_j. \\
= & \sum_{i=1}^n(1-\alpha_i-\gamma_i)\xi_i + \lambda\frac{\beta^T\beta}{2} - (\sum_{i=1}^n \alpha_iy_ix_i - (\mu-\nu))^T\beta \\
  & - \sum_{i=1}^n\alpha_iy_i\beta_0 + \sum_{j=1}^p(\rho\alpha_i\sigma_{ji} - \mu_j-\nu_j-c_j)t_j.
\end{array}
\]
Minimizing with respect to the primal variables $(\xi,\beta_0,\beta,t)$ we derive the dual problem as follows:

\begin{align}
\label{eq:dual}
\max_{\alpha,\mu,\nu} & \sum_{i=1}^n \alpha_i - \frac{1}{2\lambda}||\sum_{i=1}^n \alpha_iy_i x_i - (\mu-\nu)||_2^2, \\
\text{subject to } & \sum_{i=1}^n \alpha_i y_i = 0, \ \rho \sum_{i=1}^n \alpha_i \sigma_{i} \geq \mu + \nu, \nonumber \\
& \alpha \in [0,1], \ \mu\geq0, \ \nu\geq0. \nonumber
\end{align}

Remarks: if the precision matrix is zero, i.e. $\Sigma = 0$, then second dual constraint implies $\mu+\nu\leq0$. Furthermore by the nonnegativity constraints we have $\mu=0$ and $\nu=0$. So the dual problem becomes
\[
\begin{array}{rl}
\max_{\alpha} & \sum_{i=1}^n \alpha_i - \frac{1}{2\lambda}||\sum_{i=1}^n \alpha_i y_i x_i||_2^2, \\
\text{subject to } & \sum_{i=1}^n \alpha_i y_i = 0, \ \alpha \in [0,1],
\end{array}
\]
which is exactly the dual to the standard SVM (see, for example, (12.13) of EML).\\

One can easily determine the KKT conditions of the Interval SVM problem:\\
(1) Primal stationarity:
\begin{align}
\frac{\partial}{\partial \beta}: & \ \beta = \frac{1}{\lambda}(\sum_{i=1}^n \alpha_i y_i x_i + \nu-\mu) \\ 
\frac{\partial}{\partial \beta_0}: & \ \sum_{i=1}^n \alpha_i y_i = 0\\
\frac{\partial}{\partial \xi}: & 1-\alpha - \gamma =0.
\end{align}
(2) Complementary slackness:
\begin{align}
\alpha_i(1 - y_i(\beta_0+\beta^Tx_i)+\rho \sigma_i^Tt-\xi_i) & = 0 \\
\gamma_i\xi_i & = 0 \\
\mu_j(t_j-\beta_j) & = 0 \\
\nu_j(t_j+\beta_j) & = 0 \\
c_jt_j & = 0 \\
\rho \sum_{i=1}^n \alpha_i \sigma_{ji} - (\mu_j +\nu_j+c_j) & =0 \\
\end{align}
(3) Primal feasibility and; (4) Dual feasibility.

From the optimality conditions, it is easy to observe the following statements hold:\\
(i) If $\xi_i>0$, then $\gamma_i = 0$ and so $\alpha_i =1$. Therefore by equation (7) we have $y_i(\beta_0+\beta^Tx_i)<1+\rho \sigma_i^Tt$, which indicates that the data point $i$ is on the left of the elbow of the hinge loss. \\
(ii) If $y_i(\beta_0+\beta^Tx_i)> 1+\rho \sigma_i^Tt$, that is, when the $i$-th data point is on the right of the elbow, then $\xi=0$ and by equation (6) and (8) $\alpha_i =0$. \\
(iii) If $y_i(\beta_0+\beta^Tx_i) =  1+\rho \sigma_i^Tt$, that data point is on the elbow. In this case we can only know $\alpha_i\in[0,1]$.\\
%(iv) if $t_j>0$, then $c_j=0$. By equation (XX), $\rho\sum_{i=1}^n \alpha_i \sigma_{ji} = \mu_j+\nu_j$
(iv) It is obvious that at optimal, we have $t = |\beta|$.\\
Now for convenience let $f(x) = \beta_0+\beta^Tx$ and define the following index sets for the data points:
\[\mathcal E = \{i: y_if(x_i) =  1+\rho \sigma_i^T|\beta|, 0\leq\alpha_i\leq1\}, \ \mathcal E \text{ for Elbow},\]
\[\mathcal L = \{i: y_if(x_i) <  1+\rho \sigma_i^T|\beta|, \alpha_i = 1\}, \ \mathcal L \text{ for Left of the elbow},\]
\[\mathcal R = \{i: y_if(x_i) >  1+\rho \sigma_i^T|\beta|,\alpha_i =0 \}, \ \mathcal R \text{ for Right of the elbow}.\]
Note that the above sets are similar to those defined in \cite{key-2}. In addition, since the absolute value of $\beta$ is involved, we also need to keep track of the following index sets for the parameter vector $\beta$:
\[\mathcal V_+ = \{j: \beta_j>0, \nu_j=0\},\]
\[\mathcal V_- = \{j: \beta_j<0,\mu_j=0\},\]
\[\mathcal Z = \{j: \beta_j=0,\sum_{i=1}^n \alpha_i \sigma_{ji} \geq \mu_j + \nu_j\}.\]
\section{Initialization}
We will determine the initial state of the parameters and the sets defined above. Without loss of generality, we assume that $n_+\geq n_->0$. We start with $\lambda=+\infty$ or equivalently $C=0$. In this case, it is easy to see that $\beta=0$. 
\begin{lamma}
Given $n_+\geq n_->0$ and $\beta=0$, the optimal value for the initial value of $\beta_0$ is $\beta_0 = 1$ and the loss is $\sum_{i=1}^n \xi_i = 2n_-$. If $n_+>n_-$, then $\beta_0 = 1$.\\
\end{lamma}
{\textbf Proof.} With $\beta=0$, the primal problem becomes:
\[
\begin{array}{rl}
\min & \sum_{i=1}^n \xi_i, \\
\text{subject to } & \xi_i \geq 0, \ \xi_i \geq 1- y_i \beta_0.
\end{array}
\]
Hence for $i\in \mathcal I_+$, $\xi_i \geq 1-\beta_0$ and for $i\in \mathcal I_-$, $\xi_i \geq 1+\beta_0$. At optimal, the equal sign must hold since we are minimizing the sum $\sum_{i=1}^n \xi_i$. Also, $\xi_i$'s are nonnegative, therefore we have $1-\beta_0\geq0$ and $1+\beta_0\geq0$ and so $\beta_0\in [-1,1]$. Furthermore, the objective function can be written in terms of $n_+$ and $n_-$:
\[
\sum_{i=1}^n \xi_i = n_+(1-\beta_0)+ n_-(1+\beta_0) = (n_--n_+)\beta_0 + (n_++n_-), 
\]
which is a linear function in $\beta_0$. If $n_-=n_+$, then the above function is simply a constant $2n_-$ and so $\beta_0$ can be arbitrary chosen in $[-1,1]$; on the other hand if $n_+>n_-$, the linear function is decreasing in $\beta_0$ and so to minimize the sum, we can pick $\beta_0$ on the right end point of $[-1,1]$. So $\beta_0 = 1$ if $n_+>n_-$. \\

From now on, we can safely assume that $n_+>n_-$, in which case the initial state is $\beta = 0$, $\beta_0=1$, $\xi_i = 0$ for $i\in \mathcal I_+$ and $\xi_i = 2$ for $i\in \mathcal I_-$. Thus by optimality conditions, for any $i\in \mathcal I_-$, $\gamma_i =0$ and so $\alpha_i=1$. In addition, since $0=\sum_{i=1}^n \alpha_i y_i = \sum_{i\in \mathcal I_+} \alpha_i - \sum_{i\in \mathcal I_-} \alpha_i$, we have $\sum_{i\in \mathcal I_+} \alpha_i = \sum_{i\in \mathcal I_-} \alpha_i = n_-$. The following lamma determines the initial value for the dual valuables:
\begin{lamma} Let $\tilde{\beta} = \sum_{i=1}^n \alpha_i y_i x_i + \nu - \mu$, 
\[
\begin{array}{rl}
(\alpha^*,\mu^*,\nu^*) = & \arg\min ||\tilde{\beta}||_2^2, \\
& \text{subject to: } 0\leq \alpha_i\leq 1,  \forall i \in \mathcal I_+; \alpha_i = 1,  \forall i \in \mathcal I_-; \\
& \sum_{i \in \mathcal I_+}\alpha_i = n_-, \rho\Sigma\alpha \geq \mu+\nu, \mu\geq0, \nu\geq0. \\
\end{array}
\]
 and $c^* = \rho\Sigma\alpha^* - \mu^*-\nu^*$. Then for some $\lambda_0$ we have for all $\lambda>\lambda_0$, $(\alpha(\lambda),\mu(\lambda),\nu(\lambda),c(\lambda)) = (\alpha^*, \mu^*,\nu^*,c^*)$.
\end{lamma}  
\textbf{Proof.} See \cite{key-2}.\\
Now let $\beta^* = \sum_{i=1}^n \alpha_i^* y_i x_i + \nu^* - \mu^*$ be the fixed coefficient direction corresponding to the initial $(\alpha^*,\mu^*,\nu^*)$. By lemma (XX) and the optimality conditions, we have for all $\lambda>\lambda_0$:
\[\beta(\lambda) = \frac{\sum_{i=1}^n \alpha_i^* y_i x_i + \nu^* - \mu^*}{\lambda}.\]
We now need to determine the point $\lambda_0$ that the dual variables $(\alpha,\mu,\nu,c)$ start to change. At the very beginning when $\lambda=+\infty$, there are two possible scenarios:
\begin{itemize}
\item There exist at least two data points in $\mathcal I_+$ with $0<\alpha_i^*<1$. Notice that there cannot be only one such element due to the integer constraint $\sum_{i\in \mathcal I_+} \alpha_i^* = n_-$. 
\item For all $i\in \mathcal I_+$, $\alpha_i^*$ is either 0 or 1.
\end{itemize}
For the first scenario, arbitrary pick an $i_+ \in \mathcal I_+$ such that $0<\alpha_{i_+}^*<1$. Since any of these points will stay in the elbow until a point in $\mathcal I_-$ enters the elbow, we can consider the element in $\mathcal I_-$ that first reaches its margin, i.e. $i_- = \arg \min_{i \in \mathcal I_-} x_i^T\beta^* + \rho \sigma_i^T|\beta^*|$. Therefore at $\lambda=\lambda_0$, as both $i_+$ and $i_-$ are at their respective margin, by the definition of elbow, we have the following system of equations:
\[\beta_0+\frac{1}{\lambda}x_{i_+}^T\beta^* =  1+\frac{1}{\lambda}\rho \sigma_{i_+}^T|\beta^*|,\]
\[\beta_0+\frac{1}{\lambda}x_{i_-}^T\beta^* =  -1-\frac{1}{\lambda}\rho \sigma_{i_-}^T|\beta^*|.\]
Solving for $\lambda$ and $\beta_0$ yields:
\[\lambda_0 = \frac{1}{2}(\beta^{*T}(x_{i_+}-x_{i_-})-\rho|\beta^*|^T(\sigma_{i_+}+\sigma_{i_-})),\]
\[\beta_0 = \frac{-\beta^{*T}(x_{i_+}+x_{i_-})+\rho|\beta^*|^T(\sigma_{i_+}-\sigma_{i_-})}{\beta^{*T}(x_{i_+}-x_{i_-})-\rho|\beta^*|^T(\sigma_{i_+}+\sigma_{i_-})}.\]
For the second scenario, for the initial parameter to change, a point in $\mathcal I_-$ and a point in $\mathcal I_+$ with $\alpha_i^* = 1$ must reach the margin simultaneously. Therefore we can let $i_+ = \arg \max_{i\in \mathcal I_+, \alpha_i=1} x_i^T\beta^* - \rho \sigma_i^T|\beta^*|$ and obtain $\lambda_0$ and $\beta_0$ by solving the above equations.\\

Remarks: in \cite{key-2}, Hastie et.al. split the initialization step into two cases depending on whether $n_+=n_-$ or $n_+>n_-$. In their case $n_+=n_-$, the initial state can be obtained efficiently without solving the quadratic programming problem. This does not seem to be the case in our problem set-up, as it also involves finding the initial values of the extra dual variables $\mu$ and $\nu$. Therefore solving a quardratic problem for starting up the path algorithm cannot be avoided.\\

\section{The Path}
Our algorithm keeps track of the following events:
\begin{enumerate}
\item[1.] One or more points from $\mathcal L$ have just entered $\mathcal E$;
\item[2.] One or more points from $\mathcal R$ have just reentered $\mathcal E$;
\item[3.] One or more points in $\mathcal E$ have just left the set, to join either $\mathcal R$ or $\mathcal L$.
\end{enumerate}
\noindent The above are events that are considered by \cite{key-2} for deriving a path algorithm for standard SVM. Since our problem involves also the $l_1$ norm of the parameter $\beta$, we also need to keep track of the following event:
\begin{enumerate}
\item[4.] One or more indices of the parameter $\beta$ enter $\mathcal Z$, that is,  $\beta_j$ becomes zero, initially being either positive or negative;
\item[5.] One or more indices of the parameter $\beta$ enter $\mathcal V_+$ from $\mathcal Z$;
\item[6.]  One or more indices of the parameter $\beta$ enter $\mathcal V_-$ from $\mathcal Z$.
\end{enumerate}
\subsection{Piecewise Linearity between Events}
By continuity, all of the index sets defined will stay the same until the next event occurs. Index by the superscript $l$ the sets immediately after the $l$-th event occurs. Likewise, index all the parameters in the same manner, and let $f^l$ be the classify function at this point. Also, for notation consistency define $\alpha_0 = \lambda \beta_0$ and so $\alpha_0^l = \lambda^l \beta_0^l$. Consider for $\lambda^l > \lambda > \lambda^{l+1}$, we have:
\begin{align}
\label{eq:classifier}
f(x) & = [f(x) - \frac{\lambda^l}{\lambda}f^l(x)] + \frac{\lambda^l}{\lambda}f^l(x) \nonumber \\
& = \frac{1}{\lambda}[x^T(\sum_{i=1}^n\alpha_iy_ix_i+\nu-\mu)+\alpha_0 - x^T(\sum_{i=1}^n\alpha_i^ly_ix_i+\nu^l-\mu^l)-\alpha_0^l+\lambda^l f^l(x)] \nonumber \\
& = \frac{1}{\lambda}[x^T\sum_{i\in\mathcal E^l}(\alpha_i-\alpha_i^l)y_ix_i+x^T(\nu-\nu^l)-x^T(\mu-\mu^l)+(\alpha_0-\alpha_0^l) +\lambda^l f^l(x)],
\end{align}
where the last equality follows from the fact that $\{1,...,n\}=\mathcal L\cup\mathcal E\cup \mathcal R$, and $\alpha_i = 1$ on $\mathcal L$; $\alpha_i=0$ on $\mathcal R$. The value of $\alpha_i$ for $i$ not in the elbow remains unchanged between events. Since each data point in $\mathcal E^l$ is to stay in $\mathcal E$ for $\lambda\in (\lambda^{l+1},\lambda^{l})$, we have:
\[y_jf(x_j) = 1+ \rho\sigma_j^T|\beta|.\]
Plug in equation \eqref{eq:classifier} for $f(x_j)$, the above formula becomes:
\begin{align}
\label{eq:elbow}
\frac{1}{\lambda}[\sum_{i\in\mathcal E^l}(\alpha_i-\alpha_i^l)y_jy_ix_j^Tx_i+y_jx_j^T(\nu-\mu-(\nu^l-\mu^l))+y_j(\alpha_0-\alpha_0^l) +\lambda^l (1+\rho \sigma_j^T|\beta^l|)] = 1+\rho\sigma_j^T|\beta|.
\end{align}
We can expression the parameter $\beta_i$ in terms of $\alpha$. For any $i\in\mathcal V_+$, since $\nu_i=0$, $\mu_i = \rho\sum_{k=1}^n \alpha_k\sigma_{ik}$. Plug all these parameters into the formula for $\beta_i$, we have
\[
\beta_i = \frac{1}{\lambda}\sum_{k=1}^n(\alpha_iy_kx_{ik}-\mu_i) =\frac{1}{\lambda}\sum_{k=1}^n\alpha_k(y_kx_{ik}-\rho\sigma_{ik}) = \frac{1}{\lambda}\sum_{k=1}^n\alpha_kw_{ik}.\]
Similarly, for $i\in\mathcal V_-$, since $\mu_i=0$, $\nu_i = \rho\sum_{k=1}^n \alpha_k\sigma_{ik}$ and so
\[
\beta_i = \frac{1}{\lambda}\sum_{k=1}^n(\alpha_iy_kx_{ik}+\nu_i) =\frac{1}{\lambda}\sum_{k=1}^n\alpha_k(y_kx_{ik}+\rho\sigma_{ik})=\frac{1}{\lambda}\sum_{k=1}^n\alpha_kz_{ik}.\]
Let $h_k = \sum_{i\in\mathcal V_+}\sigma_{ij}w_{ik} - \sum_{i\in\mathcal V_-}\sigma_{ij}z_{ik}$. By splitting $\beta$ into positive and negative parts, we can get rid of the absolute value in $\sigma_j^T|\beta|$:
\[
\begin{array}{rl}
\sigma_j^T|\beta| &= \sum_{i\in\mathcal V_+}\sigma_{ij}\beta_{i} - \sum_{i\in\mathcal V_-}\sigma_{ij}\beta_{i} \\
&=\frac{1}{\lambda}\sum_{k=1}^n\alpha_k(\sum_{i\in\mathcal V_+}\sigma_{ij}w_{ik} - \sum_{i\in\mathcal V_-}\sigma_{ij}z_{ik})\\
&=\frac{1}{\lambda}\sum_{k=1}^n\alpha_kh_k
\end{array}
\] 
Next, let us look at the term $x_j^T(\nu-\mu)$:
\[
\begin{array}{rl}
x_j^T(\nu-\mu) & = \sum_{i\in\mathcal V_-}x_{ij}\nu_i - \sum_{i\in\mathcal V_+}x_{ij}\mu_i + \sum_{i\in Z}x_{ij}(\nu_i-\mu_i)\\
& = \sum_{i\in\mathcal V_-}x_{ij}(\rho\sum_{k=1}^n\alpha_k\sigma_{ik}) - \sum_{i\in\mathcal V_+}x_{ij}(\rho\sum_{k=1}^n\alpha_k\sigma_{ik}) + \sum_{i\in Z}x_{ij}(\nu_i-\mu_i)
\end{array}
\]
Notice that for $i\in Z$, $\beta_i=0$ and so $\sum_{k=1}^n\alpha_ky_kx_{ik}+\nu_i-\mu_i=0$. Therefore $\nu_i-\mu_i = -\sum_{k=1}^n\alpha_ky_kx_{ik}$. Hence we have:
\[
x_j^T(\nu-\mu) = \sum_{k=1}^n\alpha_k(\rho\sum_{i\in\mathcal V_-}x_{ij}\sigma_{ik}-\rho\sum_{i\in\mathcal V_+}x_{ij}\sigma_{ik}+\sum_{i\in Z}y_kx_{ik}) = \sum_{k=1}^n\alpha_k g_{jk},
\]
where $g_{jk}=\rho\sum_{i\in\mathcal V_-}x_{ij}\sigma_{ik}-\rho\sum_{i\in\mathcal V_+}x_{ij}\sigma_{ik}+\sum_{i\in Z}y_kx_{ik}$. Now, let $\delta_k = \alpha_k^l-\alpha_k$. After some rearrangements, equation \eqref{eq:elbow} becomes:
\[
\sum_{k\in\mathcal E}\delta_k(y_jy_kx_j^Tx_k + y_j g_{jk} - \rho h_{jk}) + y_j\delta_0 = \lambda^l-\lambda,
\]
for all $j\in\mathcal E$. Thus by constructing a matrix $\mathbf{K}$ with entry $K_{jk} = y_jy_kx_j^Tx_k + y_j g_{jk} - \rho h_{jk}$, the above system of equations can be represented by the following matrix form:
\[
\mathbf{K}\boldsymbol{\delta} + \delta_0 \mathbf{y}_l = (\lambda^l-\lambda)\textbf{1},
\]
where $\mathbf{y}_l$ is a vector of length $m$ whose entries are $y_i$'s for $i\in \mathcal E$. In addition, since $\sum_{i=1}^n \alpha_iy_i = 0$, we have $\sum_{k\in\mathcal E}y_k\delta_k=0$ and so
\[\mathbf{y}_l^T\boldsymbol{\delta}=0.\]
So all together we have $m+1$ unknown variables and $m+1$ linear equations. Now let:
\[
\mathbf{A}_l = 
\left( \begin{array}{cc}
0 & \mathbf{y}_l^T \\
\mathbf{y}_l & \mathbf{K}_l 
\end{array}\right), \
\boldsymbol{\delta}^a = 
\left( \begin{array}{c}
\delta_0 \\
\boldsymbol{\delta}
\end{array}
\right), \ 
\textbf{1}^a = 
\left( \begin{array}{c}
0 \\
\textbf{1}
\end{array}
\right). 
\]
So the linear system can be written as
\[
\mathbf{A}_l\boldsymbol{\delta}^a = (\lambda_l-\lambda)\textbf{1}^a.
\]
Let $\textbf{b}^a = \mathbf{A}_l^{-1}\textbf{1}^a$, then for $k=0$ or $k \in \mathcal E_l$, we have
\begin{align}
\label{eq:alpha}
\alpha_k = \alpha_k^l - (\lambda^l-\lambda)b_k,
\end{align}
which shows linearity of $\alpha$ between two events, i.e. $\lambda^{l+1}<\lambda<\lambda^{l}$. To evaluate the function value of $f$ at the data point $x_j$, we have
\begin{align}
\label{eq:fxj}
f(x_j) = \frac{\lambda^l}{\lambda}(f^l(x_j)-h^l(x_j))+h^l(x_j),
\end{align}
where 
\[
h^l(x) = \sum_{k\in\mathcal E_l}b_j(y_kx_j^Tx_k+g_{jk})+b_0.
\]
\subsection{Finding the Next Event}
The linear (or inverse linear) path established above continues until one of the following events occur:
\begin{enumerate}
\item One of the points (if any) on the elbow $\mathcal E_l$ is about to enter either $\mathcal R$ or $\mathcal L$. For the first case $\alpha_i = 0$, by solving equation \eqref{eq:alpha} we can obtain a candidate breakpoint $\lambda$ for the $j$-th data point:
\[
\lambda = \frac{\lambda^lb_j-\alpha_j^l}{b_j}.
\]
Similar, in the case where the point is about to enter $\mathcal L$ we have
\[
\lambda = \frac{\lambda^lb_j-\alpha_j^l+1}{b_j}.
\]
Compute the above candidate break points for all data points that are currently on the elbow (so that we have $2m$ such candidates). Take the greatest such $\lambda$ that is smaller than $\lambda^l$, denote that quantity by $\lambda_a$.
\item One of the points $j$ in either $\mathcal L^l$ or $\mathcal R^l$ enters the elbow, that is $y_jf(x_j) = 1+\rho\sigma_j^T|\beta|$. By equation \eqref{eq:fxj}, we have
\[
\frac{\lambda^l}{\lambda}(f^l(x_j)-h^l(x_j))y_j + h^l(x_j)y_j = 1 + \frac{1}{\lambda}\sum_{i=1}^n\alpha_kh_k.
\]   
The right-hand-side of the above equation can be rewritten as
\[
1+\frac{1}{\lambda}\sum_{k\in\mathcal L}h_k + \frac{1}{\lambda}\sum_{k\in\mathcal E}(\alpha_k^l + (\lambda-\lambda^l)b_k)h_k.
\]
So a break point candidate is
\[
\lambda = \frac{\lambda^l(f^l(x_j)-h^l(x_{jk}))-y_j\sum_{k\in\mathcal L}h_{jk} - y_j\sum_{k\in\mathcal E}\alpha_k^lh_{jk} + \lambda^l\sum_{k\in\mathcal E}b_k h_{jk}}{y_j-h^l(x_j)+y_j\sum_{k\in\mathcal E}b_kh_{jk}}.
\]
\item A nonzero component of $\beta$ becomes zero. This means for each $i\in\mathcal V_+$, by equation  we solve $\sum_{k=1}^n\alpha_kw_{ik}=0$ and obtain a break point candidate
\[
\lambda = \frac{\lambda^l\sum_{k\in\mathcal E} b_kw_{ik}-\sum_{k\in\mathcal E}\alpha_k^l w_{ik}-\sum_{k\in\mathcal L} w_{ik}}{\sum_{k\in\mathcal E} b_kw_{ik}}.
\]
For $i\in\mathcal V_-$, simply replace $w_{ik}$ by $z_{ik}$.

\item A zero component of $\beta$ becomes nonzero. For a component $i\in Z$ to become positive, we require $c_i = 0$ and $\nu_i =0$. By equation (XX), $\mu_i = \sum_{k=1}^n\alpha_ky_kx_{ik}$, together with the optimality condition (XX), we need to solve $\rho\sum_{k=1}^n\alpha_k\sigma_{ik}=\sum_{k=1}^n\alpha_ky_kx_{ik}$. Same analysis for $i\in Z$ to become negative. Hence we have
\[
\lambda = \frac{\lambda^l\sum_{k\in\mathcal E} b_kw_{ik}-\sum_{k\in\mathcal E}\alpha_k^l w_{ik}-\sum_{k\in\mathcal L} w_{ik}}{\sum_{k\in\mathcal E} b_kw_{ik}}.
\]

\end{enumerate}
\section{Termination}
\section{Computation Complexity}
\section{Extension to Kernal} (You need to transform the uncertainty in the original data space into the kernal space)

\begin{thebibliography}{References}

\bibitem{key-1}Saharon Rosset, Ji Zhu. (2007)

\bibitem{key-2}T Hastie, S Rosset, R Tibshirani\ldots{} - The Journal
of Machine \ldots{}, 2004 - dl.acm.org

\bibitem{key-3}L El Ghaoui, G Lanckeriet, G Natsoulis. (2003)

\bibitem{key-4} Element of machine learning
\end{thebibliography}

\end{document}

### 2012-05-09 report/ms.tex
one more small change
added very modest contribution to report ms.tex.

@@
 \subsection{The Data Sets}
+The first dataset analyzed contained two classes of Cepheids (CEP):  classical and [popII].
+Each class consisted of $n=200$ observations and $p=58$ features so that each observation is hyperrectangle in $\mathbb{R}^{58}$.
+The second dataset consisted of two classes of RR,  RR Lyrae AB and RR Lyrae D, with the same values of $n$ and $p$.
+\subsubsection{Preprocessing the data with quantile ranking}
+A quantile ranking technique was used to normalize values in each feature dimension by reducing the effects of outliers.
+Viewing the interval data as a three-dimensional array, the end-slices corresponding to the lower- and upper-bounds of the confidence intervals were isolated and then concatenated together to yield a $2n\times p$ array whose values were then mapped to the standard normal distribution.
+Features containing all zeroes or some NaNs were removed from the dataset.
 
 \subsection{Results}
+
+\subsubsection{Performance}
+The performance of the combined SVM model was compared to those of its degenerates by computing expected losses for multiple values of $\lambda$ and $\rho$.
+For a given $(\lambda,\rho)$, the expected loss was computed by performing cross-validation in 90-10 splits so that the union of testing points across splits is the entire dataset and the intersection is disjoint.
+See surface plots of loss versus $(\lambda,\rho)$: for the CEP dataset, $\lambda\in \lbrace 0\rbrace\cup [0.375,0.750]$ and $\rho\in\lbrace 0\rbrace\cup [0.090,0.032]$ while for the RR dataset, $\lambda\in\lbrace 0\rbrace\cup [54,284]$ and $\rho\in\lbrace 0\rbrace\cup [0.375,0.750]$.
+Observe that $(\lambda^*,\rho^*)\neq (0,0)$ for both datasets, which implies that the combined model outperforms both of its degenerates.
+For the CEP dataset, the optimal $(\lambda^*,\rho^*)=(9,0.320)$ yielded 13.25\% classification error while for the RR dataset, $(\lambda^*,\rho^*)=(284,0.48)$ yielded 21.50\% classification error.
+THESE NUMBERS DON'T LOOK RIGHT, MUST RERUN analyze_feature.m.
+
+The curves of loss versus $\lambda$ and loss versus $\rho$ were also analyzed.
+The loss versus $\lambda$ plot corresponds to the standard point SVM model in Hastie while the loss versus $\rho$ plot corresponds to the interval SVM model in El Ghaoui.
+Observe the convex-like curvatures, which suggest global minima and hence optimal $\lambda$ and $\rho$.
+
+\subsubsection{Feature selection as suggested by $||\beta||_0$ values}
 
@@
 \item kernels, are they possible to use
+\item links to code / git repo
 \end{enumerate}

### 2012-05-10 report/ms.tex
added \ to an _
merged siqi's work with report.tex

@@
-\documentclass[11pt]{article}
-\usepackage{amsmath,textcomp,amssymb,geometry,graphicx}
+\documentclass[10pt]{article}
+\usepackage{amsmath,textcomp,amssymb,graphicx,amsthm,enumerate}
+\usepackage[top=.75in, bottom=.75in, left=.75in, right=.75in]{geometry}
 \newcommand{\argmin}[1]{\underset{#1}{\operatorname{argmin}}\text{ }}
+\newtheorem*{theorem}{Theorem}
+\newtheorem{lamma}{Lemma}[section]
+\theoremstyle{definition}
+\newtheorem*{definition}{Definition}
 \begin{document}
@@
 The size of modern data sets requires that much of this work be automated by machine learning and statistical classifiers.
-\begin{figure}[h]
-  \begin{center}
-    \begin{includegraphics}[scale=.5]{2000.pdf}
+\begin{figure}[ht]
+\begin{minipage}[t]{.45\linewidth}
+  \centering
+    \begin{includegraphics}[scale=.48]{2000.pdf}
       \caption{Light curve of a Classical Cepheid type variable star.
@@
     \end{includegraphics}
-  \end{center}
+\end{minipage}
+\hspace{1cm}
+\begin{minipage}[t]{.45\linewidth}
+  \centering
+    \begin{includegraphics}[scale=.48]{204.pdf}
+      \caption{Light curve of a Mira type variable star.
+Mira variable stars have higher amplitude and longer periods than Cepheid variables.
+Notice that the period estimate of 322.55 appears to be incorrect.
+The true period is likely half of this.\label{fig:mira}}
+    \end{includegraphics}
+\end{minipage}
 \end{figure}
@@
 The true period appears to be around 161 days, half of the estimate.
-\begin{figure}[h]
-  \begin{center}
-    \begin{includegraphics}[scale=.5]{204.pdf}
-      \caption{Light curve of a Mira type variable star.\label{fig:mira}}
-    \end{includegraphics}
-  \end{center}
-\end{figure}
 \subsection{Classification Methodology}
@@
 \section{Path Algorithm for Interval SVM}
+
+\subsection{Problem formulation}
+Suppose $n$ data points are given: $(x_i,y_i)$ for $i=1,...,n$.
+Let $\mathcal I_+ = \{i: y_i=+1\}$ and $\mathcal I_- = \{i: y_i=-1\}$ be the set of positive class and negative class respectively.
+Also let $n_+=|\mathcal I_+|$ and $n_-=|\mathcal I_-|$ be the number of data points in these two classes.
+In this section, we will derive an efficient algorithm to compute the entire regularization path for the following interval SVM problem:
+\begin{equation}
+\label{eq:svmInit}
+\min_{\beta}\sum_{i=1}^n(1-y_i(\beta_0+\beta^Tx_i)+\rho\sigma_i^T|\beta|)_++\frac{\lambda}{2} ||\beta||_2^2.
+\end{equation}
+%\eqref{eq:q}
+%(\ref{eq:q})
+Introducing slack variables, the problem becomes:
+\begin{align}
+\label{eq:primal}
+\min & \sum_{i=1}^n\xi_i + \lambda\frac{\beta^T\beta}{2}, \\
+\text{subject to } & \xi_i \geq 1 - y_i(\beta_0+\beta^Tx_i)+\rho \sigma_i^Tt,\nonumber \\
+                   & \xi_i \geq 0, \text{ for }i=1,2,...,n; \nonumber\\
+                   & -t_j\leq \beta_j \leq t_j,\nonumber\\
+                   & t_i \geq 0, \text{ for } j=1,2,...,p. \nonumber                      
+\end{align}
+Let the above problem be the primal problem. The Lagrangian for this problem is
+\[
+\begin{array}{rl}
+L(\xi,\beta_0,\beta,t,\alpha,\gamma,\nu,\mu,c)
+%= & \sum_{i=1}^n \xi_i + \lambda \frac{\beta^T\beta}{2} + \sum_{i=1}^n\alpha_i(1 - y_i(\beta_0+\beta^Tx_i)+\rho \sigma_i^Tt-\xi_i) \\
+%& - \sum_{j=1}^p\mu_j(t_j-\beta_j) - \sum_{j=1}^p\nu_j(t_j+\beta_j) - \sum_{i=1}^n\gamma_i\xi_i - \sum_{i=1}^nc_jt_j. \\
+= & \sum_{i=1}^n(1-\alpha_i-\gamma_i)\xi_i + \lambda\frac{\beta^T\beta}{2} - (\sum_{i=1}^n \alpha_iy_ix_i - (\mu-\nu))^T\beta \\
+  & - \sum_{i=1}^n\alpha_iy_i\beta_0 + \sum_{j=1}^p(\rho\alpha_i\sigma_{ji} - \mu_j-\nu_j-c_j)t_j.
+\end{array}
+\]
+Minimizing with respect to the primal variables $(\xi,\beta_0,\beta,t)$, we derive the dual problem as follows:
+
+\begin{align}
+\label{eq:dual}
+\max_{\alpha,\mu,\nu} & \sum_{i=1}^n \alpha_i - \frac{1}{2\lambda}||\sum_{i=1}^n \alpha_iy_i x_i - (\mu-\nu)||_2^2, \\
+\text{subject to } & \sum_{i=1}^n \alpha_i y_i = 0, \ \rho \sum_{i=1}^n \alpha_i \sigma_{i} \geq \mu + \nu, \nonumber \\
+& \alpha \in [0,1], \ \mu\geq0, \ \nu\geq0. \nonumber
+\end{align}
+
+%Remarks: if the precision matrix $\Sigma$ is zero, the second constraint in the dual problem implies $\mu+\nu\leq0$.
+In addition, since both $\mu$ and $\nu$ are nonnegative,  we have $\mu=0$ and $\nu=0$.
+So the dual problem in this case becomes
+%\[
+%\begin{array}{rl}
+%\max_{\alpha} & \sum_{i=1}^n \alpha_i - \frac{1}{2\lambda}||\sum_{i=1}^n \alpha_i y_i x_i||_2^2, \\
+%\text{subject to } & \sum_{i=1}^n \alpha_i y_i = 0, \ \alpha \in [0,1],
+%\end{array}
+%\]
+%which is exactly the dual to the standard SVM. See, for example, Equation (12.13) of EML Hastie et al (2009) \cite{hasie2009elements}.\\
+
+One can easily determine the KKT conditions of the interval SVM problem:\\
+(1) Primal stationarity:
+\begin{align}
+\frac{\partial}{\partial \beta}: & \ \beta = \frac{1}{\lambda}(\sum_{i=1}^n \alpha_i y_i x_i + \nu-\mu) \\ 
+\frac{\partial}{\partial \beta_0}: & \ \sum_{i=1}^n \alpha_i y_i = 0\\
+\frac{\partial}{\partial \xi}: & 1-\alpha - \gamma =0.
+\end{align}
+(2) Complementary slackness:
+\begin{align}
+\alpha_i(1 - y_i(\beta_0+\beta^Tx_i)+\rho \sigma_i^Tt-\xi_i) & = 0 \\
+\gamma_i\xi_i & = 0 \\
+\mu_j(t_j-\beta_j) & = 0 \\
+\nu_j(t_j+\beta_j) & = 0 \\
+c_jt_j & = 0 \\
+\rho \sum_{i=1}^n \alpha_i \sigma_{ji} - (\mu_j +\nu_j+c_j) & =0 
+\end{align}
+(3) Primal feasibility and; (4) Dual feasibility. Both omitted here due to triviality.\\
+
+From the above optimality conditions, it is easy to observe the following statements hold:\\
+(i) If $\xi_i>0$, then $\gamma_i = 0$ and so $\alpha_i =1$.
+Therefore by (7) we have $y_i(\beta_0+\beta^Tx_i)<1+\rho \sigma_i^Tt$, which indicates that the data point $i$ is on the left of the elbow of the hinge loss.
+\\
+(ii) If $y_i(\beta_0+\beta^Tx_i)> 1+\rho \sigma_i^Tt$, that is, when the $i$-th data point is on the right of the elbow, then $\xi=0$ and by equation (6) and (8) $\alpha_i =0$. \\
+(iii) If $y_i(\beta_0+\beta^Tx_i) =  1+\rho \sigma_i^Tt$, that data point is on the elbow. In this case we can only know $\alpha_i\in[0,1]$.\\
+%(iv) if $t_j>0$, then $c_j=0$. By equation (XX), $\rho\sum_{i=1}^n \alpha_i \sigma_{ji} = \mu_j+\nu_j$
+(iv) It is obvious that at optimal, we have $t = |\beta|$.
+Hence if $\beta_j>0$ we have $t_j>0$ and so $c_j=0$.
+On the other hand, since $t_j+\beta_j>0$, $\nu_j=0$.
+Therefore in this case, $\mu_j = \rho \sum_{i=1}^n \alpha_i \sigma_{ji}$.\\
+(v) Similarly, if $\beta_j<0$, $c_j=0$, $\mu_j=0$ and $\nu_j = \rho \sum_{i=1}^n \alpha_i \sigma_{ji}$.\\
+
+Now for convenience let $f(x) = \beta_0+\beta^Tx$ and define the following index sets for the data points:
+\[\mathcal E = \{i: y_if(x_i) =  1+\rho \sigma_i^T|\beta|, 0\leq\alpha_i\leq1\}, \ \mathcal E \text{ for Elbow},\]
+\[\mathcal L = \{i: y_if(x_i) <  1+\rho \sigma_i^T|\beta|, \alpha_i = 1\}, \ \mathcal L \text{ for Left of the elbow},\]
+\[\mathcal R = \{i: y_if(x_i) >  1+\rho \sigma_i^T|\beta|,\alpha_i =0 \}, \ \mathcal R \text{ for Right of the elbow}.\]
+Note that the definition of the above sets are similar to those defined in \cite{hastie2004entire} except that we have an extra term $\rho \sigma_i^T|\beta|$ that is related to the uncertainty of the data.
+In addition, since the absolute value of $\beta$ is involved in our formulation, we also need to keep track of the following index sets for the parameter vector $\beta$:
+\[\mathcal V_+ = \{j: \beta_j>0, \nu_j=0\},\]
+\[\mathcal V_- = \{j: \beta_j<0,\mu_j=0\},\]
+\[\mathcal Z = \{j: \beta_j=0,\sum_{i=1}^n \alpha_i \sigma_{ji} \geq \mu_j + \nu_j\}.\]
+\subsection{Initialization}
+We will determine the initial state of the parameters and the sets defined above.
+Without loss of generality, we assume that $n_+\geq n_->0$.
+We start with $\lambda=+\infty$ or equivalently $C=0$.
+In this case, it is easy to see that $\beta=0$.
+\begin{lamma}
+Given $n_+\geq n_->0$ and $\beta=0$, the optimal value for the initial value of $\beta_0$ is $\beta_0 = 1$ and the loss is $\sum_{i=1}^n \xi_i = 2n_-$. If $n_+>n_-$, then $\beta_0 = 1$.\\
+\end{lamma}
+\noindent\textbf {Proof.} With $\beta=0$, the primal problem becomes:
+\[
+\begin{array}{rl}
+\min & \sum_{i=1}^n \xi_i, \\
+\text{subject to } & \xi_i \geq 0, \ \xi_i \geq 1- y_i \beta_0.
+\end{array}
+\]
+Hence for $i\in \mathcal I_+$, $\xi_i \geq 1-\beta_0$ and for $i\in \mathcal I_-$, $\xi_i \geq 1+\beta_0$.
+At optimal, the equal sign must hold since we are minimizing the sum $\sum_{i=1}^n \xi_i$.
+Also, $\xi_i$'s are nonnegative, therefore we have $1-\beta_0\geq0$ and $1+\beta_0\geq0$ and so $\beta_0\in [-1,1]$.
+Furthermore, the objective function can be written in terms of $n_+$ and $n_-$:
+\[
+\sum_{i=1}^n \xi_i = n_+(1-\beta_0)+ n_-(1+\beta_0) = (n_--n_+)\beta_0 + (n_++n_-), 
+\]
+which is a linear function in $\beta_0$.
+If $n_-=n_+$, then the above function is simply a constant $2n_-$ and so $\beta_0$ can be arbitrary chosen in $[-1,1]$; on the other hand if $n_+>n_-$, the linear function is decreasing in $\beta_0$ and so to minimize the sum, we can pick $\beta_0$ on the right end point of $[-1,1]$.
+So $\beta_0 = 1$ if $n_+>n_-$.
+\\
+
+From now on, we can safely assume that $n_+>n_-$, in which case the initial state is $\beta = 0$, $\beta_0=1$, $\xi_i = 0$ for $i\in \mathcal I_+$ and $\xi_i = 2$ for $i\in \mathcal I_-$.
+Thus by optimality conditions, for any $i\in \mathcal I_-$, $\gamma_i =0$ and so $\alpha_i=1$.
+In addition, since $0=\sum_{i=1}^n \alpha_i y_i = \sum_{i\in \mathcal I_+} \alpha_i - \sum_{i\in \mathcal I_-} \alpha_i$, we have $\sum_{i\in \mathcal I_+} \alpha_i = \sum_{i\in \mathcal I_-} \alpha_i = n_-$.
+The following lemma determines the initial value for the dual valuables:
+\begin{lamma} Let $\tilde{\beta} = \sum_{i=1}^n \alpha_i y_i x_i + \nu - \mu$, 
+\[
+\begin{array}{rl}
+(\alpha^*,\mu^*,\nu^*) = & \arg\min ||\tilde{\beta}||_2^2, \\
+& \text{subject to: } 0\leq \alpha_i\leq 1,  \forall i \in \mathcal I_+; \alpha_i = 1,  \forall i \in \mathcal I_-; \\
+& \sum_{i \in \mathcal I_+}\alpha_i = n_-, \rho\Sigma\alpha \geq \mu+\nu, \mu\geq0, \nu\geq0. \\
+\end{array}
+\]
+ and $c^* = \rho\Sigma\alpha^* - \mu^*-\nu^*$. Then for some $\lambda_0$ we have for all $\lambda>\lambda_0$, $(\alpha(\lambda),\mu(\lambda),\nu(\lambda),c(\lambda)) = (\alpha^*, \mu^*,\nu^*,c^*)$.
+\end{lamma}  
+\noindent\textbf{Proof.} The proof follows directly from Lemma 2 in \cite{hastie2004entire}.
+The key observasion is that  $\sum_{i=1}^n \alpha_i = 2n_-$ and this sum will remain constant for a while as $\beta$ grows from zero.
+Then we can plug this sum into the dual problem \eqref{eq:dual} and solve it with additional constraints: $\alpha_i = 1,  \forall i \in \mathcal I_-$ and $\sum_{i \in \mathcal I_+}\alpha_i = n_-$.
+\\
+
+Now let $\beta^* = \sum_{i=1}^n \alpha_i^* y_i x_i + \nu^* - \mu^*$ be the fixed coefficient direction corresponding to the initial $(\alpha^*,\mu^*,\nu^*)$.
+By the above lemma and the optimality conditions, we have for all $\lambda>\lambda_0$:
+\[\beta(\lambda) = \frac{\sum_{i=1}^n \alpha_i^* y_i x_i + \nu^* - \mu^*}{\lambda}.\]
+We now need to determine the point $\lambda_0$ that the dual variables $(\alpha,\mu,\nu,c)$ start to change. At the very beginning when $\lambda=+\infty$, there are two possible scenarios:
+\begin{itemize}
+\item There exist at least two data points in $\mathcal I_+$ with $0<\alpha_i^*<1$.
+Notice that there cannot be only one such element due to the integer constraint $\sum_{i\in \mathcal I_+} \alpha_i^* = n_-$.
+\item For all $i\in \mathcal I_+$, $\alpha_i^*$ is either 0 or 1.
+\end{itemize}
+For the first scenario, arbitrary pick an $i_+ \in \mathcal I_+$ such that $0<\alpha_{i_+}^*<1$.
+Since any of these points will stay in the elbow until a point in $\mathcal I_-$ enters the elbow, we can consider the element in $\mathcal I_-$ that first reaches its margin, i.e.
+$i_- = \arg \min_{i \in \mathcal I_-} x_i^T\beta^* + \rho \sigma_i^T|\beta^*|$.
+Therefore at $\lambda=\lambda_0$, as both $i_+$ and $i_-$ are at their respective margin, by the definition of elbow, we have the following system of equations:
+\begin{align*}
+\begin{cases}
+\beta_0+\frac{1}{\lambda}x_{i_+}^T\beta^* =  1+\frac{1}{\lambda}\rho \sigma_{i_+}^T|\beta^*|,\\
+\beta_0+\frac{1}{\lambda}x_{i_-}^T\beta^* =  -1-\frac{1}{\lambda}\rho \sigma_{i_-}^T|\beta^*|.
+\end{cases}
+\end{align*}
+Solving for $\lambda$ and $\beta_0$ yields:
+\begin{align}
+\begin{cases}
+\lambda_0 = \frac{1}{2}(\beta^{*T}(x_{i_+}-x_{i_-})-\rho|\beta^*|^T(\sigma_{i_+}+\sigma_{i_-})),\\
+\beta_0 = \frac{-\beta^{*T}(x_{i_+}+x_{i_-})+\rho|\beta^*|^T(\sigma_{i_+}-\sigma_{i_-})}{\beta^{*T}(x_{i_+}-x_{i_-})-\rho|\beta^*|^T(\sigma_{i_+}+\sigma_{i_-})}.
+\end{cases}
+\end{align}
+For the second scenario, for the initial parameter to change, a point in $\mathcal I_-$ and a point in $\mathcal I_+$ with $\alpha_i^* = 1$ must reach the margin simultaneously.
+Therefore we can let $i_+ = \arg \max_{i\in \mathcal I_+, \alpha_i=1} x_i^T\beta^* - \rho \sigma_i^T|\beta^*|$ and obtain $\lambda_0$ and $\beta_0$ by solving the above equations.\\
+
+%Remarks: in \cite{hastie2004entire}, Hastie et.al.
+split the initialization step into two cases depending on whether $n_+=n_-$ or $n_+>n_-$.
+In their case $n_+=n_-$, the initial state can be obtained efficiently without solving the quadratic programming problem.
+This does not seem to be the case in our problem, as it also involves finding the initial values of the extra dual variables $\mu$ and $\nu$.
+Therefore solving a quardratic problem for starting up the path algorithm cannot be avoided in our case.\\
+
+\subsection{The Path}
+As in \cite{hastie2004entire}, our algorithm keeps track of the following events:
+\begin{enumerate}
+\item[1.] One or more points from $\mathcal L$ have just entered $\mathcal E$;
+\item[2.] One or more points from $\mathcal R$ have just reentered $\mathcal E$;
+\item[3.] One or more points in $\mathcal E$ have just left the set, to join either $\mathcal R$ or $\mathcal L$.
+\end{enumerate}
+\noindent In addition, we also need to keep track of the following events involving the sign of the components of $\beta$:
+\begin{enumerate}
+\item[4.] One or more indices of the parameter $\beta$ enter $\mathcal Z$, that is,  $\beta_j$ becomes zero, initially being either positive or negative;
+\item[5.] One or more indices of the parameter $\beta$ enter $\mathcal V_+$ from $\mathcal Z$;
+\item[6.]  One or more indices of the parameter $\beta$ enter $\mathcal V_-$ from $\mathcal Z$.
+\end{enumerate}
+\subsection{Piecewise Linearity between Events}
+By continuity, all of the index sets defined will stay the same until the next event occurs.
+Index by the superscript $l$ the sets immediately after the $l$-th event occurs.
+Likewise, index all the parameters in the same manner, and let $f^l$ be the classify function at this point.
+Also, for notation consistency define $\alpha_0 = \lambda \beta_0$ and so $\alpha_0^l = \lambda^l \beta_0^l$.
+Consider for $\lambda^l > \lambda > \lambda^{l+1}$, we have:
+\begin{align}
+\label{eq:classifier}
+f(x) & = [f(x) - \frac{\lambda^l}{\lambda}f^l(x)] + \frac{\lambda^l}{\lambda}f^l(x) \nonumber \\
+%& = \frac{1}{\lambda}[x^T(\sum_{i=1}^n\alpha_iy_ix_i+\nu-\mu)+\alpha_0 - x^T(\sum_{i=1}^n\alpha_i^ly_ix_i+\nu^l-\mu^l)-\alpha_0^l+\lambda^l f^l(x)] \nonumber \\
+& = \frac{1}{\lambda}[x^T\sum_{i\in\mathcal E^l}(\alpha_i-\alpha_i^l)y_ix_i+x^T(\nu-\nu^l)-x^T(\mu-\mu^l)+(\alpha_0-\alpha_0^l) +\lambda^l f^l(x)],
+\end{align}
+where the last equality follows from the fact that $\{1,...,n\}=\mathcal L\cup\mathcal E\cup \mathcal R$, $\alpha_i = 1$ on $\mathcal L$ and $\alpha_i=0$ on $\mathcal R$.
+The value of $\alpha_i$ for $i$ not in the elbow remains unchanged between events.
+Since each data point in $\mathcal E^l$ is to stay in $\mathcal E$ for $\lambda\in (\lambda^{l+1},\lambda^{l})$, we have:
+\[y_jf(x_j) = 1+ \rho\sigma_j^T|\beta|, \forall j\in\mathcal E.\]
+Plug in \eqref{eq:classifier} for $f(x_j)$, the above equation becomes:
+\begin{align}
+\label{eq:elbow}
+\frac{1}{\lambda}[\sum_{i\in\mathcal E^l}(\alpha_i-\alpha_i^l)y_jy_ix_j^Tx_i+y_jx_j^T(\nu-\mu-(\nu^l-\mu^l))+y_j(\alpha_0-\alpha_0^l) +\lambda^l (1+\rho \sigma_j^T|\beta^l|)] = 1+\rho\sigma_j^T|\beta|.
+\end{align}
+We can expression the parameter $\beta_i$ in terms of $\alpha$.
+For any $i\in\mathcal V_+^l$, since $\nu_i=0$, $\mu_i = \rho\sum_{k=1}^n \alpha_k\sigma_{ik}$.
+Plug all these parameters into the formula for $\beta_i$, we have
+\[
+\beta_i = \frac{1}{\lambda}\sum_{k=1}^n(\alpha_iy_kx_{ik}-\mu_i) =\frac{1}{\lambda}\sum_{k=1}^n\alpha_k(y_kx_{ik}-\rho\sigma_{ik}) = \frac{1}{\lambda}\sum_{k=1}^n\alpha_kw_{ik},\]
+where $w_{ik} =y_kx_{ik}-\rho\sigma_{ik}$. Similarly, for $i\in\mathcal V_-$, since $\mu_i=0$, $\nu_i = \rho\sum_{k=1}^n \alpha_k\sigma_{ik}$ and so
+\[
+\beta_i = \frac{1}{\lambda}\sum_{k=1}^n(\alpha_iy_kx_{ik}+\nu_i) =\frac{1}{\lambda}\sum_{k=1}^n\alpha_k(y_kx_{ik}+\rho\sigma_{ik})=\frac{1}{\lambda}\sum_{k=1}^n\alpha_kz_{ik}.\]
+Let $h_{jk} = \sum_{i\in\mathcal V_+^l}\sigma_{ij}w_{ik} - \sum_{i\in\mathcal V_-^l}\sigma_{ij}z_{ik}$. By splitting $\beta$ into positive and negative parts, we have:
+\[
+\begin{array}{rl}
+\sigma_j^T|\beta| &= \sum_{i\in\mathcal V_+^l}\sigma_{ij}\beta_{i} - \sum_{i\in\mathcal V_-^l}\sigma_{ij}\beta_{i} \\
+&=\frac{1}{\lambda}\sum_{k=1}^n\alpha_k(\sum_{i\in\mathcal V_+^l}\sigma_{ij}w_{ik} - \sum_{i\in\mathcal V_-^l}\sigma_{ij}z_{ik})\\
+&=\frac{1}{\lambda}\sum_{k=1}^n\alpha_kh_{jk}.
+\end{array}
+\] 
+Next, look at the term $x_j^T(\nu-\mu)$. Notice that:
+\[
+\begin{array}{rl}
+x_j^T(\nu-\mu) %& = \sum_{i\in\mathcal V_-^l}x_{ij}\nu_i - \sum_{i\in\mathcal V_+^l}x_{ij}\mu_i + \sum_{i\in Z^l}x_{ij}(\nu_i-\mu_i)\\
+& = \sum_{i\in\mathcal V_-^l}x_{ij}(\rho\sum_{k=1}^n\alpha_k\sigma_{ik}) - \sum_{i\in\mathcal V_+^l}x_{ij}(\rho\sum_{k=1}^n\alpha_k\sigma_{ik}) + \sum_{i\in Z^l}x_{ij}(\nu_i-\mu_i)
+\end{array}
+\]
+Observe that for $i\in Z^l$, $\beta_i=0$ and so $\sum_{k=1}^n\alpha_ky_kx_{ik}+\nu_i-\mu_i=0$. Therefore $\nu_i-\mu_i = -\sum_{k=1}^n\alpha_ky_kx_{ik}$. Hence we have:
+\[
+x_j^T(\nu-\mu) = \sum_{k=1}^n\alpha_k(\rho\sum_{i\in\mathcal V_-}x_{ij}\sigma_{ik}-\rho\sum_{i\in\mathcal V_+}x_{ij}\sigma_{ik}+\sum_{i\in Z}y_kx_{ik}) = \sum_{k=1}^n\alpha_k g_{jk},
+\]
+where $g_{jk}=\rho\sum_{i\in\mathcal V_-^l}x_{ij}\sigma_{ik}-\rho\sum_{i\in\mathcal V_+^l}x_{ij}\sigma_{ik}+\sum_{i\in Z^l}y_kx_{ik}$.
+Now, let $\delta_k = \alpha_k^l-\alpha_k$.
+After some rearrangements, Equation \eqref{eq:elbow} becomes:
+\[
+\sum_{k\in\mathcal E}\delta_k(y_jy_kx_j^Tx_k + y_j g_{jk} - \rho h_{jk}) + y_j\delta_0 = \lambda^l-\lambda,
+\]
+for all $j\in\mathcal E$.
+Thus following \cite{hastie2004entire}, by constructing a matrix $\mathbf{K}$ with entry $K_{jk} = y_jy_kx_j^Tx_k + y_j g_{jk} - \rho h_{jk}$, the above system of equations can be written:
+\[
+\mathbf{K}\boldsymbol{\delta} + \delta_0 \mathbf{y}_l = (\lambda^l-\lambda)\textbf{1},
+\]
+where $\mathbf{y}_l$ is a vector of length $m$ whose entries are $y_i$'s for $i\in \mathcal E^l$. In addition, since $\sum_{i=1}^n \alpha_iy_i = 0$, we have $\sum_{k\in\mathcal E}y_k\delta_k=0$ and so
+\[\mathbf{y}_l^T\boldsymbol{\delta}=0.\]
+So all together we have $m+1$ unknown variables and $m+1$ linear equations. Now let:
+\[
+\mathbf{A}_l = 
+\left( \begin{array}{cc}
+0 & \mathbf{y}_l^T \\
+\mathbf{y}_l & \mathbf{K}_l 
+\end{array}\right), \
+\boldsymbol{\delta}^a = 
+\left( \begin{array}{c}
+\delta_0 \\
+\boldsymbol{\delta}
+\end{array}
+\right), \ 
+\textbf{1}^a = 
+\left( \begin{array}{c}
+0 \\
+\textbf{1}
+\end{array}
+\right). 
+\]
+So the linear system can be written as
+\[
+\mathbf{A}_l\boldsymbol{\delta}^a = (\lambda_l-\lambda)\textbf{1}^a.
+\]
+Let $\textbf{b}^a = \mathbf{A}_l^{-1}\textbf{1}^a$, then for $k=0$ or $k \in \mathcal E^l$, we have
+\begin{align}
+\label{eq:alpha}
+\alpha_k = \alpha_k^l - (\lambda^l-\lambda)b_k,
+\end{align}
+which shows linearity of $\alpha$ between two events, i.e. $\lambda^{l+1}<\lambda<\lambda^{l}$. To evaluate the function value of $f$ at the data point $x_j$, we have
+\begin{align}
+\label{eq:fxj}
+f(x_j) = \frac{\lambda^l}{\lambda}(f^l(x_j)-h^l(x_j))+h^l(x_j),
+\end{align}
+where $h^l(x) = \sum_{k\in\mathcal E_l}b_j(y_kx_j^Tx_k+g_{jk})+b_0$.
+
+\subsection{Finding the Next Event}
+The linear path established above continues until one of the following events occur:
+\begin{enumerate}
+\item One of the points (if any) on the elbow $\mathcal E^l$ is about to enter either $\mathcal R$ ($\alpha_i=0$) or $\mathcal L$ ($\alpha_i=1$).
+By solving equation \eqref{eq:alpha} we can obtain a candidate breakpoint $\lambda$ for the $j$-th data point to enter the respectively $\mathcal R$ and $\mathcal L$:
+\[
+\lambda = \frac{\lambda^lb_j-\alpha_j^l}{b_j} \text{ and } \lambda = \frac{\lambda^lb_j-\alpha_j^l+1}{b_j}.
+\]
+%Compute the above candidate break points for all data points that are currently on the elbow (so that we have $2m$ such candidates).
+Take the greatest such $\lambda$ that is smaller than $\lambda^l$, denote that quantity by $\lambda_a$.
+\item One of the points $j$ in either $\mathcal L^l$ or $\mathcal R^l$ enters the elbow, that is $y_jf(x_j) = 1+\rho\sigma_j^T|\beta|$. By Equation \eqref{eq:fxj}, we have
+\[
+\frac{\lambda^l}{\lambda}(f^l(x_j)-h^l(x_j))y_j + h^l(x_j)y_j = 1 + \frac{1}{\lambda}\sum_{i=1}^n\alpha_kh_k.
+\]   
+%The right-hand-side of the above equation can be rewritten as
+%\[
+%1+\frac{1}{\lambda}\sum_{k\in\mathcal L^l}h_k + \frac{1}{\lambda}\sum_{k\in\mathcal E^l}(\alpha_k^l + (\lambda-\lambda^l)b_k)h_k.
+%\]
+Solving the above equation for $\lambda$, we have:
+\[
+\lambda = \frac{\lambda^l(f^l(x_j)-h^l(x_{jk}))-y_j\sum_{k\in\mathcal L^l}h_{jk} - y_j\sum_{k\in\mathcal E^l}\alpha_k^lh_{jk} + \lambda^l\sum_{k\in\mathcal E^l}b_k h_{jk}}{y_j-h^l(x_j)+y_j\sum_{k\in\mathcal E^l}b_kh_{jk}}.
+\]
+\item A nonzero component of $\beta$ becomes zero. This means for each $i\in\mathcal V_+^l$, by equation  we solve $\sum_{k=1}^n\alpha_kw_{ik}=0$ and obtain a break point candidate
+\[
+\lambda = \frac{\lambda^l\sum_{k\in\mathcal E^l} b_kw_{ik}-\sum_{k\in\mathcal E^l}\alpha_k^l w_{ik}-\sum_{k\in\mathcal L^l} w_{ik}}{\sum_{k\in\mathcal E^l} b_kw_{ik}}.
+\]
+For $i\in\mathcal V_-^l$, simply replace $w_{ik}$ by $z_{ik}$.
+
+\item A zero component of $\beta$ becomes nonzero.
+For a component $i\in Z^l$ to become positive, we require $c_i = 0$ and $\nu_i =0$, therefore $\mu_i = \sum_{k=1}^n\alpha_ky_kx_{ik}$.
+Together with the optimality conditions, we need to solve $\rho\sum_{k=1}^n\alpha_k\sigma_{ik}=\sum_{k=1}^n\alpha_ky_kx_{ik}$.
+Same analysis for $i\in Z^l$ to become negative.
+The formula for $\lambda$ turns out to have the same form as that in 3.
+
+\end{enumerate}
+
+Compute the all of the above $\lambda$'s and take the greatest such $\lambda$ that is smaller than $\lambda^l$. That $\lambda$ will be the break point for the next event.
+
+\subsection{Continuation and termination}
+After finding the $\lambda$ at which the next event occurs, we can update all the index sets accordingly and continue to find the next event.
+If the data points are separable in the sense of interval data (that is, there is a hyperplane that separates all the rectangles formed by the data points in the two classes), the algorithm can terminate once $\mathcal L^l$ becomes empty.
+If the points are not separable, then we rely on the user to provide an upper bound or $\lambda$ or a maximum number of break points.
+
+\subsection{A simple simulated example}
+To test the correctness and efficiency of our proposed algorithm, we construct a test data set as follows: let $n_+=10$ and $n_-=8$, and to keep the example simple let us consider having only $p=5$ features.
+For each $i\in\mathcal V_+$ and $j=1,...,5$, generate $x_{ij}$ from a standard normal distribution $N(0,1)$, independently of each other.
+Similarly, generate each $x_{ij}$ in the negative class from the normal distribution $N(-0.5,1)$.
+To construct the precision matrix, for each entry in that matrix, simulate a number from $N(0.1,0.1)$ and then take the absolute value of it.
+Also, we set $\rho = 1.0$ and target the range of $C$ to be $[0,3]$.
+First, we use a brute-force algorithm to compute the regularization paths for the parameters, making a call to the function that solves one interval SVM problem ({\tt svmInterval}) at a finite break points of along the interval $[0,3]$.
+We then run our interval SVM path algorithm on this data set and compare the results of the two approaches.
+The paths for $\beta$ are shown in Figure~\ref{fig:betaPath} and the plots for $\beta_0$ and $\alpha$ can be found in the Appendix.
+In each of the plot, the paths are computed via the brute-force algorithm and the break points (indicated by the dash lines) are predicted by the path algorithm.
+It can be seen that our path algorithm correctly identifies all the changing points in this example.
+
+\begin{center}
+\begin{figure}[!h]
+   \centering
+   \includegraphics[width=0.7\textwidth]{./betaPath.png} 
+      \caption{The path of $\beta$ for the simulated data.}
+   \label{fig:betaPath}
+\end{figure}
+\end{center}
+
+\subsection{Computation Complexity}
+Hastie et al \cite{hastie2004entire} suggests the running time of their algorithm to be $O(n^2m+nm^2)$, where $m$ is the average size of the elbow $\mathcal E^l$.
+Since our algorithm is a variant of theirs (in particular, the core burden of the computation is still to solve the linear system which results in $O(m_l^3)$.
+Of course, we might have many of such systems the along the path), we conjecture our running time to be the same.
+We time our path algorithm for fitting the data in the previous section and the elapsed time is 1.01 secs on a 2.66 GHz Intel Core 2 Duo Mac OS machine.
+As a comparison, the running time for the brute-force algorithm is 66.27 secs for 300 points along the path.
+Note that the path algorithm gives the true path while the brute-force algorithm is still finding only a few snapshots of the path.
+
+%\subsection{Extension to Kernal} (You need to transform the uncertainty in the original data space into the kernal space)
+%\note{in fitting the CEP data,  between 2.03 and 2.13 $\beta0$ value can be arbitrary}
+\subsection{Matlab and R programs}
+All the programs for this project are included in the {\tt zip} file submitted together with this hard copy.
+In particular, the matlab package {\tt svmIntervalPath} is the implementation of our path algorithm.
+Also, matlab and R code for testing and data analysis can be found in that file as well.
 
@@
 For the CEP dataset, the optimal $(\lambda^*,\rho^*)=(9,0.320)$ yielded 13.25\% classification error while for the RR dataset, $(\lambda^*,\rho^*)=(284,0.48)$ yielded 21.50\% classification error.
-THESE NUMBERS DON'T LOOK RIGHT, MUST RERUN analyze_feature.m.
+THESE NUMBERS DON'T LOOK RIGHT, MUST RERUN analyze\_feature.m.
 
@@
 
+\subsection{Appendix}
+\begin{center}
+\begin{figure}[!h]
+   \centering
+   \includegraphics[width=0.7\textwidth]{./beta0Path.png} 
+      \caption{The path of the intercept parameter $\beta_0$ for the simulated data. Notice that since $n_+=10>8=n_-$, by the first lemma, $\beta_0(0)=1$.}
+   \label{fig:beta0Path}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}[!h]
+   \centering
+   \includegraphics[width=0.7\textwidth]{./alphaPath.png} 
+      \caption{The path of $\alpha$ for the simulated data.}
+   \label{fig:alphaPath}
+\end{figure}
+\end{center}
+
 \bibliographystyle{plain}

### 2012-05-10 report/ms.tex
converted .png to .pdf
added some results from today. Ranges of C could perhaps be improved.

--- 2012-05-09 report/ms.tex
@@
 For a given $(\lambda,\rho)$, the expected loss was computed by performing cross-validation in 90-10 splits so that the union of testing points across splits is the entire dataset and the intersection is disjoint.
-See surface plots of loss versus $(\lambda,\rho)$: for the CEP dataset, $\lambda\in \lbrace 0\rbrace\cup [0.375,0.750]$ and $\rho\in\lbrace 0\rbrace\cup [0.090,0.032]$ while for the RR dataset, $\lambda\in\lbrace 0\rbrace\cup [54,284]$ and $\rho\in\lbrace 0\rbrace\cup [0.375,0.750]$.
+See surface plots of loss versus $(\lambda,\rho)$: for the CEP dataset, $\lambda\in \lbrace 0\rbrace\cup [0.375,9]$ and $\rho\in\lbrace 0\rbrace\cup [0.90,0.32]$ while for the RR dataset, $\lambda\in\lbrace 0\rbrace\cup [54,284]$ and $\rho\in[0.00,0.48]$.
 Observe that $(\lambda^*,\rho^*)\neq (0,0)$ for both datasets, which implies that the combined model outperforms both of its degenerates.

### 2012-05-10 code/analyze_features.m

@@ -13,6 +13,8 @@ end
 [X Y S class_of_each_datapoint feature_names] = preprocess_data(X,Y,S,class_of_each_datapoint,feature_names);
 [loss b b0] = svm(X,Y,X,Y,lambdaBEST,rhoBEST,S);
 b=abs(b);
+disp('||beta||_0 = ')
+disp(numel(find(b<10e-8)));
 [R iSorted] = sort(b);
 b = b(iSorted);
 feature_namesOLD = feature_names;

### 2012-05-10 code/batch.m
added batch.m

@@ -1,0 +1,16 @@
+tic
+name_of_dataset = 'RR2';
+fname = ['/home/aa/ugrad/mrogers/ee227a/project/data/' name_of_dataset 'convexInterval.mat']; % filename where the data is stored
+save_dname = ['/home/aa/ugrad/mrogers/ee227a/project/results/' name_of_dataset 'convexInterval/']; % directory where results are saved
+params_fname = ['/home/aa/ugrad/mrogers/ee227a/project/params' name_of_dataset '.mat']; % where parameters are saved
+load(params_fname);
+num_processes = numel(C)*numel(Rho);
+num_batches = ceil(num_processes / 100);
+iBatch = input(['Please enter index of batch (1 through ' num2str(num_batches) '): ']);
+if iBatch == num_batches && mod(num_processes,100)~=0
+	iParams = [1:mod(num_processes,100)] + 100*(iBatch-1);
+else
+	iParams = [1:100] + 100*(iBatch-1);
+end
+computeResults(iParams,fname,save_dname,params_fname);
+toc

### 2012-05-10 code/analyze_features.m
added more results from today for larger values of C.  Also added code with additional comments.

@@ -1,4 +1,9 @@
 function analyze_features(data_fname,results_fname,sname,params_fname,name_of_dataset)
+% data_fname: name of file containing original data
+% results_fname: name of file containing summary results
+% sname: save name
+% params_fname: name of file where Params, Lambda, Rho, C are stored.
+% name_of_dataset: either 'CEP' or 'RR2'
 
 min_loss = inf;
 load(results_fname);
@@ -6,15 +11,22 @@ load(params_fname);
 load(data_fname);
 for i = 1:numel(loss_values)
 	if loss_values(i) < min_loss
+		min_loss = loss_values(i);
 		lambdaBEST = Params{i}(1);
 		rhoBEST = Params{i}(2);
 	end
 end
 [X Y S class_of_each_datapoint feature_names] = preprocess_data(X,Y,S,class_of_each_datapoint,feature_names);
 [loss b b0] = svm(X,Y,X,Y,lambdaBEST,rhoBEST,S);
+disp('loss = ')
+disp(loss)
+disp('lambda* = ')
+disp(lambdaBEST)
+disp('rho* = ')
+disp(rhoBEST)
 b=abs(b);
 disp('||beta||_0 = ')
-disp(numel(find(b<10e-8)));
+disp(numel(find(b>=10e-8)))
 [R iSorted] = sort(b);
 b = b(iSorted);
 feature_namesOLD = feature_names;
@@ -23,6 +35,7 @@ for i = 1:numel(feature_names)
 	feature_names{i} = feature_namesOLD{iSorted(i)};
 end
 
+% create text file
 f=fopen(sname,'w');
 for i = numel(feature_names):-1:1
 	fprintf(f,[feature_names{i} ':\t\t\t\t' num2str(b(i),'%.10f') '\n']);

### 2012-05-10 code/collect.m

@@ -1,5 +1,7 @@
-dname = '/home/aa/ugrad/mrogers/ee227a/project/results/RR2convexInterval/';
-save_dname = '/home/aa/ugrad/mrogers/ee227a/project/results/summary/may7_1/';
-params_fname = '~/ee227a/project/paramsRR2.mat';
+% collect.m is the script used to call the driver function collectResults.m
 name_of_dataset = 'RR2';
+subdir_name = 'may9_2';
+dname = ['/home/aa/ugrad/mrogers/ee227a/project/results/' name_of_dataset 'convexInterval/']; % name of directory where results, i.e., outputs from batch.m, are stored. not to be confused with the directory where summary results are stored.
+save_dname = ['/home/aa/ugrad/mrogers/ee227a/project/results/summary/' subdir_name '/']; % name of directory where summary results are stored.
+params_fname = ['~/ee227a/project/params' name_of_dataset '.mat']; % name of file containing Params cell array, Lambda, Rho, and C
 collectResults(dname,save_dname,params_fname,name_of_dataset);

### 2012-05-10 code/computeResults.m

@@ -1,5 +1,5 @@
 function computeResults(iParams,fname,save_dname,params_fname)
-% computeResults.m computes the loss of the SVM interval classifier when applied to data in fname. The result is stored in sname_prefix_iParam.mat, the parameters are loaded from params_fname, and iParam is the index of the cell array Params, located in params_fname, to use.
+% computeResults.m computes the loss of the SVM interval classifier when applied to data in fname. The result is stored in sname_prefix_iParam.mat, the parameters are loaded from params_fname, and iParams is a subset of the indices of the cell array Params, located in params_fname, to use.
 
 if ~strcmp(save_dname(numel(save_dname)),'/')
 	save_dname = [save_dname '/'];
@@ -21,8 +21,8 @@ for i = iParams
 	[loss b b0] = xval(X,Y,S,lambda,rho,cv_split,num_cv_splits);
 	iParam = i;
 	if i==1
-		save([save_dname num2str(i,'%03d') '.mat'],'lambda','rho','loss','b','b0','iParam','feature_names','class_of_each_datapoint');
+		save([save_dname num2str(i,'%09d') '.mat'],'lambda','rho','loss','b','b0','iParam','feature_names','class_of_each_datapoint');
 	else
-		save([save_dname num2str(i,'%03d') '.mat'],'lambda','rho','loss','b','b0','iParam');
+		save([save_dname num2str(i,'%09d') '.mat'],'lambda','rho','loss','b','b0','iParam');
 	end
 end

### 2012-05-10 code/features.m

@@ -1,6 +1,8 @@
-data_fname = '/home/aa/ugrad/mrogers/ee227a/project/data/CEPconvexInterval.mat';
-results_fname=  '/home/aa/ugrad/mrogers/ee227a/project/results/summary/may7_1/CEP_results.mat';
-sname = '/home/aa/ugrad/mrogers/ee227a/project/results/summary/may7_1/CEP_features.txt';
-params_fname = '/home/aa/ugrad/mrogers/ee227a/project/paramsCEP.mat';
-name_of_dataset = 'CEP';
+% features.m is the script used to call the driver function analyze_features.m
+name_of_dataset = 'RR2';
+subdir_name = 'may9_2';
+data_fname = ['/home/aa/ugrad/mrogers/ee227a/project/data/' name_of_dataset 'convexInterval.mat'];
+results_fname=  ['/home/aa/ugrad/mrogers/ee227a/project/results/summary/' subdir_name '/' name_of_dataset '_results.mat'];
+sname = ['/home/aa/ugrad/mrogers/ee227a/project/results/summary/' subdir_name '/' name_of_dataset '_features.txt'];
+params_fname = ['/home/aa/ugrad/mrogers/ee227a/project/params' name_of_dataset '.mat'];
 analyze_features(data_fname,results_fname,sname,params_fname,name_of_dataset);

### 2012-05-10 code/getParams.m

@@ -1,5 +1,11 @@
 function getParams(sname,C,Lambda,Rho)
-
+% produces a MAT file containing Params={|Lambda| x |Rho|}, a cell array such that Params{i,j} = [Lambda(i) Rho(j)].  NOte that we cannot allow lambda=inf (or C=0). If passing C only, let Lambda = []. If passing Lambda only, let C = [].
+if isempty(Lambda)
+	Lambda = sort(1./C);
+end
+if isempty(C)
+	C = sort(1./Lambda);
+end
 if size(Lambda,2)==1
 	Lambda = Lambda';
 end

### 2012-05-10 report/ms.tex
removed some text that merge conflict wrote in ms.tex

--- 2012-05-10 report/ms.tex
@@
 Support Vector Machines (SVMs) are a popular method for constructing classifiers.
-Let $x_i \in \mathbb{R}^p$ be the vector of features for observation $i$ and $y_i$ its class (either $-1$ or $+1$), we can determine the SVM classifier by solving the optimization problem,
+Let $x_i \in \mathbb{R}^p$ be the vector of features for observation $i$ and $y_i$ its class (either $-1$ or $+1$).
+We determine the SVM classifier by solving the optimization problem,
 \begin{equation}
@@
 \end{equation}
-The optimal $\beta^*$ and $\beta_0^*$ are used to classify a new observation $x$ using $sign(\beta^* x + \beta_0)$.
+The optimal $\beta^{*}$ and $\beta_0^*$ are used to classify a new observation $x$ using $sign(\beta^{*T}x + \beta_0)$.
 $\lambda$ is a tuning parameter that balances a tradeoff between maximizing the margin and separating observations in different classes.
@@
 Various extensions to the standard SVM have been proposed that seek to incorporate uncertainty in the features into the optimization problem.
-These formulations often take (or can be interpreted) as minimizing the objective function for a worst case allocation of features in some fixed set, i.e.
+These formulations often take the form of (or can be interpreted as) minimizing the objective function for a worst case allocation of features in some fixed set, i.e.
 \begin{equation}
 \label{eq:svm_minimax}
-\min_{\beta,\beta_0}  \max_{z \in \mathcal{X}} \sum_{i=1}^n (1 - y_i(\beta^Tz_i + \beta_0))_{+} + \frac{\lambda}{2}\beta^T\beta
+\min_{\beta,\beta_0}  \max_{z \in \mathcal{X}(\rho)} \sum_{i=1}^n (1 - y_i(\beta^Tz_i + \beta_0))_{+} + \frac{\lambda}{2}\beta^T\beta
 \end{equation}
+where $\rho$ is some scalar and $\mathcal{X}(\rho)$ defines some set to which $(z_1, \ldots, z_n)$ belong.
 See \cite{bhattacharyya2004robust,shivaswamy2006second,ben2011chance} for discussions of some of these models.
 
-TO DISCUSS:
-\begin{enumerate}
-\item similarities to elastic net of LASSO / SVM e.g. Wang \cite{wang2007hybrid}
-\item our algorithm is not contained (?) in those considered by Russet \cite{rosset2007piecewise}
-\end{enumerate}
+One way to represent feature uncertainty is to specify that observations must lie within hyper-rectangles of feature space.
+Formally we let $X$ be an $n \times p$ matrix where row $i$ represents the center of the hyper-rectangle for observation $j$.
+We define $\Sigma$ to be an $n \times p$ matrix where $\Sigma_{i,j}$ is half the width of the hyper-rectangle around observation $i$, on feature $j$.
+Following the notation of the SVM above we can express this uncertainty model as
+\begin{equation}
+\mathcal{X}(\rho) = \{Z : X - p\Sigma \leq Z \leq X + \rho \Sigma\}
+\end{equation}
+$\rho$ is a global uncertainty parameter that shrinks or expands the hyper-rectangles uniformly.
+This model was considered in El Ghaoui\cite{el2003robust}.
+It is easy to show that for this form of $\mathcal{X}(\rho)$ one can explicity solve for the inner max in equation \eqref{eq:svm_minimax} and obtain
+\begin{equation}
+\label{eq:svmInit}
+\min_{\beta}\sum_{i=1}^n(1-y_i(\beta_0+\beta^Tx_i)+\rho\sigma_i^T|\beta|)_++\frac{\lambda}{2} ||\beta||_2^2.
+\end{equation}
+where $\sigma_i$ is the $i^{th}$ row of $\Sigma$.
+In \cite{el2003robust}, El Ghaoui drew similarities between the $\rho\sigma_i^T|\beta|$ in this expression and standard $L_1$ regularization for SVMs.
+For example, if $\Sigma_{i,j} = 1 \ \forall i,j$ then then expression becomes $\rho||\beta||_1$.
+This interpretation of $\mathcal{X}(\rho)$ in part motivates the use of $\rho$ as a tuning parameter rather than a quantity that is fixed by the inherent uncertainty in the data.
+
+In this work we will fit model \eqref{eq:svmInit} the periodic variable star data set.
+This provides an opportunity to make use of known feature uncertainty in our classifier.
+In addition, the connections between $\rho$ and sparsity, may allow us to obtain highly interpretatable classifiers, with few non-zero feature coefficients.
+
+Before we apply the model to the data, we describe a path algorithm that allows us to fit the model for all values of $\lambda$, rather than performing a brute force grid search.
+This is an adaptation of Hastie's path algorithm for standard SVMs \cite{hastie2004entire}.
 
@@
 Also let $n_+=|\mathcal I_+|$ and $n_-=|\mathcal I_-|$ be the number of data points in these two classes.
-In this section, we will derive an efficient algorithm to compute the entire regularization path for the following interval SVM problem:
-\begin{equation}
-\label{eq:svmInit}
-\min_{\beta}\sum_{i=1}^n(1-y_i(\beta_0+\beta^Tx_i)+\rho\sigma_i^T|\beta|)_++\frac{\lambda}{2} ||\beta||_2^2.
-\end{equation}
+In this section, we will derive an efficient algorithm to compute the entire regularization path for the interval SVM problem \eqref{eq:svmInit}.
+%% \begin{equation}
+%% \label{eq:svmInit}
+%% \min_{\beta}\sum_{i=1}^n(1-y_i(\beta_0+\beta^Tx_i)+\rho\sigma_i^T|\beta|)_++\frac{\lambda}{2} ||\beta||_2^2.
+%% \end{equation}
 %\eqref{eq:q}
@@
    \centering
-   \includegraphics[width=0.7\textwidth]{./betaPath.png} 
+   \includegraphics[width=0.7\textwidth]{./betaPath.pdf} 
       \caption{The path of $\beta$ for the simulated data.}
@@
 \section{Application to Variable Star Data Sets}
+We now return to the periodic variable classification problem and discuss construction of hyper-rectangles, the specific data sets we use, and results from the models.
 \subsection{Constructing the Intervals from the Time Series}
@@
 
-With astronomy data there is no clearly correct way to construct intervals around features. A few possibilities include:
+With astronomy data there is no clearly correct way to construct intervals around features which are themselves complicated functions of time series. A few possibilities include:
 \begin{enumerate}
@@
 Long time series will have small intervals around features, short time series will have wide intervals.
-For simple features, such as the standard deviation of the brightness measurements, making the interval width go down at rate root-n has a probabilistic interpretation via the central limit theorem.
+For simple features, such as the standard deviation of the brightness measurements, making the interval width go down at rate $\sqrt{n}$ has a probabilistic interpretation via the central limit theorem.
 \item Subsample the time series and derive features for each subsample.
@@
 In this work we take the second approach.
-While the first approach is attractive for simple features, many features (such as frequency) do not have a sqrt-n convergence to the true value.
-Further the irregular time sampling means that even simple features may not have a root-n convergence.
+While the first approach is attractive for simple features, many features (such as frequency) do not have a $\sqrt{n}$ convergence to the true value.
+Further, the irregular time sampling means that even simple features may not have a $\sqrt{n}$ convergence.
 The third approach involves a lot of domain knowledge and will change from application to application.
@@
 Certain computational considerations enter here.
-It takes around 1 second to derive features for an average length light curve.
+It takes around 1 second to derive features for an average length astronomical time series.
 So sampling, say 20 times, could become prohibitively expansive if the data set is initially at the limits of what is computationally feasible.
@@
 \item Slice each light curve into 5 contiguous sections, producing 5 time series.
-Slice 1 is $(t_i,m_i,e_i)$ for $\frac{0}{10}l \leq i \leq \frac{5}{10}l$, slice 2 is $\frac{1}{10}l \leq i \leq \frac{6}{10}l$, ect.
+Slice 1 is $(t_i,m_i,e_i)$ for $0 \leq i \leq .5l$, slice 2 for $.125l \leq i \leq .625l$, slice 3 for $.25l \leq i \leq .75l$ ect.
 %% \begin{enumerate}
@@
 \subsection{The Data Sets}
-The first dataset analyzed contained two classes of Cepheids (CEP):  classical and [popII].
+We use light curves from the Optical Gravitational Lensing Survey III (OGLEIII).\footnote{Light curves can be obtained here: http://ogledb.astrouw.edu.pl/~ogle/CVS/}.
+Since we want to focus on studying sparsity and the relationship between $\rho$ and $\lambda$, we select subsamples from four classes of periodic variable stars and turn these four classes into two separate data sets.
+
+The CEP dataset contains two classes of Cepheids --  Classical Cepheids and Population II Cepheids.
 Each class consisted of $n=200$ observations and $p=58$ features so that each observation is hyperrectangle in $\mathbb{R}^{58}$.
-The second dataset consisted of two classes of RR,  RR Lyrae AB and RR Lyrae D, with the same values of $n$ and $p$.
+The RR data set consists of two classes of RR --  RR Lyrae AB and RR Lyrae D, again with $n=200$ and $p=58$.
+
 \subsubsection{Preprocessing the data with quantile ranking}
-A quantile ranking technique was used to normalize values in each feature dimension by reducing the effects of outliers.
-Viewing the interval data as a three-dimensional array, the end-slices corresponding to the lower- and upper-bounds of the confidence intervals were isolated and then concatenated together to yield a $2n\times p$ array whose values were then mapped to the standard normal distribution.
-Features containing all zeroes or some NaNs were removed from the dataset.
+Many SVM machine implementation normalize features to ensure that margins are comparable between features e.g.
+\cite{dimitriadou2011package}.
+We normalize our data by assigning normal quantiles to the 2n values (lower and upper bounds of the interval) for each feature.
+This normalization preserves order relations among intervals in the sense that if one interval is completely above another then after normalization it is completely above, and if there is some overlap before normalization there will be some overlap after.
+Features containing all zeroes were removed from the dataset and missing values were inferred using the median for the feature.
 
@@
 \item links to code / git repo
+\item similarities to elastic net of LASSO / SVM e.g. Wang \cite{wang2007hybrid}
+\item our algorithm is not contained (?) in those considered by Russet \cite{rosset2007piecewise}
 \end{enumerate}
@@
    \centering
-   \includegraphics[width=0.7\textwidth]{./beta0Path.png} 
+   \includegraphics[width=0.7\textwidth]{./beta0Path.pdf} 
       \caption{The path of the intercept parameter $\beta_0$ for the simulated data. Notice that since $n_+=10>8=n_-$, by the first lemma, $\beta_0(0)=1$.}
@@
    \centering
-   \includegraphics[width=0.7\textwidth]{./alphaPath.png} 
+   \includegraphics[width=0.7\textwidth]{./alphaPath.pdf} 
       \caption{The path of $\alpha$ for the simulated data.}

### 2012-05-10 code/svmIntervalPath/svmInterval.m
now version controlling all of siqi's code

@@ -1,0 +1,36 @@
+function [beta0,beta,e,t,alpha,gamma,c,v,u,margin,obj_val] = svmInterval(x,y,Sigma,rho,C)
+% brute-force cvx way of fitting interval svm
+% x: transposed design matrix, rows represent features, column observations
+% y: 1 by n row vector
+% Sigma: the precision matrix of x, of the same dim of x
+% rho: the precision weight
+% C: 1/lambda
+
+% important outputs are
+% beta0: the intercept
+% beta: the classifier weights
+
+lambda = 1/C;
+[m,n] = size(x);
+cvx_quiet(true);
+cvx_begin
+ variable e(n);
+ variable beta(m);
+ variable beta0;
+ variable t(m);
+ dual variables alpha gamma v u c;
+ minimize(sum(e)+lambda*.5*beta'*beta);
+ subject to
+  
+  alpha:  1 - (y.*(beta0+beta'*x))'+ rho*Sigma'*t-e<=0;
+  gamma:  e >= 0;
+  u: t-beta>=0;
+  v: beta+t>=0;
+  c: t>=0;
+
+cvx_end
+
+obj_val = cvx_optval;
+margin = (y.*(beta0+beta'*x))';
+
+

### 2012-05-10 code/svmIntervalPath/svmIntervalFindNext.m

@@ -1,0 +1,260 @@
+function [Lambda_l,Beta0_l,Beta_l] = svmIntervalFindNext(x,y,rho,Sigma,iPlus,iMinus,iter_max)
+
+% This function finds the regularization path of an interval SVM
+% Inputs:
+% x: transposed design matrix, rows represent features, column observations
+% y: 1 by n row vector
+% Sigma: the precision matrix of x, of the same dim of x
+% rho: the precision weight
+% iPlus, iMinus: the +1 and -1 index set
+% iter_max: maximum break points
+
+% Outputs:
+% Lambda_l: the break points at which an event occurs
+% Beta0_l, Beta_l: the parameter values at those break points
+
+[p,n] = size(x);
+% beginning of the initialization step
+% modify this so it works for arbitrary starting point
+  [alphaS,nuS,muS] = svmIntervalInit(x,y,rho,Sigma,iPlus,iMinus);
+  [lambda_l,beta0_l,beta_l,alpha_l,nu_l,mu_l] = svmIntervalFindNext0(x,y,rho,Sigma,alphaS,nuS,muS,iPlus,iMinus);
+
+% Storing the results
+  Beta0_l = beta0_l;
+  Beta_l = beta_l;
+  Alpha_l = alpha_l;
+  Nu_l = nu_l;
+  Mu_l = mu_l;
+  Lambda_l = lambda_l;
+% end of the init step
+
+  alpha0_l = lambda_l*beta0_l;
+
+
+  % initialize the sets
+  l = y.*(beta0_l+beta_l'*x);
+  r = 1 + rho*(abs(beta_l)'*Sigma);
+  diff = l - r;
+  Elbow = find( abs(diff)<=1e-4); 
+  Left =  find( diff < -1e-4);
+  Right =  find( diff > 1e-4);
+
+  sizeOfElbow = length(Elbow);
+
+  VPlus = find(beta_l>1e-5); % index set for positive coef
+  VMinus = find(beta_l<-1e-5); % index set for negative coef
+  Z = find(abs(beta_l)<=1e-5); % index set for zero coef
+
+%Elbow = [56,362]
+
+% some global data computation
+Y = repmat(y,p,1); % p by n matrix
[…]

### 2012-05-10 code/svmIntervalPath/svmIntervalFindNext0.m

@@ -1,0 +1,41 @@
+function [lambdaNext,beta0Next,betaNext,alphaS,nuS,muS] = svmIntervalFindNext0(x,y,rho,Sigma,alphaS,nuS,muS,iPlus,iMinus)
+
+% finding the initial parameter values for the case n_+ > n_-
+% return the following variables:
+% lambdaNext: the lambda at which the next event occurs;
+% beta0Next, betaNext, alphaS, nuS, nuS: parameter values at lambdaNext
+
+[p,n] = size(x);
+
+betaS = x*(alphaS.*y')+(nuS-muS);
+temp = zeros(1,n);
+temp(iPlus) = betaS'*x(:,iPlus) - rho*abs(betaS)'*Sigma(:,iPlus);
+temp(iMinus) = betaS'*x(:,iMinus) + rho*abs(betaS)'*Sigma(:,iMinus);
+
+
+iPlusMaxTemp = find(alphaS'>1e-5 & alphaS'<1 - 1e-5 & y == 1);
+if length(iPlusMaxTemp) > 0
+% Case 1: some plus points have alpha in (0,1)
+  iPlusMax = iPlusMaxTemp(1);
+else
+% Case 2: all the plus points have alpha == 0 or 1
+  validIndex = find(y == 1 & abs(alphaS -1)'<1e-5); % y == 1 and alpha = 1
+  tempPlusMax = max(temp(validIndex));
+  iPlusMax = find(temp == tempPlusMax & y == 1 & abs(alphaS -1)'<1e-5 );
+end
+
+% Do the same thing for the minus points
+validIndex2 = find(y == -1 & abs(alphaS-1)'<1e-5); % y == -1 and alpha = 1
+tempMinusMin = min(temp(validIndex2));
+iMinusMin = find(temp == tempMinusMin & y == -1 & abs(alphaS - 1)'<1e-5);
+
+xiP = x(:,iPlusMax);
+xiM = x(:,iMinusMin);
+
+APlus = Sigma(:,iPlusMax)'*abs(betaS);
+AMinus = Sigma(:,iMinusMin)'*abs(betaS);
+
+% get the lambda0 and beta0 where the first event occurs:
+lambdaNext = 0.5*(-rho*(AMinus+APlus)+(xiP-xiM)'*betaS);
+beta0Next = 1 + (rho*APlus-xiP'*betaS)/lambdaNext;
+betaNext = betaS/lambdaNext;

### 2012-05-10 code/svmIntervalPath/svmIntervalInit.m

@@ -1,0 +1,19 @@
+function [alpha,nu,mu] = svmIntervalInit(x,y,rho,Sigma,iPlus,iMinus)
+[m,n] = size(x);
+numNeg = length(iMinus);
+cvx_quiet(true);
+cvx_begin
+  variable alpha(n);
+  variable nu(m);
+  variable mu(m);
+  minimize(norm(x*(alpha.*y')+nu-mu));
+  subject to
+    alpha(iPlus)<=1;
+    alpha(iPlus)>=0;
+    alpha(iMinus) == 1;
+    sum(alpha(iPlus))== numNeg;
+    rho*(Sigma*alpha)>=mu+nu;
+    mu>=0;
+    nu>=0;
+cvx_end;
+    

### 2012-05-10 code/svmIntervalPath/svmIntervalPath.m

@@ -1,0 +1,29 @@
+function [Lambda_l,Beta0_l,Beta_l] = svmIntervalPath(x,y,rho,Sigma,iter_max)
+
+% This function finds the regularization path of an interval SVM
+% Inputs:
+% x: transposed design matrix, rows represent features, column observations
+% y: 1 by n row vector
+% Sigma: the precision matrix of x, of the same dim of x
+% rho: the precision weight
+% iter_max: maximum break points
+
+% Outputs:
+% Lambda_l: the break points at which an event occurs
+% Beta0_l, Beta_l: the parameter values at those break points
+nPlus = sum(y == +1);
+nMinus = sum(y == -1);
+
+if nPlus < nMinus
+  y = -y;
+end
+
+iPlus = find( y == +1);
+iMinus = find( y == -1);
+
+[Lambda_l,Beta0_l,Beta_l] = svmIntervalFindNext(x,y,rho,Sigma,iPlus,iMinus,iter_max);
+
+if nPlus < nMinus
+  Beta0_l = -Beta0_l;
+  Beta_l = -Beta_l;
+end

### 2012-05-10 code/svmIntervalPath/svmIntervalTest.m

@@ -1,0 +1,81 @@
+% simulating data
+whichData = 4; % choose the data you want to fit
+randn('seed',227);
+if whichData == 1
+  % 2d data for visualization
+  % negative Beta0 and Beta
+  xPlus = normrnd(-5,2,2,10);
+  yPlus = repmat(1,1,10);
+  xMinus = normrnd(5,2,2,8);
+  yMinus = repmat(-1,1,8);
+  x = [xPlus xMinus];
+  y = [yPlus yMinus];
+  [m,n] = size(x);
+  % Sigma matrix with equal columns: 2-dim, for visualization purpose only:
+  Sigma = repmat([1,0.7]',1,n);
+  rho = 1;
+end;
+if whichData == 2
+  xPlus = [normrnd(-5,2,1,10);normrnd(0,2,1,10)];
+  yPlus = repmat(1,1,10);
+  xMinus = [normrnd(5,2,1,8);normrnd(0,2,1,8)];
+  yMinus = repmat(-1,1,8);
+  x = [xPlus xMinus];
+  y = [yPlus yMinus];
+  [m,n] = size(x);
+  Sigma = repmat([1,0.7]',1,n);
+  rho = 1;
+end;
+if whichData == 3
+  % 5 dimension example
+  xPlus = normrnd(0,1,5,10) ;
+  yPlus = repmat(1,1,10);
+  xMinus = normrnd(0,1,5,8) - 1;
+  yMinus = repmat(-1,1,8);
+  x = [xPlus xMinus];
+  y = [yPlus yMinus];
+  [m,n] = size(x);
+  Sigma = abs(normrnd(0.1,0.1,m,n));
+  rho = 1;
+end;
+if whichData == 4
+  % 5 dimension example
+  xPlus = normrnd(0,1,5,10) ;
+  yPlus = repmat(1,1,10);
+  xMinus = normrnd(0,1,5,8) - 0.5;
+  yMinus = repmat(-1,1,8);
+  x = [xPlus xMinus];
+  y = [yPlus yMinus];
+  [m,n] = size(x);
+  Sigma = abs(normrnd(0.1,0.1,m,n));
+  rho = 1;
+end;
+
+C =0.0001:0.01:3
+p = length(C);
+Beta0 = zeros(1,p);
+Beta = zeros(m,p);
+Alpha = zeros(n,p);
+V = zeros(m,p);
+U = zeros(m,p);
+CC = zeros(m,p);
[…]

### 2012-05-10 report/ms.tex
lots of changes, getting close to done

@@
 \section{Introduction}
+In this work we design an efficient, robust support vector machine (SVM) algorithm by combining 1) automated tuning of the regularization parameter $\lambda$ and 2) classification of interval data.
+The performance of this novel SVM is tested using periodic variable star data where features are believed to lie within confidence intervals.
+The paper begins with a motivating example -- classification of astronomical time series, continues with a discussion of interval SVMs and efficient path algorithms for these models, and concludes with an application of interval SVMs to two data sets from astronomy.
 
@@
 \subsection{Classification Methodology}
-There has been a lot of recent progress in the astronomy literature towards developing highly accurate classifiers for periodic variables \cite{debosscher2007automated,richards2011machine,dubath2011random}.
+There has been a lot of recent progress in the astronomy literature towards developing highly accurate classifiers for the time series generated by periodic variables \cite{debosscher2007automated,richards2011machine,dubath2011random}.
 The standard approach works as follows.
-A telescope observes a source $j$ at times $t_{1},\ldots,t_{l}$, recording flux measurements of $m_{1},\ldots,m_{l}$.
+A telescope observes a source $j$ at times $t_{1},\ldots,t_{l}$, recording flux measurements (how bright the object is) of $m_{1},\ldots,m_{l}$.
 Typically there are measurements of uncertainty on the flux measurements $e_{1},\ldots,e_{l}$.
-So each source $j$ is initially characterized by an $l \times 3$ matrix $D_j=\{(t_{i},m_{i},e_{i})\}_{i=1}^{l}$.
+So each source $j$ is initially characterized by an $l$ tuples $D_j=\{(t_{i},m_{i},e_{i})\}_{i=1}^{l}$.
 Note that $l$, the number of times the source is observed, is different for each $D_j$.
@@
 Various extensions to the standard SVM have been proposed that seek to incorporate uncertainty in the features into the optimization problem.
-These formulations often take the form of (or can be interpreted as) minimizing the objective function for a worst case allocation of features in some fixed set, i.e.
+These formulations can often be written as minimizing the objective function for a worst case allocation of features in some fixed set, i.e.
 \begin{equation}
@@
 Formally we let $X$ be an $n \times p$ matrix where row $i$ represents the center of the hyper-rectangle for observation $j$.
-We define $\Sigma$ to be an $n \times p$ matrix where $\Sigma_{i,j}$ is half the width of the hyper-rectangle around observation $i$, on feature $j$.
+We define $\Sigma$ to be an $n \times p$ matrix where $\Sigma_{i,j}$ is the relative uncertainty on observation $i$, on feature $j$.
 Following the notation of the SVM above we can express this uncertainty model as
@@
 $\rho$ is a global uncertainty parameter that shrinks or expands the hyper-rectangles uniformly.
-This model was considered in El Ghaoui\cite{el2003robust}.
+We could think of $\rho$ as a robustness parameter which larger $\rho$ leads to more robust perturbations of the input data.
+Or from a probabilistic stand--point, larger $\rho$ will increase the chance that a random feature vector is in $\mathcal{X}(\rho)$, thus ensuring separation with higher probability.
+
+This model, but without the $\frac{\lambda}{2}\beta^T\beta$ regularization, was considered in El Ghaoui \cite{el2003robust}.
 It is easy to show that for this form of $\mathcal{X}(\rho)$ one can explicity solve for the inner max in equation \eqref{eq:svm_minimax} and obtain
@@
 
-In this work we will fit model \eqref{eq:svmInit} the periodic variable star data set.
+In this work we will fit model \eqref{eq:svmInit} to the periodic variable star data sets.
 This provides an opportunity to make use of known feature uncertainty in our classifier.
@@
 
-%% \begin{enumerate}
-%% \item measurements in the middle of the light curve get used more often
-%% \item sometimes the intervals do not contain the feature obtained when using the whole light curve.
-this is because taking shorter sections of light curves biases certain features high or low (frequency significance features tend to go down, should probably just get rid of these anyway)
-%% \end{enumerate}
-%% Bootstrap sampling might be a good approach, but this would destroy cadence sensitive features.
-So not sure what to do.
-This might be something interesting to discuss in the paper: \textbf{Determining feature error intervals for time series / image data is difficult.}
-
-%% \section{Light Curves}
-
-%% Figures \ref{fig:mira}, \ref{fig:cepheid}, \ref{fig:rrlyrae} show the light curves (i.e.
-time series) of three stars.
-Each is of a different class.
-The figures show the raw light curve (time on x-axis, magnitude on y-axis) and folded light curve (phase on x-axis, magnitude on y-axis).
-The phase is determined by computing a period (sometimes wrong!, for example figure \ref{fig:mira}) for each star, and then looking at the remainder of time divided by the period.
-The folded light curve often make the structure of the function much clearer.
-
-%% \begin{figure}[h]
-%%   \begin{center}
-%%     \begin{includegraphics}[scale=.5]{4000.pdf}
-%%       \caption{Light curve of a RR Lyrae AB variable star.\label{fig:rrlyrae}}
-%%     \end{includegraphics}
-%%   \end{center}
-%% \end{figure}
-
-%% \section{Initial Classification Work}
-
-%% \subsection{Ignoring Errors}
-%% I made a data set of 5508 of these light curves of class Mira, Classical Cepheid, and RR Lyrae AB.
-Random forest (a type of classifier) obtained a 0.55\% error rate, without using any feature error information.
-So the current classes may be too easy.
-I could generate features for some stars that belong to classes that are more similar to each other e.g.
-using stars from classes RR Lyrae C and RR Lyrae D (not used here) are a lot alike and would have much higher error rates.
-
-\subsection{The Data Sets}
-We use light curves from the Optical Gravitational Lensing Survey III (OGLEIII).\footnote{Light curves can be obtained here: http://ogledb.astrouw.edu.pl/~ogle/CVS/}.
-Since we want to focus on studying sparsity and the relationship between $\rho$ and $\lambda$, we select subsamples from four classes of periodic variable stars and turn these four classes into two separate data sets.
-
-The CEP dataset contains two classes of Cepheids --  Classical Cepheids and Population II Cepheids.
-Each class consisted of $n=200$ observations and $p=58$ features so that each observation is hyperrectangle in $\mathbb{R}^{58}$.
-The RR data set consists of two classes of RR --  RR Lyrae AB and RR Lyrae D, again with $n=200$ and $p=58$.
-
-\subsubsection{Preprocessing the data with quantile ranking}
+\subsection{Preprocessing the data with quantile ranking}
 Many SVM machine implementation normalize features to ensure that margins are comparable between features e.g.
@@
 
+\subsection{The Data Sets}
+We use light curves from the Optical Gravitational Lensing Survey III (OGLEIII).\footnote{Light curves can be obtained here: http://ogledb.astrouw.edu.pl/~ogle/CVS/}.
+Since we want to focus on studying sparsity and the relationship between $\rho$ and $C$, we choose two small data sets that will be easy to analyze.
+\begin{enumerate}
+\item The CEP dataset contains two classes of Cepheids --  Classical Cepheids and Population II Cepheids.  Each class consisted of $n=200$ observations and $p=58$ features.
+\item The RR data set consists of two classes of RR Lyrae stars -- RR Lyrae AB and RR Lyrae D, again with $n=200$ and $p=58$.
+\end{enumerate}
+
 \subsection{Results}
@@
 \subsubsection{Performance}
-The performance of the combined SVM model was compared to those of its degenerates by computing expected losses for multiple values of $\lambda$ and $\rho$.
+We treat $C$ and $\rho$ as tuning parameters and grid search across them to find the optimal values.
+We use a grid search for $C$, rather than the path algorithm, because it gives more consistent results.
+This may be due to a bug somewhere in our path code.
+In order to assess performance on the grid, we perform 10 fold cross validation, with some initial processing to determine where the grid should be placed.
+
+Figure \ref{fig:regularizations} shows cross-validation error rates for given C (x-axis) and $\rho$ y-axis for the RR data set (left) and the CEP data set (right).
+The color strip on the right shows performance when $C=\infty$, i.e.
+no $L_2$ regularization.
+In both cases, using $\rho>0$ and $C < \infty$ gives better performance than only relying on one method for regularization.
+In the left plot (RR data set), there is some evidence of a tradeoff in regularization between $\rho$ and $C$.
+By this we mean, as one increases $C$ (regularizes less using the standard penalty), the optimal hyper-rectangle size increases, suggesting this is making up for less $L_2$ regularization.
+
+One attractive feature of using hyper-rectangles to represent uncertainty is the opportunity to obtain sparse solutions.
+In Figures \ref{fig:RRfeatures} (RR) and \ref{fig:CEPfeatures} (CEP) we list the features and coefficients for all features with non-zero coefficients for the models with the lowest error rate.
+In both cases, over half the features have coefficients exactly 0.
+It is also true that in both cases many feature have coefficients which are close to, but not quite 0.
+We might be able to obtain sparser solutions by increasing our $\rho$.
+The tradeoff to this, is that this would mean choosing a model that did not obtain optimal misclassification performance.
+
+The performance of the SVM model was compared  all values of $\lambda$ and a grid search on $\rho$.
 For a given $(\lambda,\rho)$, the expected loss was computed by performing cross-validation in 90-10 splits so that the union of testing points across splits is the entire dataset and the intersection is disjoint.
@@
 
-\subsubsection{Feature selection as suggested by $||\beta||_0$ values}
+\begin{figure}[ht]
+\begin{center}
+\begin{tabular}{cc}
+$\begin{array}{cc}
+\multicolumn{1}{l}{\mbox{(a)}} & \multicolumn{1}{l}{\mbox{(b)}} \\ \\ \\ [-.35in]
+\includegraphics[width=0.45\textwidth]{RR2_svmIntC} &
+\includegraphics[width=0.45\textwidth]{CEP_svmIntC}
+\end{array}$
+\end{tabular}
+\end{center}
+\caption{(a) Performance across tuning parameters for RR data set. (b) Performance across tuning parameters for CEP data set.}
+\label{fig:regularizations}
+\end{figure}
+
+\begin{figure}
+\include{RR2_features}
+\caption{RR features with non-zero coefficients.
+Some coefficient are reported here as 0 due to rounding.
+Choosing a slightly higher $\rho$ may have caused severl of the features with very small coefficients to become exactly 0, leading to a very sparse solution.\label{fig:RRfeatures}}
+\end{figure}
+
+\begin{figure}
+\include{CEP_features}
+\caption{CEP features. Features with large coefficients correspond well to features that are known to be important for separating these two classes.\label{fig:CEPfeatures}}
+\end{figure}
+
+%\subsubsection{Feature selection as suggested by $||\beta||_0$ values}
 

### 2012-05-10 report/ms.tex
almost done

@@
-\documentclass[10pt]{article}
+\documentclass[11pt]{article}
 \usepackage{amsmath,textcomp,amssymb,graphicx,amsthm,enumerate}
@@
 
+\begin{figure}[ht]
+\begin{center}
+\begin{tabular}{cc}
+$\begin{array}{cc}
+\multicolumn{1}{l}{\mbox{(a)}} & \multicolumn{1}{l}{\mbox{(b)}} \\ \\ \\ [-.35in]
+\includegraphics[width=0.45\textwidth]{./beta0Path} &
+\includegraphics[width=0.45\textwidth]{./alphaPath}
+\end{array}$
+\end{tabular}
+\end{center}
+\caption{(a) Performance across tuning parameters for RR data set. (b) The path of $\alpha$ for the simulated data.}
+\label{fig:beta0alphaPath}
+\end{figure}
+
 %\subsection{Extension to Kernal} (You need to transform the uncertainty in the original data space into the kernal space)
@@
 It takes around 1 second to derive features for an average length astronomical time series.
-So sampling, say 20 times, could become prohibitively expansive if the data set is initially at the limits of what is computationally feasible.
+So sampling, say 20 times, could become prohibitively expensive if the data set is initially at the limits of what is computationally feasible.
 \begin{figure*}[ht]
@@
 
-\subsubsection{Performance}
 We treat $C$ and $\rho$ as tuning parameters and grid search across them to find the optimal values.
@@
 We might be able to obtain sparser solutions by increasing our $\rho$.
-The tradeoff to this, is that this would mean choosing a model that did not obtain optimal misclassification performance.
+The tradeoff is that this would mean choosing a model that did not obtain optimal misclassification performance.
 
-The performance of the SVM model was compared  all values of $\lambda$ and a grid search on $\rho$.
+%% The performance of the SVM model was compared  all values of $\lambda$ and a grid search on $\rho$.
 For a given $(\lambda,\rho)$, the expected loss was computed by performing cross-validation in 90-10 splits so that the union of testing points across splits is the entire dataset and the intersection is disjoint.
@@
 
-The curves of loss versus $\lambda$ and loss versus $\rho$ were also analyzed.
+%% The curves of loss versus $\lambda$ and loss versus $\rho$ were also analyzed.
 The loss versus $\lambda$ plot corresponds to the standard point SVM model in Hastie while the loss versus $\rho$ plot corresponds to the interval SVM model in El Ghaoui.
@@
 \subsection{Conclusions}
-\begin{enumerate}
-\item constructing intervals is non-trivial in many high dimensional problems
-\item not clear that this robust framework is ideal when new observation might have low error on certain features
-\item kernels, are they possible to use
-\item links to code / git repo
-\item similarities to elastic net of LASSO / SVM e.g. Wang \cite{wang2007hybrid}
-\item our algorithm is not contained (?) in those considered by Russet \cite{rosset2007piecewise}
-\end{enumerate}
-
-\subsection{Appendix}
-\begin{center}
-\begin{figure}[!h]
-   \centering
-   \includegraphics[width=0.7\textwidth]{./beta0Path.pdf} 
-      \caption{The path of the intercept parameter $\beta_0$ for the simulated data. Notice that since $n_+=10>8=n_-$, by the first lemma, $\beta_0(0)=1$.}
-   \label{fig:beta0Path}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}[!h]
-   \centering
-   \includegraphics[width=0.7\textwidth]{./alphaPath.pdf} 
-      \caption{The path of $\alpha$ for the simulated data.}
-   \label{fig:alphaPath}
-\end{figure}
-\end{center}
+We have developed an algorithm and empirically studied an SVM interval model which incorporates feature uncertainty and produces sparse classifiers.
+The model improves on classification performance over ignoring feature uncertainty.
+We feel that the results warrent applying this method to larger and multi-class astronomy data sets.
+From a data perspective we faced several challenges, the greatest of which was determinining intervals for features.
+This will be common in many high dimensional classification problems where there is uncertainty on features, but no clear way to contruct intervals.
 

### 2012-05-10 report/ms.tex
almost done

@@
 In this work we design an efficient, robust support vector machine (SVM) algorithm by combining 1) automated tuning of the regularization parameter $\lambda$ and 2) classification of interval data.
-The performance of this novel SVM is tested using periodic variable star data where features are believed to lie within confidence intervals.
-The paper begins with a motivating example -- classification of astronomical time series, continues with a discussion of interval SVMs and efficient path algorithms for these models, and concludes with an application of interval SVMs to two data sets from astronomy.
+The performance of this SVM is tested using periodic variable star data where features are believed to lie within confidence intervals.
+The paper begins with a motivating example -- classification of astronomical time series (Section \ref{sec:data}), continues with a discussion of interval SVMs and efficient path algorithms for these models (Sections \ref{sec:interval_svms} and \ref{sec:path_algorithm}), and concludes with an application of interval SVMs to two data sets from astronomy (Section \ref{sec:application}).
 
 \section{The Data}
+\label{sec:data}
 \subsection{Background on Periodic Variables}
@@
 \section{SVMs for Interval Data}
+\label{sec:interval_svms}
 Support Vector Machines (SVMs) are a popular method for constructing classifiers.
@@
 \section{Path Algorithm for Interval SVM}
-
+\label{sec:path_algorithm}
 \subsection{Problem formulation}
@@
 
+\begin{center}
+\begin{figure}[!h]
+   \centering
+   \includegraphics[width=0.5\textwidth]{./betaPath.pdf} 
+      \caption{The path of $\beta$ for the simulated data.}
+   \label{fig:betaPath}
+\end{figure}
+\end{center}
+
 \subsection{The Path}
@@
 
+\begin{figure}[ht]
+\begin{center}
+\begin{tabular}{cc}
+$\begin{array}{cc}
+\multicolumn{1}{l}{\mbox{(a)}} & \multicolumn{1}{l}{\mbox{(b)}} \\ \\ \\ [-.35in]
+\includegraphics[width=0.45\textwidth]{./beta0Path} &
+\includegraphics[width=0.45\textwidth]{./alphaPath}
+\end{array}$
+\end{tabular}
+\end{center}
+\caption{(a) Performance across tuning parameters for RR data set. (b) The path of $\alpha$ for the simulated data.}
+\label{fig:beta0alphaPath}
+\end{figure}
+
 \subsection{Finding the Next Event}
@@
 
-\begin{center}
-\begin{figure}[!h]
-   \centering
-   \includegraphics[width=0.7\textwidth]{./betaPath.pdf} 
-      \caption{The path of $\beta$ for the simulated data.}
-   \label{fig:betaPath}
-\end{figure}
-\end{center}
-
 \subsection{Computation Complexity}
@@
 Note that the path algorithm gives the true path while the brute-force algorithm is still finding only a few snapshots of the path.
-
-\begin{figure}[ht]
-\begin{center}
-\begin{tabular}{cc}
-$\begin{array}{cc}
-\multicolumn{1}{l}{\mbox{(a)}} & \multicolumn{1}{l}{\mbox{(b)}} \\ \\ \\ [-.35in]
-\includegraphics[width=0.45\textwidth]{./beta0Path} &
-\includegraphics[width=0.45\textwidth]{./alphaPath}
-\end{array}$
-\end{tabular}
-\end{center}
-\caption{(a) Performance across tuning parameters for RR data set. (b) The path of $\alpha$ for the simulated data.}
-\label{fig:beta0alphaPath}
-\end{figure}
 
@@
 \section{Application to Variable Star Data Sets}
+\label{sec:application}
 We now return to the periodic variable classification problem and discuss construction of hyper-rectangles, the specific data sets we use, and results from the models.
 \subsection{Constructing the Intervals from the Time Series}
+\begin{figure*}[ht]
+\begin{center}
+{\small
+\framebox[6in]{
+\begin{minipage}[t]{5.8in}
+% Insert here your text
+\begin{center} \textbf{Constructing Hyper-rectangles from Time Series} \end{center}
+\begin{enumerate}
+\item Order the light curve measurements in time i.e. $\{(t_1,m_1,e_1),(t_2,m_2,e_2), \ldots , (t_l,m_l,e_l)\}$ where $t_i < t_j$ for $i < j$.
+\item Slice each light curve into 5 contiguous sections, producing 5 time series.
+Slice 1 is $(t_i,m_i,e_i)$ for $0 \leq i \leq .5l$, slice 2 for $.125l \leq i \leq .625l$, slice 3 for $.25l \leq i \leq .75l$ ect.
+%% \begin{enumerate}
+%% \item $\{(t_1,m_1,e_1), \ldots , (t_{l/2},m_{l/2},e_{l/2})\}$
+%% \item $\{(t_1,m_1,e_1),(t_2,m_2,e_2), \ldots , (t_l,m_l,e_l)\}$
+%% \end{enumerate}
+\item Derive features for each of these slices.
+\item Put the interval minimum at the lowest value of the feature for the 5 slices. Put the interval max at the maximum feature value across the 5 slices.
+\end{enumerate}
+\end{minipage}
+}
+}
+\end{center}
+\caption{Description of interval construction algorithm.\label{fig:interval_construction}}
+\label{lb}
+\end{figure*}
 In certain applications, methods for constructing hyper-rectangles (or hyper-spheres) in feature space may be fairly straitforward.
@@
 So sampling, say 20 times, could become prohibitively expensive if the data set is initially at the limits of what is computationally feasible.
-\begin{figure*}[ht]
-\begin{center}
-{\small
-\framebox[6in]{
-\begin{minipage}[t]{5.8in}
-% Insert here your text
-\begin{center} \textbf{Constructing Hyper-rectangles from Time Series} \end{center}
-\begin{enumerate}
-\item Order the light curve measurements in time i.e. $\{(t_1,m_1,e_1),(t_2,m_2,e_2), \ldots , (t_l,m_l,e_l)\}$ where $t_i < t_j$ for $i < j$.
-\item Slice each light curve into 5 contiguous sections, producing 5 time series.
-Slice 1 is $(t_i,m_i,e_i)$ for $0 \leq i \leq .5l$, slice 2 for $.125l \leq i \leq .625l$, slice 3 for $.25l \leq i \leq .75l$ ect.
-%% \begin{enumerate}
-%% \item $\{(t_1,m_1,e_1), \ldots , (t_{l/2},m_{l/2},e_{l/2})\}$
-%% \item $\{(t_1,m_1,e_1),(t_2,m_2,e_2), \ldots , (t_l,m_l,e_l)\}$
-%% \end{enumerate}
-\item Derive features for each of these slices.
-\item Put the interval minimum at the lowest value of the feature for the 5 slices. Put the interval max at the maximum feature value across the 5 slices.
-\end{enumerate}
-\end{minipage}
-}
-}
-\end{center}
-\caption{Description of interval construction algorithm.\label{fig:interval_construction}}
-\label{lb}
-\end{figure*}
 
@@
 \subsection{Results}
-
+\begin{figure}[ht]
+\begin{center}
+\begin{tabular}{cc}
+$\begin{array}{cc}
+\multicolumn{1}{l}{\mbox{(a)}} & \multicolumn{1}{l}{\mbox{(b)}} \\ \\ \\ [-.35in]
+\includegraphics[width=0.45\textwidth]{RR2_svmIntC} &
+\includegraphics[width=0.45\textwidth]{CEP_svmIntC}
+\end{array}$
+\end{tabular}
+\end{center}
+\caption{(a) Performance across tuning parameters for RR data set. (b) Performance across tuning parameters for CEP data set.}
+\label{fig:regularizations}
+\end{figure}
 We treat $C$ and $\rho$ as tuning parameters and grid search across them to find the optimal values.
@@
 
-\begin{figure}[ht]
-\begin{center}
-\begin{tabular}{cc}
-$\begin{array}{cc}
-\multicolumn{1}{l}{\mbox{(a)}} & \multicolumn{1}{l}{\mbox{(b)}} \\ \\ \\ [-.35in]
-\includegraphics[width=0.45\textwidth]{RR2_svmIntC} &
-\includegraphics[width=0.45\textwidth]{CEP_svmIntC}
-\end{array}$
-\end{tabular}
-\end{center}
-\caption{(a) Performance across tuning parameters for RR data set. (b) Performance across tuning parameters for CEP data set.}
-\label{fig:regularizations}
-\end{figure}
-
 \begin{figure}

### 2012-05-10 report/ms.tex
final change to ms

@@
 This time series is periodic.
-Using fourier methods we can estimate a period of 4.51 days.
+Using Fourier methods we can estimate a period of 4.51 days.
 We can convert the times from the top plot into phase ((time modulo period) / period)).
@@
 The 0 point on the time axis is arbitrary.
-Using fourier methods, one can estimate a period using these measurements.
+Using Fourier methods, one can estimate a period using these measurements.
 The lower plot of Figure \ref{fig:cepheid} displays the flux measurements of the same object.
@@
 From the y-axis we can see that this source has higher amplitude than the Classical Cepheid (this is typical of the Mira class) and more sinusoidal variation (also typical).
-Note that the fourier methods appear to have estimated an incorrect period for this source.
+Note that the Fourier methods appear to have estimated an incorrect period for this source.
 The true period appears to be around 161 days, half of the estimate.
@@
 take functions of $D_j$) that will separate sources into different classes.
-Features vary from study to study, but typical ones include period (inverse of strongest fourier frequency), amplitude, skew, and estimates of derivatives.
+Features vary from study to study, but typical ones include period (inverse of strongest Fourier frequency), amplitude, skew, and estimates of derivatives.
 
@@
 Some of the observations have values outside these physical limits, clearly indicating that the features are incorrectly estimated.
-This suggests that classifiers which incorporate feature uncertainty may be able to acheive improved performance.
+This suggests that classifiers which incorporate feature uncertainty may be able to achieve improved performance.
 
@@
 This model, but without the $\frac{\lambda}{2}\beta^T\beta$ regularization, was considered in El Ghaoui \cite{el2003robust}.
-It is easy to show that for this form of $\mathcal{X}(\rho)$ one can explicity solve for the inner max in equation \eqref{eq:svm_minimax} and obtain
+It is easy to show that for this form of $\mathcal{X}(\rho)$ one can explicitly solve for the inner max in equation \eqref{eq:svm_minimax} and obtain
 \begin{equation}
@@
 \noindent\textbf{Proof.} The proof follows directly from Lemma 2 in \cite{hastie2004entire}.
-The key observasion is that  $\sum_{i=1}^n \alpha_i = 2n_-$ and this sum will remain constant for a while as $\beta$ grows from zero.
+The key observation is that  $\sum_{i=1}^n \alpha_i = 2n_-$ and this sum will remain constant for a while as $\beta$ grows from zero.
 Then we can plug this sum into the dual problem \eqref{eq:dual} and solve it with additional constraints: $\alpha_i = 1,  \forall i \in \mathcal I_-$ and $\sum_{i \in \mathcal I_+}\alpha_i = n_-$.
@@
 This does not seem to be the case in our problem, as it also involves finding the initial values of the extra dual variables $\mu$ and $\nu$.
-Therefore solving a quardratic problem for starting up the path algorithm cannot be avoided in our case.\\
+Therefore solving a quadratic problem for starting up the path algorithm cannot be avoided in our case.\\
 
@@
 
-%\subsection{Extension to Kernal} (You need to transform the uncertainty in the original data space into the kernal space)
+%\subsection{Extension to Kernel} (You need to transform the uncertainty in the original data space into the kernel space)
 %\note{in fitting the CEP data,  between 2.03 and 2.13 $\beta0$ value can be arbitrary}
@@
 All the programs for this project are included in the {\tt zip} file submitted together with this hard copy.
-In particular, the matlab package {\tt svmIntervalPath} is the implementation of our path algorithm.
-Also, matlab and R code for testing and data analysis can be found in that file as well.
+In particular, the Matlab package {\tt svmIntervalPath} is the implementation of our path algorithm.
+Also, Matlab and R code for testing and data analysis can be found in that file as well.
 
@@
 \end{figure*}
-In certain applications, methods for constructing hyper-rectangles (or hyper-spheres) in feature space may be fairly straitforward.
+In certain applications, methods for constructing hyper-rectangles (or hyper-spheres) in feature space may be fairly strait forward.
 For example in El Ghaoui \cite{el2003robust}, the authors discuss applications to micro-array data where several replicates of some experiment are available, and a hyper-rectangle can be chosen to enclose all replicates.
@@
 Some coefficient are reported here as 0 due to rounding.
-Choosing a slightly higher $\rho$ may have caused severl of the features with very small coefficients to become exactly 0, leading to a very sparse solution.\label{fig:RRfeatures}}
+Choosing a slightly higher $\rho$ may have caused several of the features with very small coefficients to become exactly 0, leading to a very sparse solution.\label{fig:RRfeatures}}
 \end{figure}
@@
 \include{CEP_features}
-\caption{CEP features. Features with large coefficients correspond well to features that are known to be important for separating these two classes.\label{fig:CEPfeatures}}
+\caption{CEP features with non-zero coefficients. Some coefficients are reported as 0 here due to rounding.\label{fig:CEPfeatures}}
 \end{figure}
@@
 The model improves on classification performance over ignoring feature uncertainty.
-We feel that the results warrent applying this method to larger and multi-class astronomy data sets.
-From a data perspective we faced several challenges, the greatest of which was determinining intervals for features.
-This will be common in many high dimensional classification problems where there is uncertainty on features, but no clear way to contruct intervals.
+We feel that the results warrant applying this method to larger and multi-class astronomy data sets.
+From a data perspective we faced several challenges, the greatest of which was determining intervals for features.
+This will be common in many high dimensional classification problems where there is uncertainty on features, but no clear way to construct intervals.
+Generalizing feature extraction methods to produce estimates of uncertainty will make application of interval SVM methods much easier.
+
+A natural extension of the SVM interval concept is to incorporate the feature uncertainty of the unknown test data point into the classifier.
+Broadly, if a new unlabeled observation has a lot of uncertainty on feature $x$, then it does not make sense to use feature $x$ heavily in the classifier.
+However if feature $x$ has small error then a classifier should make as much use of $x$ as possible.
+Since different observations will have different amounts of noise in different features, it may make sense to develop interval SVM methods that are specifically tuned the the uncertainty of each unlabeled observation.
+We will work on developing this idea further in future work.
 

### 2012-05-10 report/create_table.py
changed code for making latex table

@@ -29,14 +29,15 @@ if __name__ == "__main__":
 
     ### print non-zero features in nice table
     ## beginning parts of table
-    table = r"""\begin{center}\n\begin{tabular}{ | l | l |}\n\hline"""
+    table = r"""\begin{center}""" + "\n" + r"""\begin{tabular}{ | l | l |}""" + "\n" + r"""\hline""" + "\n"
+    table = table + r"""\textbf{feature name} & \textbf{beta} \\""" + "\n"
     for j in zip(feature_names,weight):
         if j[1] > 0.0:
-            table = table + r"&" + j[0] + r" & " + repr(j[1]) + r"\\" + r"\n"
-    table = table +  r"""\hline\n\end{tabular}\n\end{center}"""
+            table = table + j[0] + r" & " + ("%.2f" % j[1]) + r"\\" + "\n"
+    table = table +  r"""\hline""" + "\n" + """\end{tabular}""" + "\n" + """\end{center}"""
     print table
+    table = table.replace("_"," ")
     output_file = sys.argv[1].split('/').pop().split('.')[0] + ".tex"
     g = open(output_file,'w')
-    table = table.split('\n')
-    g.writelines(table)
+    g.write(table)
     g.close()
